### 2016-06-13 paper.tex
first commit

\documentclass[english, apj]{emulateapj}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{array}
\usepackage{rotating}
\usepackage{units}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{amsbsy}
\usepackage{amstext}
\usepackage{graphicx}
\usepackage{url}
\usepackage{babel}
\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
\usepackage[all]{hypcap}

\makeatletter

\newcommand{\msun}{\mbox{$\,{\rm M}_\odot$}}

\sloppy

\providecommand{\tabularnewline}{\\}

\begin{document}

\title{Cannibalism among the supermassive black holes}

\author{Charles Zivancev\altaffilmark{1}, Andreas H.W. K\"upper\altaffilmark{1,2}, Jeremiah P. Ostriker\altaffilmark{1,3}}
\altaffiltext{1}{Department of Astronomy, Columbia University, 550 West 120th Street, New York, NY 10027, USA}
\altaffiltext{2}{Hubble Fellow}
\altaffiltext{3}{Princeton University, New Jersey, USA}
\email{Correspondence to: csz2104@columbia.edu}

\begin{abstract}

\end{abstract}

\keywords{Galaxy: kinematics and dynamics}

\section{Introduction}\label{sec:introduction}

\section{Methods}\label{sec:methods}

\subsection{Merger tree}
Where we got the merger data from and how we extracted it.
- Using Andrea Kulier's cosmological simulation, we plotted galaxy masses as a function of time.
- We took the data from the three most massive galaxies (ie, most massive at redshift z=0).
- We curve-fit each galaxy's mass to polynomial functions of time.
- We also curve-fit each galaxy's (accreted+seeded) central black hole mass to exponential functions of time.
- We added those functions to the Fortran hermite code
- We implemented the SO potential-density pair (using the m200, r200 from the fitting functions above, getting half-mass radius from NFW profile, and using it as half-mass radius for the SO profile).

Simulation of Cen et al. (have to look up the year)

\subsection{AR-Chain code}
Summary of the code and the modifications we made.

For the numerical simulations presented here, we used a modified version of the algorithmic chain integrator \textsc{AR-Chain} developed by \citet{Mikkola06}. It uses algorithmic chain regularization for high-precision integration of few-body dynamics, and is capable of handling velocity-dependent forces efficiently. It includes relativistic post-Newtonian terms up to order PN2.5 \citep{Mikkola08}.

\subsubsection{Galaxy background potential}

\subsubsection{Phase-space diffusion}
Weak encounters with background stars will let the SMBHs diffuse through phase space while they are orbiting within the gravitational potential of the galaxy.

\subsubsection{Gravitational wave recoils}
The code \textsc{AR-Chain} includes PN terms up to order 2.5. The SMBHs can therefore merge via gravitational wave emission. We include gravitational wave recoils following the prescription outlined in \citet{Kulier_2015}, which is based on the fitting formula by \citet{Lousto12}. To save computational time, we assume that a merger will be inevitable when the separation between two SBHs gets smaller than 10\,000 Schwarzschild radii. At the moment of the merger, we assume that the spin vectors of the two SBHs are randomly aligned. This results in kick velocities of up to several thousand km\,s$^{-1}$, with a median kick of $\approx 290$\,km\,s$^{-1}$. Since our simulations focus on NSC with relatively low escape velocities, this implies that a majority of the merging SBHs escape from the NSCs.

Black holes can also eject each other via strong three-body interactions. We remove SBHs from the simulations once they move beyond 1\,kpc from the NSC, assuming that it will take them more than a Hubble time to find their way back into the center of the host galaxy.

\subsection{Simulation setup}
Injection, merging, escape, effective radius, set of galaxies

\section{Results}\label{sec:results}

\subsection{Mergers}

\begin{figure}
\centering
%\includegraphics[width=0.45\textwidth]{plots/plot1.png}
\caption{This is a caption.}
\label{this_is_a_label}
\end{figure}

\subsection{Ejections}

\subsection{Stalling SMBH binaries}

\subsection{Stalling SMBHs in the halo}

\section{Conclusions}\label{sec:conclusions}
What do we want to say?

\section*{Acknowledgements}

The authors would like to thank Andrea Kulier for providing merger tree data. AHWK acknowledges support by NASA through Hubble Fellowship grant HST-HF-51323.01-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS 5-26555.

\bibliographystyle{apj}
\begin{thebibliography}{}

\bibitem[\protect\citeauthoryear{Aarseth}{2003}]{Aarseth03}
Aarseth, S.~J., 2003, Gravitational N-Body Simulations (Cambridge University Press)

\bibitem[\protect\citeauthoryear{K{\"u}pper et al.}{2011}]{Kupper11} 
K{\"u}pper, A.~H.~W., Maschberger, T., Kroupa, P., Baumgardt, H., 2011, MNRAS, 417, 2300

\end{thebibliography}
\end{document}

### 2016-08-03 paper.tex
added biblio.bib file for references; modified citations.

@@
 \subsection{Merger tree}
-Where we got the merger data from and how we extracted it.
+- Where we got the merger data from and how we extracted it.
+Our merger tree data came from cosmological simulations of Kulier
 - Using Andrea Kulier's cosmological simulation, we plotted galaxy masses as a function of time.
+
 - We took the data from the three most massive galaxies (ie, most massive at redshift z=0).
+
 - We curve-fit each galaxy's mass to polynomial functions of time.
+
 - We also curve-fit each galaxy's (accreted+seeded) central black hole mass to exponential functions of time.
+
 - We added those functions to the Fortran hermite code
+
 - We implemented the SO potential-density pair (using the m200, r200 from the fitting functions above, getting half-mass radius from NFW profile, and using it as half-mass radius for the SO profile).
@@
 
-For the numerical simulations presented here, we used a modified version of the algorithmic chain integrator \textsc{AR-Chain} developed by \citet{Mikkola06}.
+For the numerical simulations presented here, we used a modified version of the algorithmic chain integrator \textsc{AR-Chain} developed by \citet{2006MNRAS.372..219M}.
 It uses algorithmic chain regularization for high-precision integration of few-body dynamics, and is capable of handling velocity-dependent forces efficiently.
-It includes relativistic post-Newtonian terms up to order PN2.5 \citep{Mikkola08}.
+It includes relativistic post-Newtonian terms up to order PN2.5 \citep{2008AJ....135.2398M}.
 
@@
 The SMBHs can therefore merge via gravitational wave emission.
-We include gravitational wave recoils following the prescription outlined in \citet{Kulier_2015}, which is based on the fitting formula by \citet{Lousto12}.
+We include gravitational wave recoils following the prescription outlined in \citet{2015ApJ...799..178K}, which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.
 To save computational time, we assume that a merger will be inevitable when the separation between two SBHs gets smaller than 10\,000 Schwarzschild radii.
@@
 \bibliographystyle{apj}
-\begin{thebibliography}{}
+\bibliography{test}
 
-\bibitem[\protect\citeauthoryear{Aarseth}{2003}]{Aarseth03}
-Aarseth, S.~J., 2003, Gravitational N-Body Simulations (Cambridge University Press)
+%\begin{thebibliography}{}
 
-\bibitem[\protect\citeauthoryear{K{\"u}pper et al.}{2011}]{Kupper11} 
-K{\"u}pper, A.~H.~W., Maschberger, T., Kroupa, P., Baumgardt, H., 2011, MNRAS, 417, 2300
+%\bibitem[\protect\citeauthoryear{Aarseth}{2003}]{Aarseth03}
+%Aarseth, S.~J., 2003, Gravitational N-Body Simulations (Cambridge University Press)
 
-\end{thebibliography}
+%\bibitem[\protect\citeauthoryear{K{\"u}pper et al.}{2011}]{Kupper11} 
+%K{\"u}pper, A.~H.~W., Maschberger, T., Kroupa, P., Baumgardt, H., 2011, MNRAS, 417, 2300
+
+%\end{thebibliography}
 \end{document}

### 2016-08-04 paper.tex
added mods to paper.tex and paper.blg
wrote Merger Tree section.

@@
 \usepackage[all]{hypcap}
+%\usepackage{siunitx}
 
@@
 \subsection{Merger tree}
-- Where we got the merger data from and how we extracted it.
-Our merger tree data came from cosmological simulations of Kulier
-- Using Andrea Kulier's cosmological simulation, we plotted galaxy masses as a function of time.
+Our merger tree data came from the SMBH evolution simulations of \citet{2015ApJ...799..178K}, which used the large-scale hydrodynamical galaxy simulations outlined by \citet{2011ApJ...741...99C}, \citet{2011ApJ...742L..33C}, \citet{2012ApJ...753...17C}, \citet{2012ApJ...748..121C} and \citet{2013ApJ...770..139C}.
+The following cosmological parameters were used in their simulation:   $\Omega_M = 0.28$, $\Omega_b = 0.046$, $\Omega_\Lambda = 0.72$, $\sigma_8 = 0.82$, $H_0 = 100h^{-1}Mpc^{-1} = 70 km s^{-1} Mpc^{-1}$, and $n = 0.96$.
+The SMBHs were evolved from $4\geq z \geq 0$.
 
-- We took the data from the three most massive galaxies (ie, most massive at redshift z=0).
+The merger tree data was in two primary files.
+One file was centered around SMBHs at each redshift slice, giving information for the black hole's seed mass, accreted and seed mass, its host galaxy, the stellar mass in its host galaxy, and time after z=4 at which the BH entered the host galaxy (if it is not the central BH).
+The other file was centered on galaxies at each redshift slice, prociding information on the galaxyies' stellar mass, dark matter mass, its central BH, and any orbiting black holes within the galaxy.
 
-- We curve-fit each galaxy's mass to polynomial functions of time.
+Starting with this data, we plotted the galaxy masses as a function of time.
+Since the raw data was given in terms of redshift, we converted redshift to time with the help of a 'cosmology calculator', courtesy of Ned Wright and James Schombert (\url{http://www.astro.ucla.edu/~wright/CosmoCalc.html}).
+We chose three galaxies to run our simulations.
+The galaxies were chosen using the following basic criteria:
+\begin{itemize}
+\item The galaxies had to exist through the entire simulation, from $z=4$ to $z=0$.
+\item They had to have a central SMBH.
+\item They had to have at least XXX orbiting black holes.
+\item We ordered the galaxies by decreasing mass at $z=0$, and starting with the largest tier of mass (~$10^{14} M_{\odot}$), we spaced their masses by approximately 1-2 orders of magnitude.
+\end{itemize}
 
-- We also curve-fit each galaxy's (accreted+seeded) central black hole mass to exponential functions of time.
-
-- We added those functions to the Fortran hermite code
+After finding our subject galaxies, we curve-fit their total masses as a function of time using a simple $7^{th}$-order polynomial fit, so as to be able to use their masses in the AR-Chain code.
+Additionally, we curve-fit each galaxy's accreted+seed central black hole mass to exponential functions of time.
 
 - We implemented the SO potential-density pair (using the m200, r200 from the fitting functions above, getting half-mass radius from NFW profile, and using it as half-mass radius for the SO profile).
-
-Simulation of Cen et al. (have to look up the year)
 
@@
 \bibliographystyle{apj}
-\bibliography{test}
+\bibliography{biblio}
 

### 2016-08-12 paper.tex
worked on Galaxy Background Potential section.

@@
 
-- We implemented the SO potential-density pair (using the m200, r200 from the fitting functions above, getting half-mass radius from NFW profile, and using it as half-mass radius for the SO profile).
-
 \subsection{AR-Chain code}
@@
 \subsubsection{Galaxy background potential}
+The simulations from which we obtained the merger tree data considered only dark matter distributions and were run using the Navarro-Frenk-White (NFW) profile described in \citet{1997ApJ...490..493N}.
+Since our study is more interested SMBH mergers at the center of galaxies, dynamical friction, and hence baryonic matter, was of considerable importance.
+Therefore, NFW background potential was less suitable for our application.
+
+In considering a suitable potential-density pair, characteristics that were important were:
+\begin{itemize}
+\item It must take into account baryonic mater
+\item It must have a finite density in the center out to a scale radius
+\item Declining density that drops more sharply out to a second scale radius
+\item An even sharper decline in density beyond the second scale radius
+\item It must be easily parametrized and written in analytic, closed form
+\end{itemize}
+
+For our simulations, the Jerry profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, was used.
+In order to fully parametrize the Jerry profile so as to use it in our simulations, we needed to match the stellar and halo mass data from the Kulier et al simulations, to the velocity dispersion at the galaxy's effective radius.
+In Kulier's simulations, a galaxy's effective radius $R_{e}$ and velocity dispersion $\sigma(R_e)$ at the effective radius are:
+\begin{equation}
+R_{e} = 2.5 kpc\left(\frac{M_*}{10^{11}M_{\odot}}\right)^{0.73}(1+z)^{-0.98}
+\end{equation}
+\begin{equation}
+\sigma(R_{e}) = 190km/s\left(\frac{M_{*}}{10^{11}M_{\odot}}\right)^{0.2}(1+z)^{0.47}
+\end{equation}
+
+Given the galaxy's stellar mass $M_{*}$ at redshift z from Kulier's simulations, we can calculate the effective radius and velocity dispersion.
+We can then equate these values to the analytic expressions for $\sigma(R_{e})$ in the Jerry profile.
+Using a core radius $r_c$ = 100, we can solve for the halo radius $r_h$ using a simple recursive Newton method.
+Whether $\sigma_{near}$ or $\sigma_{far}$ is used is determined by whether $R_e$ is less than or greater than $\sqrt{r_c r_h}$.
 

### 2016-08-13 paper.tex
worked on Simulation Setup section.

@@
 \begin{itemize}
-\item It must take into account baryonic mater
+\item It must take into account baryonic matter
 \item It must have a finite density in the center out to a scale radius
@@
 In Kulier's simulations, a galaxy's effective radius $R_{e}$ and velocity dispersion $\sigma(R_e)$ at the effective radius are:
-\begin{equation}
+\begin{equation} \label{re}
 R_{e} = 2.5 kpc\left(\frac{M_*}{10^{11}M_{\odot}}\right)^{0.73}(1+z)^{-0.98}
 \end{equation}
-\begin{equation}
+\begin{equation} \label{sig}
 \sigma(R_{e}) = 190km/s\left(\frac{M_{*}}{10^{11}M_{\odot}}\right)^{0.2}(1+z)^{0.47}
@@
 Injection, merging, escape, effective radius, set of galaxies
+
+Using the merger tree data, orbiting black holes were injected into its host galaxy at redshift z, at a distance from the galactic center of $R_{e}$ (Eqn.
+\ref{re}).
+Their initial velocity was arbitrarily chosen to be circular, $v_c = \sqrt{M(R_e)/R_e}$, with $v_x$, $v_y$, and $v_z$ randomly chosen.
 

### 2016-08-25 paper.tex
added plots

@@
 \section{Methods}\label{sec:methods}
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_1.png}
+\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_65.png}\\
+\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_187.png}
+\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_217.png}\\
+\caption{default}
+\label{default}
+\end{center}
+\end{figure*}
 
@@
 \section{Results}\label{sec:results}
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_1.png}
+\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_65.png}\\
+\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_187.png}
+\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_217.png}\\
+\caption{default}
+\label{default}
+\end{center}
+\end{figure*}
 
 \subsection{Mergers}
-
-\begin{figure}
-\centering
-%\includegraphics[width=0.45\textwidth]{plots/plot1.png}
-\caption{This is a caption.}
-\label{this_is_a_label}
-\end{figure}
 
@@
 \subsection{Stalling SMBHs in the halo}
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{plots/t_at_center_histogram_gal_1.png}
+\includegraphics[width=0.45\textwidth]{plots/t_at_center_histogram_gal_65.png}\\
+\includegraphics[width=0.45\textwidth]{plots/t_at_center_histogram_gal_187.png}
+\includegraphics[width=0.45\textwidth]{plots/t_at_center_histogram_gal_217.png}\\
+\caption{default}
+\label{default}
+\end{center}
+\end{figure*}
 

### 2016-08-26 paper.tex
added new plots of radii over time

@@
 
+Note: we only inject the BHs into the simulation that have a $t_{fric}$ smaller than 100 times the Hubble time.
+
 \section{Results}\label{sec:results}
+\begin{figure*}[htbp]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{plots/radius_A.png}
+\includegraphics[width=0.45\textwidth]{plots/radius_B.png}\\
+\includegraphics[width=0.45\textwidth]{plots/radius_C.png}
+\includegraphics[width=0.45\textwidth]{plots/radius_D.png}\\
+\caption{default}
+\label{default}
+\end{center}
+\end{figure*}
+
 \begin{figure*}[htbp]
@@
 \subsection{Mergers}
+\noindent A: two mergers early on, and then two more at around 10-12 Gyr\\
+B: 4 mergers across the final 8 Gyr\\
+C: two mergers in the final Gyrs\\
+D: ?\\
 
 \subsection{Ejections}
+No complete ejections, but kicks to higher energy orbits.
+\noindent A: one in a three-body encoutner\\
+B: 7-ish kicks, some in nearly 4-body encounters\\
+C: none\\
+D: ?\\
 
 \subsection{Stalling SMBH binaries}
+A: two periods of BH binary in center for > Gyr, up to 6 Gyr\\
+B: two short periods of BHBs\\
+C: 2 classic BHB periods of about 1 Gyr each\\
+D: ?
 
@@
 \end{figure*}
+
+A: 95\% never make it into the central kpc\\
+B: still about 90\% are in the halo\\
+C: \\
+D: ?
 

### 2016-09-15 paper.tex
added figure for BH masses
Added tables of merger results

@@
 \usepackage{babel}
+%\usepackage{siunitx}
+%\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
 \usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
 \usepackage[all]{hypcap}
-%\usepackage{siunitx}
 
@@
 Since the raw data was given in terms of redshift, we converted redshift to time with the help of a 'cosmology calculator', courtesy of Ned Wright and James Schombert (\url{http://www.astro.ucla.edu/~wright/CosmoCalc.html}).
-We chose three galaxies to run our simulations.
+We chose four galaxies to run our simulations.
 The galaxies were chosen using the following basic criteria:
@@
 
+\subsection{Description of Simulations}
+\begin{table}
+\caption{Merger Results}
+\begin{tabular}{c c c c}
+\hline\hline \\
+Galaxy & Orbiting BHs & $t_{fric}<100*t_H$ & Simulation Mergers \\
+A & 206 & 19 & 4 \\
+B & 29 & 12 & 4 \\
+C & 3 & 3 & 2 \\
+D & 4 & 4 & 2 \\
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{Galaxies used in Simulation}
+\begin{tabular}{c| c c| c c| c c|}
+\hline\hline \\
+& \multicolumn{2}{c}{$M_{gal}$ [$M_{\odot}$]} & 
+\multicolumn{2}{c}{$M_{*}$ [$M_{\odot}$]} & 
+\multicolumn{2}{c}{$M_{BH}$ [$M_{\odot}$]} \\
+Galaxy & Init & Final & Init & Final & Init & Final \\
+A & $7.42\mathrm{e}{11}$ & $1.09\mathrm{e}{14}$  & $1.22\mathrm{e}{11}$ & $1.75\mathrm{e}{13}$ & $4.80\mathrm{e}{06}$ & $2.19\mathrm{e}{09}$\\
+B & $1.11\mathrm{e}{12}$ & $3.41\mathrm{e}{13}$ & $1.80\mathrm{3}{11}$ & $5.58\mathrm{e}{12}$ & $1.94\mathrm{e}{08}$ & $1.46\mathrm{e}{09}$\\
+C & $7.23\mathrm{e}{10}$ & $3.48\mathrm{e}{12}$ & $1.18\mathrm{e}{10}$ & $5.68\mathrm{e}{11}$ & $9.47\mathrm{e}{04}$ & $2.70\mathrm{e}{08}$\\
+D & $3.92\mathrm{e}{10}$ & $1.34\mathrm{e}{12}$ & $6.47\mathrm{e}{9}$ & $2.20\mathrm{e}{11}$ & $9.95\mathrm{e}{05}$ & $8.32\mathrm{e}{07}$\\
+\end{tabular}
+\end{table}
+
 \section{Results}\label{sec:results}
@@
 \subsection{Mergers}
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{plots/masses_ABCD.png}
+\caption{default}
+\label{default}
+\end{center}
+\end{figure}
+
 \noindent A: two mergers early on, and then two more at around 10-12 Gyr\\

### 2016-09-18 paper.tex
added some text in the intro, modified the tables

--- 2016-08-26 paper.tex
@@
 \section{Introduction}\label{sec:introduction}
+A majority of all galaxies with masses $>10^8\msun$ at $z=0$ are believed to host super-massive black holes (SMBHs) in their cores.
+In a $\Lambda$CDM universe, galaxies at the high end of the galaxy-mass function are merger products of tens to hundreds of such massive galaxies.
+Even if only a small fraction of merging galaxies hosted an SMBH in their core at the time of merging, it is reasonable to assume that, during a Hubble time of continuous growth, these galaxies they will have substantial phases in which they contain two or more SMBHs at the same time.
+
+Here we look at the merger history of four exemplary galaxies across the galaxy mass spectrum extracted from a cosmological simulation of hierarchical structure formation.
+We investigate how, after merging with incoming galaxies, SMBHs diffuse into the cores of the hosts and interact with the resident black hole.
+We show that gravitational interactions of multiple SMBHs is most probable in high-mass galaxies with $10^{12}<M/\msun < 10^{13}$.
+Galaxies with lower masses  have too few mergers with SMBH hosting galaxies.
+Galaxies with higher masses tend to be too extended, making dynamical friction processes inefficient and hence failing to drive SMBHs into the host galaxy core.
+
+This paper is organized as follows: in Section \ref{sec:methods} we are going to describe the cosmological simulation from which we use the merger history to setup our idealized numerical simulations.
+We present the few-body integration code, \textsc{AR-Chain} that we used for our simulations of SMBH dynamics, and the modifications we made to this code in order to deal with a host galaxy's gravitational potential.
+In Section \ref{sec:results}, we show the results of our four exemplary simulations of galaxies growing with time and acquiring new SMBHs.
+We analyze how the SMBHs are driven into the core of their new host galaxies and how interaction with the host black hole leads to near-ejections or mergers.
+The final Section \ref{sec:conclusions} contains a discussion of the result and our conclusions.
 
@@
 \subsection{Merger tree}
-Our merger tree data came from the SMBH evolution simulations of \citet{2015ApJ...799..178K}, which used the large-scale hydrodynamical galaxy simulations outlined by \citet{2011ApJ...741...99C}, \citet{2011ApJ...742L..33C}, \citet{2012ApJ...753...17C}, \citet{2012ApJ...748..121C} and \citet{2013ApJ...770..139C}.
+Our merger tree data came from the SMBH evolution simulations of \citet{2015ApJ...799..178K}, which used the large-scale hydrodynamical galaxy simulations outlined in \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C}.
 The following cosmological parameters were used in their simulation:   $\Omega_M = 0.28$, $\Omega_b = 0.046$, $\Omega_\Lambda = 0.72$, $\sigma_8 = 0.82$, $H_0 = 100h^{-1}Mpc^{-1} = 70 km s^{-1} Mpc^{-1}$, and $n = 0.96$.
@@
 
+\subsection{Description of Simulations}
+\begin{table*}
+\centering
+\caption{Galaxy characteristics}
+\begin{tabular}{c| c c| c c| c c}
+ & \multicolumn{2}{c}{$M_{gal}$ [$M_{\odot}$]} & 
+\multicolumn{2}{c}{$M_{*}$ [$M_{\odot}$]} & 
+\multicolumn{2}{c}{$M_{BH}$ [$M_{\odot}$]} \\
+\hline
+Galaxy & Init & Final & Init & Final & Init & Final \\
+ \hline
+A & $7.42\times10^{11}$ & $1.09\times10^{14}$  & $1.22\times10^{11}$ & $1.75\times10^{13}$ & $4.80\times10^{6}$ & $2.19\times10^{9}$\\
+B & $1.11\times10^{12}$ & $3.41\times10^{13}$ & $1.80\mathrm{3}{11}$ & $5.58\times10^{12}$ & $1.94\times10^{8}$ & $1.46\times10^{9}$\\
+C & $7.23\times10^{10}$ & $3.48\times10^{12}$ & $1.18\times10^{10}$ & $5.68\times10^{11}$ & $9.47\times10^{4}$ & $2.70\times10^{8}$\\
+D & $3.92\times10^{10}$ & $1.34\times10^{12}$ & $6.47\times10^{9}$ & $2.20\times10^{11}$ & $9.95\times10^{5}$ & $8.32\times10^{7}$\\
+\end{tabular}
+\end{table*}
+
 \section{Results}\label{sec:results}
+\begin{table*}
+\centering
+\caption{SMBH statistics}
+\begin{tabular}{c| c |c |c}
+Galaxy & Infalling SMBHs & SMBHs with $t_{fric}<100\,t_H$ & Mergers \\
+\hline
+A & 206 & 19 & 4 \\
+B & 29 & 12 & 4 \\
+C & 3 & 3 & 2 \\
+D & 4 & 4 & 2 \\
+\end{tabular}
+\end{table*}
+
 \begin{figure*}[htbp]

### 2018-04-25 paper.tex
Brought this version of paper up to date with version on Authorea.

@@
 
-\author{Charles Zivancev\altaffilmark{1}, Andreas H.W. K\"upper\altaffilmark{1,2}, Jeremiah P. Ostriker\altaffilmark{1,3}}
+\author{Charles Zivancev\altaffilmark{1}, Jeremiah P. Ostriker\altaffilmark{1,3}, Andreas H.W. K\"upper\altaffilmark{1,2}}
 \altaffiltext{1}{Department of Astronomy, Columbia University, 550 West 120th Street, New York, NY 10027, USA}
@@
 In a $\Lambda$CDM universe, galaxies at the high end of the galaxy-mass function are merger products of tens to hundreds of such massive galaxies.
-Even if only a small fraction of merging galaxies hosted an SMBH in their core at the time of merging, it is reasonable to assume that, during a Hubble time of continuous growth, these galaxies they will have substantial phases in which they contain two or more SMBHs at the same time.
+Even if only a small fraction of merging galaxies hosted an SMBH in their core at the time of merging, it is reasonable to assume that, during a Hubble time of continuous growth, these galaxies will have substantial phases in which they contain two or more SMBHs at the same time.
 
@@
 We investigate how, after merging with incoming galaxies, SMBHs diffuse into the cores of the hosts and interact with the resident black hole.
-We show that gravitational interactions of multiple SMBHs is most probable in high-mass galaxies with $10^{12}<M/\msun < 10^{13}$.
+We show that gravitational interactions of multiple SMBHs are most probable in high-mass galaxies with $10^{12}<M/\msun < 10^{13}$.
 Galaxies with lower masses  have too few mergers with SMBH hosting galaxies.
@@
 
-This paper is organized as follows: in Section \ref{sec:methods} we are going to describe the cosmological simulation from which we use the merger history to setup our idealized numerical simulations.
+This paper is organized as follows: in Section \ref{sec:methods} we are going to describe the cosmological simulation from which we use the merger history to set up our idealized numerical simulations.
 We present the few-body integration code, \textsc{AR-Chain} that we used for our simulations of SMBH dynamics, and the modifications we made to this code in order to deal with a host galaxy's gravitational potential.
@@
 \caption{default}
-\label{default}
+\label{default1}
 \end{center}
@@
 One file was centered around SMBHs at each redshift slice, giving information for the black hole's seed mass, accreted and seed mass, its host galaxy, the stellar mass in its host galaxy, and time after z=4 at which the BH entered the host galaxy (if it is not the central BH).
-The other file was centered on galaxies at each redshift slice, prociding information on the galaxyies' stellar mass, dark matter mass, its central BH, and any orbiting black holes within the galaxy.
+The other file was centered on galaxies at each redshift slice, providing information on the galaxies' stellar mass, dark matter mass, central BH, and any orbiting black holes within the galaxy.
 
@@
 Since our study is more interested SMBH mergers at the center of galaxies, dynamical friction, and hence baryonic matter, was of considerable importance.
-Therefore, NFW background potential was less suitable for our application.
+Therefore, the NFW background potential was less suitable for our application.
 
@@
 
-For our simulations, the Jerry profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, was used.
-In order to fully parametrize the Jerry profile so as to use it in our simulations, we needed to match the stellar and halo mass data from the Kulier et al simulations, to the velocity dispersion at the galaxy's effective radius.
+For our simulations, the Ostriker-Stone profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, was used.
+In order to fully parametrize this profile so as to use it in our simulations, we needed to match the stellar and halo mass data from the Kulier et al simulations, to the velocity dispersion at the galaxy's effective radius.
 In Kulier's simulations, a galaxy's effective radius $R_{e}$ and velocity dispersion $\sigma(R_e)$ at the effective radius are:
@@
 Given the galaxy's stellar mass $M_{*}$ at redshift z from Kulier's simulations, we can calculate the effective radius and velocity dispersion.
-We can then equate these values to the analytic expressions for $\sigma(R_{e})$ in the Jerry profile.
+We can then equate these values to the analytic expressions for $\sigma(R_{e})$ in the Ostriker-Stone profile.
 Using a core radius $r_c$ = 100, we can solve for the halo radius $r_h$ using a simple recursive Newton method.
@@
 Weak encounters with background stars will let the SMBHs diffuse through phase space while they are orbiting within the gravitational potential of the galaxy.
+The diffusion can be expressed as change in velocity of an SMBH by $\Delta \vec{v}$ per unit time.
+We can split this change into a component along the direction of motion of the SMBH, and one perpendicular to that.
+Following \citet{Binney08}, the diffusion coefficients can be expressed as
+\begin{eqnarray}
+D[\Delta v_\parallel] & = & -\frac{4\pi G^2\rho(r)M_\bullet\ln\Lambda}{\sigma^2}f(\chi),\label{eq:df}\\
+D[(\Delta v_\parallel)^2] & = & \frac{4\sqrt{2}\pi G^2\rho(r)M_\bullet\ln\Lambda}{\sigma}\frac{f(\chi)}{\chi},\\
+D[(\Delta \vec{v}_\bot)^2] & = & \frac{4\sqrt{2}\pi G^2\rho(r)M_\bullet\ln\Lambda}{\sigma}\left[\frac{\mbox{erf}(\chi)-f(\chi)}{\chi}\right],
+\end{eqnarray} 
+where $\Delta v_\parallel \equiv \Delta \vec{v}\cdot\vec{v}/v$ is the velocity change in direction of motion, and $\Delta \vec{v}_\bot \equiv \Delta \vec{v} - \Delta v_\parallel \cdot\vec{v}/v$ is the velocity change perpendicular to the direction of motion.
+Here, $M_\bullet$ is the mass of the black hole, and $\chi = \frac{v}{\sqrt{2}\sigma(r)}$.
+The function $f(\chi)$ is given by
+\begin{equation}
+f(\chi) = \frac{1}{2\chi^2}\left(\mbox{erf}(\chi)-\frac{2\chi}{\sqrt{\pi}}\exp\left(-\chi^2\right)\right).
+\end{equation}
+We approximate the factor $\Lambda$ in the Coulomb logarithm as
+\begin{equation}
+\Lambda = \left(\frac{M_{NSC}}{M_\bullet}\right)\left(\frac{r}{r_h}\right).
+\end{equation}
+We can identify Eq.~\ref{eq:df} as the dynamical friction term, that is, if we assumed $D[(\Delta v_\parallel)^2]  = D[(\Delta \vec{v}_\bot)^2]  = 0$, we would get Chandrasekhar's dynamical friction formula.
+The second term introduces a variance of the friction term, and even allows the SBHs to be accelerated when the velocity of a SBH gets sufficiently small.
+The third term introduces a change in velocity perpendicular to the direction of motion of the SBH.
+It is a randomly oriented vector, and hence causes the SBHs to execute a random walk in phase space.
+The last two terms will establish that the SBHs are ultimately in energy equipartition with the background stars.
+The velocity changes $\Delta v_\parallel$ and $\Delta\vec{v}_\bot$ per unit time $\Delta t$ can be computed with the above equations.
+Both changes are normal distributed, where the mean, $\mu$, and the variance, $\Sigma$, of the distributions are given by
+\begin{eqnarray}
+\mu_\parallel &=& D[\Delta v_\parallel]\Delta t,\\
+\Sigma_\parallel &=& D[(\Delta v_\parallel)^2]\Delta t,\\
+\mu_\bot &=& 0,\\
+\Sigma_\bot &=& D[(\Delta \vec{v}_\bot)^2]\Delta t.
+\end{eqnarray}
+We compute the diffusion coefficients for each black hole at each time step, and modify its velocity on a Monte Carlo basis.
+For each time step we draw a random orientation before adding the perpendicular velocity change to the respective SBH.
+Hence, the SBH's modified velocity, $v_f$, is computed using
+\begin{eqnarray}
+\vec{v}_f &=& \vec{v}_0 + \Delta v_\parallel \hat{v}_\parallel + \Delta v_\bot \hat{v}_\bot,\\
+\Delta v_\parallel &=& \mathcal{N}(\mu_\parallel, \Sigma_\parallel),\\
+\Delta v_\bot &=& \mathcal{N}(\mu_\bot, \Sigma_\bot).
+\end{eqnarray}
+The change of energy, $\mbox{d}E_{BH}$, of the orbiting black hole due to phase-space diffusion is given back to the stellar background potential, with $\mbox{d}E = -\mbox{d}E_{BH}$.
+As a consequence of this energy transfer, inspiralling black holes will cause an expansion of the NSC.
+For this purpose we calculate the change in potential energy, $\mbox{d}W$, of the stellar system using
+\begin{eqnarray}
+E &=& T + W = \frac{1}{2}W,\\
+\mbox{d}W &=& -2\,\mbox{d}E_{BH},
+\end{eqnarray}
+where we made use of the virial theorem $2T+W =0$.
+With this change in potential energy we can calculate a new radius for the stellar background potential at each integration step.
+For the Plummer sphere the new scale radius can be calculated as
+\begin{equation}
+a_{new} = a\left(1+\frac{32a\,\mbox{d}W}{3\pi GM_{NSC}^2}\right)^{-1}.
+\end{equation}
 
@@
 We include gravitational wave recoils following the prescription outlined in \citet{2015ApJ...799..178K}, which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.
-To save computational time, we assume that a merger will be inevitable when the separation between two SBHs gets smaller than 10\,000 Schwarzschild radii.
+To save computational time, we assume that a merger will be inevitable when the separation between two SBHs gets smaller than 1.0 Schwarzschild radii.
 At the moment of the merger, we assume that the spin vectors of the two SBHs are randomly aligned.
@@
 \caption{default}
-\label{default}
+\label{default2}
 \end{center}
@@
 \caption{default}
-\label{default}
+\label{default3}
 \end{center}
@@
 \caption{default}
-\label{default}
+\label{default4}
 \end{center}
@@
 
-\noindent A: two mergers early on, and then two more at around 10-12 Gyr\\
-B: 4 mergers across the final 8 Gyr\\
-C: two mergers in the final Gyrs\\
-D: ?\\
+\noindent A: two mergers early on, and then two more at around 10-12 Gyr
+B: 4 mergers across the final 8 Gyr
+C: two mergers in the final Gyrs
+D: ?
 
@@
 \caption{default}
-\label{default}
+\label{default5}
 \end{center}

### 2018-04-26 paper.tex
Worked on merger tree data section.  Added bibliographic references.

@@
 \subsection{Merger tree}
-Our merger tree data came from the SMBH evolution simulations of \citet{2015ApJ...799..178K}, which used the large-scale hydrodynamical galaxy simulations outlined in \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C}.
-The following cosmological parameters were used in their simulation:   $\Omega_M = 0.28$, $\Omega_b = 0.046$, $\Omega_\Lambda = 0.72$, $\sigma_8 = 0.82$, $H_0 = 100h^{-1}Mpc^{-1} = 70 km s^{-1} Mpc^{-1}$, and $n = 0.96$.
-The SMBHs were evolved from $4\geq z \geq 0$.
+Our merger tree data came from two sources:
+\begin{itemize}
+\item Galactic merger tree data from simulations of \citet{2012MNRAS.425..641L} (hereafter Lackner12), which was centered on galaxies at each redshift slice, providing information on the galaxies' stellar mass, dark matter mass, central BH, and any orbiting black holes within the galaxy.
+\item SMBH evolution simulations of \citet{2015ApJ...799..178K} (hereafter Kulier15), which used the large-scale hydrodynamical galaxy simulations outlined in \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C}.
+The data was centered around SMBHs at each redshift slice between $z=4$ to $z=0$, giving information for each SMBH's seed mass, accreted and seed mass, its host galaxy (categorically defined), the stellar mass in its host galaxy, and time after z=4 at which the BH entered the host galaxy (if it is not the central BH).
+\end{itemize}
 
-The merger tree data was in two primary files.
-One file was centered around SMBHs at each redshift slice, giving information for the black hole's seed mass, accreted and seed mass, its host galaxy, the stellar mass in its host galaxy, and time after z=4 at which the BH entered the host galaxy (if it is not the central BH).
-The other file was centered on galaxies at each redshift slice, providing information on the galaxies' stellar mass, dark matter mass, central BH, and any orbiting black holes within the galaxy.
+The following cosmological parameters were used in the simulations of both Lackner12 and Kulier15:   $\Omega_M = 0.28$, $\Omega_b = 0.046$, $\Omega_\Lambda = 0.72$, $\sigma_8 = 0.82$, $H_0 = 100h^{-1}Mpc^{-1} = 70 km s^{-1} Mpc^{-1}$, and $n = 0.96$.
+
+Lackner12 noted that the efficiency of star formation in their simulations, defined as $f_*=M_*/M_{DM}(\Omega_{DM}/\Omega_b)$, was approximately 0.6.
+Compared with the expected range of $0.10 \lessapprox f_* \lessapprox 0.15$ that they referenced from \citet{2012ApJ...746...95L}, their stellar masses were a factor of roughly 4 times greater.
+In order to adjust our stellar masses to levels more in line with current observations, we used observational data from \citet{2018AstL...44....8K}, in particular Figure 11.
+(SHOULD I ADD PLOT OF OUR ORIGINAL STELLAR DATA?
+THE PLOT FROM KRAVTSOV WAS RECREATED BY EYEBALL WITH A FEW STRAIGHT LINES TO APPROXIMATE HIS CURVE.
+HOW TO INCORPORATE THAT?)
 
@@
 It includes relativistic post-Newtonian terms up to order PN2.5 \citep{2008AJ....135.2398M}.
+
+As in the simulations from Kulier12, the SMBHs were evolved from $z=4$ to $z=0$.
 
@@
 
-The authors would like to thank Andrea Kulier for providing merger tree data.
+The authors would like to thank Andrea Kulier and Claire Lackner for providing merger tree data.
 AHWK acknowledges support by NASA through Hubble Fellowship grant HST-HF-51323.01-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS 5-26555.

### 2018-05-07 paper.tex
Worked on Methods section.  Moved some things around.
Worked on Methods section.  Moved some things around.

@@
 \section{Methods}\label{sec:methods}
-\begin{figure*}[htbp]
-\begin{center}
-\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_1.png}
-\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_65.png}\\
-\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_187.png}
-\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_217.png}\\
-\caption{default}
-\label{default1}
-\end{center}
-\end{figure*}
+%\begin{figure*}[htbp]
+%\begin{center}
+%\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_1.png}
+%\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_65.png}\\
+%\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_187.png}
+%\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_217.png}\\
+%\caption{default}
+%\label{default1}
+%\end{center}
+%\end{figure*}
+
+\subsection{Overview of simulation}
+Our simulations focused on elliptical galaxies with central SMBHs.
+The galaxies were given a background potential based on the Ostriker-Stone profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form.
+The galaxies were evolved between $0 < z < 4$.
+Orbiting black holes were periodically introduced into the "host" galaxy and their dynamical interaction with the background potential and central SMBH were followed.
+
+For the numerical simulations presented here, we used a modified version of the algorithmic chain integrator \textsc{AR-Chain} developed by \citet{2006MNRAS.372..219M}.
+It uses algorithmic chain regularization for high-precision integration of few-body dynamics, and is capable of handling velocity-dependent forces efficiently.
+It includes relativistic post-Newtonian terms up to order PN2.5 \citep{2008AJ....135.2398M}.
 
@@
 \item SMBH evolution simulations of \citet{2015ApJ...799..178K} (hereafter Kulier15), which used the large-scale hydrodynamical galaxy simulations outlined in \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C}.
-The data was centered around SMBHs at each redshift slice between $z=4$ to $z=0$, giving information for each SMBH's seed mass, accreted and seed mass, its host galaxy (categorically defined), the stellar mass in its host galaxy, and time after z=4 at which the BH entered the host galaxy (if it is not the central BH).
+The data was centered around SMBHs at each redshift slice between $0 < z < 4$, giving information for each SMBH's seed mass, accreted and seed mass, its host galaxy (categorically defined), the stellar mass in its host galaxy, and time after z=4 at which the BH entered the host galaxy (if it is not the central BH).
 \end{itemize}
+
+SHOULD I INCLUDE PLOTS AND/OR HISTOGRAMS OF THE DISTRIBUTION OF GALAXY MASSES, STELLAR MASSES, ETC AT Z=0?
 
@@
 \begin{itemize}
-\item The galaxies had to exist through the entire simulation, from $z=4$ to $z=0$.
+\item The galaxies had to exist through the entire simulation ($0 < z < 4$).
 \item They had to have a central SMBH.
@@
 \item We ordered the galaxies by decreasing mass at $z=0$, and starting with the largest tier of mass (~$10^{14} M_{\odot}$), we spaced their masses by approximately 1-2 orders of magnitude.
+We chose the four largest galaxies that also satisfied the above criteria.
 \end{itemize}
 
-After finding our subject galaxies, we curve-fit their total masses as a function of time using a simple $7^{th}$-order polynomial fit, so as to be able to use their masses in the AR-Chain code.
+After finding our subject galaxies, we curve-fit their total masses as a function of time using a $7^{th}$-order polynomial fit, so as to be able to use their masses in the AR-Chain code.
 Additionally, we curve-fit each galaxy's accreted+seed central black hole mass to exponential functions of time.
@@
 
-For the numerical simulations presented here, we used a modified version of the algorithmic chain integrator \textsc{AR-Chain} developed by \citet{2006MNRAS.372..219M}.
-It uses algorithmic chain regularization for high-precision integration of few-body dynamics, and is capable of handling velocity-dependent forces efficiently.
-It includes relativistic post-Newtonian terms up to order PN2.5 \citep{2008AJ....135.2398M}.
-
-As in the simulations from Kulier12, the SMBHs were evolved from $z=4$ to $z=0$.
-
 \subsubsection{Galaxy background potential}
-The simulations from which we obtained the merger tree data considered only dark matter distributions and were run using the Navarro-Frenk-White (NFW) profile described in \citet{1997ApJ...490..493N}.
+The simulations from which we obtained the merger tree data considered only dark matter distributions and were run using the Navarro-Frenk-White (NFW) profile \citet{1997ApJ...490..493N}.
 Since our study is more interested SMBH mergers at the center of galaxies, dynamical friction, and hence baryonic matter, was of considerable importance.

### 2018-05-17 paper.tex
Made some of the changes to paper that Jerry marked up.  Also added folded for papers that we reference.

@@
 A majority of all galaxies with masses $>10^8\msun$ at $z=0$ are believed to host super-massive black holes (SMBHs) in their cores.
-In a $\Lambda$CDM universe, galaxies at the high end of the galaxy-mass function are merger products of tens to hundreds of such massive galaxies.
+In a $\Lambda$CDM universe, galaxies at the high end of the galaxy-mass function are merger products of numerous such massive galaxies.
 Even if only a small fraction of merging galaxies hosted an SMBH in their core at the time of merging, it is reasonable to assume that, during a Hubble time of continuous growth, these galaxies will have substantial phases in which they contain two or more SMBHs at the same time.
@@
 We investigate how, after merging with incoming galaxies, SMBHs diffuse into the cores of the hosts and interact with the resident black hole.
-We show that gravitational interactions of multiple SMBHs are most probable in high-mass galaxies with $10^{12}<M/\msun < 10^{13}$.
+We show that gravitational interactions of multiple SMBHs are most probable in high-mass galaxies with $10^{12} \msun < M < 10^{13} \msun$.
 Galaxies with lower masses  have too few mergers with SMBH hosting galaxies.
-Galaxies with higher masses tend to be too extended, making dynamical friction processes inefficient and hence failing to drive SMBHs into the host galaxy core.
+Galaxies with higher masses are more extended, making dynamical friction processes less efficient and hence failing to drive SMBHs into the host galaxy core.
+Several papers (\citet{2018arXiv180403143I}, \citet{2014ApJ...789..156M})have shown that if all galaxy mergers lead to black hole mergers, the resulting PTA signal would be roughly twice the current limits.
+One paper (\citet{2018MNRAS.473.3410R}) has indicated that dynamical interactions among multiple black holes, which eject a non-negligible fraction of the mass, may solve this problem.
+The present paper also addresses this purported dynamical solution.
 
@@
 Starting with this data, we plotted the galaxy masses as a function of time.
-Since the raw data was given in terms of redshift, we converted redshift to time with the help of a 'cosmology calculator', courtesy of Ned Wright and James Schombert (\url{http://www.astro.ucla.edu/~wright/CosmoCalc.html}).
+Since the raw data was given in terms of redshift, we converted redshift to time.
 We chose four galaxies to run our simulations.
@@
 
-For our simulations, the Ostriker-Stone profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, was used.
+For our simulations, the Stone-Ostriker profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, was used.
+It is essentially an analytic form of a finite, cored isothermal mass distribution.
 In order to fully parametrize this profile so as to use it in our simulations, we needed to match the stellar and halo mass data from the Kulier et al simulations, to the velocity dispersion at the galaxy's effective radius.
@@
 Given the galaxy's stellar mass $M_{*}$ at redshift z from Kulier's simulations, we can calculate the effective radius and velocity dispersion.
-We can then equate these values to the analytic expressions for $\sigma(R_{e})$ in the Ostriker-Stone profile.
+We can then equate these values to the analytic expressions for $\sigma(R_{e})$ in the Stone-Ostriker profile.
 Using a core radius $r_c$ = 100, we can solve for the halo radius $r_h$ using a simple recursive Newton method.

### 2018-05-18 paper.tex
Made some more changes.

@@
 The galaxies were evolved between $0 < z < 4$.
-Orbiting black holes were periodically introduced into the "host" galaxy and their dynamical interaction with the background potential and central SMBH were followed.
+Orbiting black holes were periodically introduced into the "host" galaxy and their dynamical interaction with the background potential and central SMBH were followed, as described further below.
 
@@
 
+The merger tree data from Lackner12 and Kulier15 provided 1,830 galaxies in total.  However, not all the galaxies were useful for our simulations.  We placed further:
+\begin{itemize}
+\item The galaxies had to exist through the entire simulation ($0 < z < 4$).
+\item They had to have a central SMBH.
+\item We ordered the galaxies by decreasing mass at $z=0$, and starting with the largest tier of mass (~$10^{14} M_{\odot}$), we spaced their masses by approximately 1-2 orders of magnitude.
+We chose the four largest galaxies that also satisfied the above criteria.
+\end{itemize}
+
+After finding our subject galaxies, we curve-fit their total masses as a function of time using a $7^{th}$-order polynomial fit, so as to be able to use their masses in the AR-Chain code.
+Additionally, we curve-fit each galaxy's accreted+seed central black hole mass to exponential functions of time.
+
 The following cosmological parameters were used in the simulations of both Lackner12 and Kulier15:   $\Omega_M = 0.28$, $\Omega_b = 0.046$, $\Omega_\Lambda = 0.72$, $\sigma_8 = 0.82$, $H_0 = 100h^{-1}Mpc^{-1} = 70 km s^{-1} Mpc^{-1}$, and $n = 0.96$.
@@
 
-Starting with this data, we plotted the galaxy masses as a function of time.
-Since the raw data was given in terms of redshift, we converted redshift to time.
-We chose four galaxies to run our simulations.
-The galaxies were chosen using the following basic criteria:
-\begin{itemize}
-\item The galaxies had to exist through the entire simulation ($0 < z < 4$).
-\item They had to have a central SMBH.
-\item They had to have at least XXX orbiting black holes.
-\item We ordered the galaxies by decreasing mass at $z=0$, and starting with the largest tier of mass (~$10^{14} M_{\odot}$), we spaced their masses by approximately 1-2 orders of magnitude.
-We chose the four largest galaxies that also satisfied the above criteria.
-\end{itemize}
-
-After finding our subject galaxies, we curve-fit their total masses as a function of time using a $7^{th}$-order polynomial fit, so as to be able to use their masses in the AR-Chain code.
-Additionally, we curve-fit each galaxy's accreted+seed central black hole mass to exponential functions of time.
-
 \subsection{AR-Chain code}
@@
 \subsubsection{Galaxy background potential}
-The simulations from which we obtained the merger tree data considered only dark matter distributions and were run using the Navarro-Frenk-White (NFW) profile \citet{1997ApJ...490..493N}.
+The simulations from which we obtained the merger tree data were run using the Navarro-Frenk-White (NFW) profile \citet{1997ApJ...490..493N}.
 Since our study is more interested SMBH mergers at the center of galaxies, dynamical friction, and hence baryonic matter, was of considerable importance.

### 2018-05-18 paper.tex
More modifications

@@
 The galaxies were given a background potential based on the Ostriker-Stone profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form.
-The galaxies were evolved between $0 < z < 4$.
+The galaxies were evolved from $4 > z > 0$.
 Orbiting black holes were periodically introduced into the "host" galaxy and their dynamical interaction with the background potential and central SMBH were followed, as described further below.
@@
 \item SMBH evolution simulations of \citet{2015ApJ...799..178K} (hereafter Kulier15), which used the large-scale hydrodynamical galaxy simulations outlined in \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C}.
-The data was centered around SMBHs at each redshift slice between $0 < z < 4$, giving information for each SMBH's seed mass, accreted and seed mass, its host galaxy (categorically defined), the stellar mass in its host galaxy, and time after z=4 at which the BH entered the host galaxy (if it is not the central BH).
+The data was centered around SMBHs at each redshift slice from $4 > z > 0$, giving information for each SMBH's seed mass, accreted and seed mass, its host galaxy (categorically defined), the stellar mass in its host galaxy, and time after z=4 at which the BH entered the host galaxy (if it is not the central BH).
 \end{itemize}
@@
 
-The merger tree data from Lackner12 and Kulier15 provided 1,830 galaxies in total.  However, not all the galaxies were useful for our simulations.  We placed further:
+The merger tree data from Lackner12 and Kulier15 provided 1,830 galaxies in total.  However, not all the galaxies were suitable for our simulations.  We placed further requirements as follows:
 \begin{itemize}
-\item The galaxies had to exist through the entire simulation ($0 < z < 4$).
-\item They had to have a central SMBH.
-\item We ordered the galaxies by decreasing mass at $z=0$, and starting with the largest tier of mass (~$10^{14} M_{\odot}$), we spaced their masses by approximately 1-2 orders of magnitude.
-We chose the four largest galaxies that also satisfied the above criteria.
+\item The galaxies had to exist through the entire simulation ($4 > z > 0$).  If they merged with other galaxies, they had to have been the "surviving" galaxy at each merger.
+\item They had to have accumulated orbiting black holes by z = 0.
 \end{itemize}
+
+The Kulier15 merger tree collected black holes entering galaxies during the simulation and noted the time after z=4 at which they entered their host galaxy.
+Nothing further was done with them, so each galaxy had a "running list" of other galaxies/BHs orbiting them at z=0.
+Clean up this paragraph.
 
@@
 
+\subsubsection{Galactic Stellar Mass Adjustment}
 Lackner12 noted that the efficiency of star formation in their simulations, defined as $f_*=M_*/M_{DM}(\Omega_{DM}/\Omega_b)$, was approximately 0.6.
@@
 In order to adjust our stellar masses to levels more in line with current observations, we used observational data from \citet{2018AstL...44....8K}, in particular Figure 11.
-(SHOULD I ADD PLOT OF OUR ORIGINAL STELLAR DATA?
-THE PLOT FROM KRAVTSOV WAS RECREATED BY EYEBALL WITH A FEW STRAIGHT LINES TO APPROXIMATE HIS CURVE.
-HOW TO INCORPORATE THAT?)
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{plots/stellar_to_halo_ratio.png}
+\caption{Original and rescaled stellar masses}
+\label{fig:stellar1}
+\end{center}
+\end{figure}
 

### 2018-05-21 paper.tex
Made some changes to Galaxy Background potential section.  Other smaller changes.

@@
 \subsubsection{Galaxy background potential}
-The simulations from which we obtained the merger tree data were run using the Navarro-Frenk-White (NFW) profile \citet{1997ApJ...490..493N}.
-Since our study is more interested SMBH mergers at the center of galaxies, dynamical friction, and hence baryonic matter, was of considerable importance.
-Therefore, the NFW background potential was less suitable for our application.
+For our simulations, the Stone-Ostriker profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form.
+It is essentially an analytic form of a finite, cored isothermal mass distribution:
+\begin{equation} \label{jerry}
+\rho(r) = \frac{\rho_c}{(1+r^2/r_{c}^2)(1+r^2/r_{h}^2)}
+\end{equation}
+Here $\rho_c$ is the central density, $r_c$ is the core radius, and $r_h$ is the outer halo radius.
 
-In considering a suitable potential-density pair, characteristics that were important were:
-\begin{itemize}
-\item It must take into account baryonic matter
-\item It must have a finite density in the center out to a scale radius
-\item Declining density that drops more sharply out to a second scale radius
-\item An even sharper decline in density beyond the second scale radius
-\item It must be easily parametrized and written in analytic, closed form
-\end{itemize}
-
-For our simulations, the Stone-Ostriker profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, was used.
-It is essentially an analytic form of a finite, cored isothermal mass distribution.
-In order to fully parametrize this profile so as to use it in our simulations, we needed to match the stellar and halo mass data from the Kulier et al simulations, to the velocity dispersion at the galaxy's effective radius.
-In Kulier's simulations, a galaxy's effective radius $R_{e}$ and velocity dispersion $\sigma(R_e)$ at the effective radius are:
+In order to parametrize this profile, $r_c$ was given an arbitrary initial value of 100 pc.
+To calculate $r_h$, we began by using the stellar mass to calculate the velocity dispersion at the galaxy's effective radius.
+In Kulier12, the galaxy's effective radius $R_{e}$ and velocity dispersion $\sigma(R_e)$ at the effective radius are:
 \begin{equation} \label{re}
@@
 
-Given the galaxy's stellar mass $M_{*}$ at redshift z from Kulier's simulations, we can calculate the effective radius and velocity dispersion.
-We can then equate these values to the analytic expressions for $\sigma(R_{e})$ in the Stone-Ostriker profile.
-Using a core radius $r_c$ = 100, we can solve for the halo radius $r_h$ using a simple recursive Newton method.
-Whether $\sigma_{near}$ or $\sigma_{far}$ is used is determined by whether $R_e$ is less than or greater than $\sqrt{r_c r_h}$.
+We can then equate the value for $\sigma({R_e})$ obtained from Equation \ref{sig} to the analytic expressions for $\sigma(R_{e})$ in the Stone-Ostriker profile (Eqns 9 and A1-A4).
+The only unknown is $r_h$, which we can solve for using a simple recursive Newton method.
+Whether $\sigma_{near}$ or $\sigma_{far}$ is used from Stone-Ostriker is determined by whether $R_e$ is less than or greater than $\sqrt{r_c r_h}$.
 
-\subsubsection{Phase-space diffusion}
+The central density, $\rho_c$, can be found from Equation 5 in Stone-Ostriker:
+\begin{equation} \label{rhoc}
+M_{tot} = \frac{2\pi^2r_{c}^2r_{h}^2\rho_c}{r_h+r_c},
+\end{equation}
+where $M_{tot}$ is the total dark matter mass.
+
+At each iteration in the code, $r_h$ is updated according to the stellar mass and Equations \ref{re} and \ref{sig}.
+The core radius, $r_c$, is recalculated only if an orbiting black hole gets within $r_c$.
+The work done by diffusion, as described in Section \ref{psd} is calculated, the total potential energy is updated, and $r_c$ is solved for from Equation 8 in Stone-Ostriker.
+
+\subsubsection{Phase-space diffusion} \label{psd}
 Weak encounters with background stars will let the SMBHs diffuse through phase space while they are orbiting within the gravitational potential of the galaxy.
@@
 We can split this change into a component along the direction of motion of the SMBH, and one perpendicular to that.
-Following \citet{Binney08}, the diffusion coefficients can be expressed as
+Following \citet{2008gady.book.....B}, the diffusion coefficients can be expressed as
 \begin{eqnarray}
@@
 The SMBHs can therefore merge via gravitational wave emission.
-We include gravitational wave recoils following the prescription outlined in \citet{2015ApJ...799..178K}, which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.
-To save computational time, we assume that a merger will be inevitable when the separation between two SBHs gets smaller than 1.0 Schwarzschild radii.
+We include gravitational wave recoils following the prescription outlined in Kulier15, which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.
+To save computational time, we assume that a merger will be inevitable when the separation between two SBHs gets smaller than 1.0 Schwarzschild radius.
 At the moment of the merger, we assume that the spin vectors of the two SBHs are randomly aligned.

### 2018-06-01 paper.tex
Added Jerry's additions to top of introduction
Added Jerry's additions to top of introduction.  Still need to merg it with the rest of the intro.

@@
 \section{Introduction}\label{sec:introduction}
+What is the ultimate fate of the supermassive black holes (SMBH) resident at the centers of all massive galaxies?
+For the galaxies themselves we know that mergers are frequent from the observed (ADD VAN DOKKUM PAPER) evolution of the size and mass of these systems.
+But assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2015ApJ...799..178K}, PRETONOS & OSTRIKER, SESANA, NATARJAN).
+But we do not often see multiple SMBHs at the centers of massive ellipticals.
+So, what does happen?
+What we argue in this paper is that as a result of the N-body interactions among the infalling black holes some are ejected, some remain in extended orbits and some (the few most massive ones) do in fact merge but we do not exceed the PTA limits, and the orbiting ones should be detectable via their ability to accrete gas and emit radiation.
+
 A majority of all galaxies with masses $>10^8\msun$ at $z=0$ are believed to host super-massive black holes (SMBHs) in their cores.
@@
 
-Here we look at the merger history of four exemplary galaxies across the galaxy mass spectrum extracted from a cosmological simulation of hierarchical structure formation.
+Here we look at the merger history of XX exemplary galaxies across the galaxy mass spectrum extracted from a cosmological simulation of hierarchical structure formation.
 We investigate how, after merging with incoming galaxies, SMBHs diffuse into the cores of the hosts and interact with the resident black hole.
@@
 Galaxies with higher masses are more extended, making dynamical friction processes less efficient and hence failing to drive SMBHs into the host galaxy core.
-Several papers (\citet{2018arXiv180403143I}, \citet{2014ApJ...789..156M})have shown that if all galaxy mergers lead to black hole mergers, the resulting PTA signal would be roughly twice the current limits.
+Several papers (\citet{2018arXiv180403143I}, \citet{2014ApJ...789..156M}) have shown that if all galaxy mergers lead to black hole mergers, the resulting PTA signal would be roughly twice the current limits.
 One paper (\citet{2018MNRAS.473.3410R}) has indicated that dynamical interactions among multiple black holes, which eject a non-negligible fraction of the mass, may solve this problem.
@@
 Following \citet{2008gady.book.....B}, the diffusion coefficients can be expressed as
-\begin{eqnarray}
-D[\Delta v_\parallel] & = & -\frac{4\pi G^2\rho(r)M_\bullet\ln\Lambda}{\sigma^2}f(\chi),\label{eq:df}\\
+\begin{eqnarray}\label{eq:df}
+D[\Delta v_\parallel] & = & -\frac{4\pi G^2\rho(r)M_\bullet\ln\Lambda}{\sigma^2}f(\chi),\\
 D[(\Delta v_\parallel)^2] & = & \frac{4\sqrt{2}\pi G^2\rho(r)M_\bullet\ln\Lambda}{\sigma}\frac{f(\chi)}{\chi},\\
@@
 \end{equation}
-We can identify Eq.~\ref{eq:df} as the dynamical friction term, that is, if we assumed $D[(\Delta v_\parallel)^2]  = D[(\Delta \vec{v}_\bot)^2]  = 0$, we would get Chandrasekhar's dynamical friction formula.
+We can identify Equation \ref{eq:df} as the dynamical friction term.
 The second term introduces a variance of the friction term, and even allows the SBHs to be accelerated when the velocity of a SBH gets sufficiently small.
@@
 The velocity changes $\Delta v_\parallel$ and $\Delta\vec{v}_\bot$ per unit time $\Delta t$ can be computed with the above equations.
-Both changes are normal distributed, where the mean, $\mu$, and the variance, $\Sigma$, of the distributions are given by
+Both changes are normally distributed, where the mean, $\mu$, and the variance, $\Sigma$, of the distributions are given by
 \begin{eqnarray}
@@
 \subsubsection{Gravitational wave recoils}
-The code \textsc{AR-Chain} includes PN terms up to order 2.5.
+The code \textsc{AR-Chain} includes post-Newtonian terms up to order 2.5.
 The SMBHs can therefore merge via gravitational wave emission.
@@
 \subsection{Simulation setup}
-Injection, merging, escape, effective radius, set of galaxies
+Note to discuss:  Injection, merging, escape, effective radius, set of galaxies
 
@@
 
+Note to work on:
 \noindent A: two mergers early on, and then two more at around 10-12 Gyr

### 2018-06-01 paper.tex
Added most of Jerry's references to first paragraph of introduction.
Added most of Jerry's references to first paragraph of introduction, and added referenced papers to repository.

@@
 For the galaxies themselves we know that mergers are frequent from the observed (ADD VAN DOKKUM PAPER) evolution of the size and mass of these systems.
-But assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2015ApJ...799..178K}, PRETONOS & OSTRIKER, SESANA, NATARJAN).
+But assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2015ApJ...799..178K}, \citet{2014ApJ...789..156M}, \citet{2008MNRAS.390..192S}, \citet{2013MNRAS.433L...1S}, \citet{2018ApJ...856...42S}, \citet{2009MNRAS.394.2255S}, NATARJAN).
 But we do not often see multiple SMBHs at the centers of massive ellipticals.

### 2018-06-01 paper.tex
Fixed up more of Introduction. Added papers from Ostriker on mergers and galaxy size.

--- 2018-06-01 paper.tex
@@
 \section{Introduction}\label{sec:introduction}
-What is the ultimate fate of the supermassive black holes (SMBH) resident at the centers of all massive galaxies?
-For the galaxies themselves we know that mergers are frequent from the observed (ADD VAN DOKKUM PAPER) evolution of the size and mass of these systems.
-But assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2015ApJ...799..178K}, PRETONOS & OSTRIKER, SESANA, NATARJAN).
+A majority of all galaxies with masses $>10^8\msun$ at $z=0$ are believed to host super-massive black holes (SMBHs) in their cores.
+What is the ultimate fate of the supermassive black holes (SMBH) resident at the centers of these massive galaxies?
+For the galaxies themselves we know that mergers are frequent from the observed (VAN DOKKUM PAPERS??) evolution of the size and mass of these systems.
+But assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2015ApJ...799..178K}, \citet{2014ApJ...789..156M}, \citet{2008MNRAS.390..192S}, \citet{2013MNRAS.433L...1S}, \citet{2018ApJ...856...42S}, \citet{2009MNRAS.394.2255S}, \citet{2018arXiv180403143I}, NATARAJAN??).
 But we do not often see multiple SMBHs at the centers of massive ellipticals.
 So, what does happen?
+One paper (\citet{2018MNRAS.473.3410R}) has indicated that dynamical interactions among multiple black holes, which eject a non-negligible fraction of the mass, may solve this problem.
+The present paper also addresses this purported dynamical solution.
 What we argue in this paper is that as a result of the N-body interactions among the infalling black holes some are ejected, some remain in extended orbits and some (the few most massive ones) do in fact merge but we do not exceed the PTA limits, and the orbiting ones should be detectable via their ability to accrete gas and emit radiation.
-
-A majority of all galaxies with masses $>10^8\msun$ at $z=0$ are believed to host super-massive black holes (SMBHs) in their cores.
-In a $\Lambda$CDM universe, galaxies at the high end of the galaxy-mass function are merger products of numerous such massive galaxies.
-Even if only a small fraction of merging galaxies hosted an SMBH in their core at the time of merging, it is reasonable to assume that, during a Hubble time of continuous growth, these galaxies will have substantial phases in which they contain two or more SMBHs at the same time.
 
@@
 Galaxies with higher masses are more extended, making dynamical friction processes less efficient and hence failing to drive SMBHs into the host galaxy core.
-Several papers (\citet{2018arXiv180403143I}, \citet{2014ApJ...789..156M}) have shown that if all galaxy mergers lead to black hole mergers, the resulting PTA signal would be roughly twice the current limits.
-One paper (\citet{2018MNRAS.473.3410R}) has indicated that dynamical interactions among multiple black holes, which eject a non-negligible fraction of the mass, may solve this problem.
-The present paper also addresses this purported dynamical solution.
 
-This paper is organized as follows: in Section \ref{sec:methods} we are going to describe the cosmological simulation from which we use the merger history to set up our idealized numerical simulations.
+This paper is organized as follows: in Section \ref{sec:methods} we describe the cosmological simulation from which we use the merger history to set up our idealized numerical simulations.
 We present the few-body integration code, \textsc{AR-Chain} that we used for our simulations of SMBH dynamics, and the modifications we made to this code in order to deal with a host galaxy's gravitational potential.
-In Section \ref{sec:results}, we show the results of our four exemplary simulations of galaxies growing with time and acquiring new SMBHs.
+In Section \ref{sec:results}, we show the results of our XX exemplary simulations of galaxies growing with time and acquiring new SMBHs.
 We analyze how the SMBHs are driven into the core of their new host galaxies and how interaction with the host black hole leads to near-ejections or mergers.

### 2018-06-01 paper.tex
Added more edits from Jerry.

@@
 \subsection{Overview of simulation}
-Our simulations focused on elliptical galaxies with central SMBHs.
+Our simulations focus on elliptical galaxies with central SMBHs.
 The galaxies were given a background potential based on the Ostriker-Stone profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form.
@@
 \end{itemize}
-
-SHOULD I INCLUDE PLOTS AND/OR HISTOGRAMS OF THE DISTRIBUTION OF GALAXY MASSES, STELLAR MASSES, ETC AT Z=0?
 
@@
 Compared with the expected range of $0.10 \lessapprox f_* \lessapprox 0.15$ that they referenced from \citet{2012ApJ...746...95L}, their stellar masses were a factor of roughly 4 times greater.
-In order to adjust our stellar masses to levels more in line with current observations, we used observational data from \citet{2018AstL...44....8K}, in particular Figure 11.
+We used observational data from \citet{2018AstL...44....8K}, in particular Figure 11, to rescale the stellar masses to the observed range.
 \begin{figure}[h!]
@@
 
-In order to parametrize this profile, $r_c$ was given an arbitrary initial value of 100 pc.
+In order to parametrize this profile, $r_c$ was given an initial value of 100 pc, which is reasonable for a cored massive system.
 To calculate $r_h$, we began by using the stellar mass to calculate the velocity dispersion at the galaxy's effective radius.
@@
 \begin{equation}
-f(\chi) = \frac{1}{2\chi^2}\left(\mbox{erf}(\chi)-\frac{2\chi}{\sqrt{\pi}}\exp\left(-\chi^2\right)\right).
+f(\chi) \equiv \frac{1}{2\chi^2}\left(\mbox{erf}(\chi)-\frac{2\chi}{\sqrt{\pi}}\exp\left(-\chi^2\right)\right).
 \end{equation}
@@
 \begin{equation}
-\Lambda = \left(\frac{M_{NSC}}{M_\bullet}\right)\left(\frac{r}{r_h}\right).
+\Lambda \equiv \left(\frac{M_{NSC}}{M_\bullet}\right)\left(\frac{r}{r_h}\right).
 \end{equation}

### 2018-08-02 paper.tex
Added Jerry's edits/additions from 2018 08 01 meeting

@@
 \section{Introduction}\label{sec:introduction}
+What happens to the massive black holes centrally located in galaxies when those galaxies merge with others?
+There are three possibilities: they merge, they are ejected, or they remain in orbit in the merged galaxy.
+Combinations of these options are also possible with the spin induced kick at merger leading to an ejection or extended orbit of the merged black hole.
+We now know from pulsar timing measurements (ADD REFERENCES) that the gravitational wave background is probably too low for most galaxy mergers (mass-weighted) (BUT SEE MIDLETON ET AL 2018) to lead to BH mergers, but the outcome remains uncertain.
+We will argue in this paper that a very common outcome--especially for the lower mass black holes--is for the injected objects to remain as orbiting X-ray sources in normal massive galaxies waiting to be identified by current observational techniques.
+
 A majority of all galaxies with masses $>10^8\msun$ at $z=0$ are believed to host super-massive black holes (SMBHs) in their cores.
@@
 One paper (\citet{2018MNRAS.473.3410R}) has indicated that dynamical interactions among multiple black holes, which eject a non-negligible fraction of the mass, may solve this problem.
-The present paper also addresses this purported dynamical solution.
+The present paper also addresses this purported dynamical solution, focusing attention on the large fraction of lower mass black holes that remain to be detected as they orbit in massive galaxies.
 What we argue in this paper is that as a result of the N-body interactions among the infalling black holes some are ejected, some remain in extended orbits and some (the few most massive ones) do in fact merge but we do not exceed the PTA limits, and the orbiting ones should be detectable via their ability to accrete gas and emit radiation.
 
-Here we look at the merger history of XX exemplary galaxies across the galaxy mass spectrum extracted from a cosmological simulation of hierarchical structure formation.
+Here we look at the merger history of 12 exemplary galaxies across the galaxy mass spectrum extracted from a cosmological simulation of hierarchical structure formation.
 We investigate how, after merging with incoming galaxies, SMBHs diffuse into the cores of the hosts and interact with the resident black hole.
@@
 We include gravitational wave recoils following the prescription outlined in Kulier15, which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.
-To save computational time, we assume that a merger will be inevitable when the separation between two SBHs gets smaller than 1.0 Schwarzschild radius.
+To save computational time, we assume that a merger will be inevitable when the separation between two SBHs becomes smaller than 1.0 Schwarzschild radius.
 At the moment of the merger, we assume that the spin vectors of the two SBHs are randomly aligned.
@@
 Their initial velocity was arbitrarily chosen to be circular, $v_c = \sqrt{M(R_e)/R_e}$, with $v_x$, $v_y$, and $v_z$ randomly chosen.
-
 Note: we only inject the BHs into the simulation that have a $t_{fric}$ smaller than 100 times the Hubble time.

### 2018-08-10 paper.tex
Added more edits from Jerry.  Added Merger Summary.

@@
 \usepackage{babel}
+\usepackage{float}
 %\usepackage{siunitx}
@@
 Combinations of these options are also possible with the spin induced kick at merger leading to an ejection or extended orbit of the merged black hole.
-We now know from pulsar timing measurements (ADD REFERENCES) that the gravitational wave background is probably too low for most galaxy mergers (mass-weighted) (BUT SEE MIDLETON ET AL 2018) to lead to BH mergers, but the outcome remains uncertain.
+We now know from pulsar timing measurements (ADD REFERENCES) that the gravitational wave background is probably too low for most galaxy mergers (mass-weighted) (BUT SEE MIDDLETON ET AL 2018) to lead to BH mergers, but the outcome remains uncertain.
 We will argue in this paper that a very common outcome--especially for the lower mass black holes--is for the injected objects to remain as orbiting X-ray sources in normal massive galaxies waiting to be identified by current observational techniques.
@@
 For the galaxies themselves we know that mergers are frequent from the observed (VAN DOKKUM PAPERS??) evolution of the size and mass of these systems.
-But assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2015ApJ...799..178K}, \citet{2014ApJ...789..156M}, \citet{2008MNRAS.390..192S}, \citet{2013MNRAS.433L...1S}, \citet{2018ApJ...856...42S}, \citet{2009MNRAS.394.2255S}, \citet{2018arXiv180403143I}, NATARAJAN??).
+But assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2015ApJ...799..178K}, \citet{2014ApJ...789..156M}, \citet{2008MNRAS.390..192S}, \citet{2013MNRAS.433L...1S}, \citet{2018ApJ...856...42S}, \citet{2009MNRAS.394.2255S}, \citet{2018arXiv180403143I}).
 But we do not often see multiple SMBHs at the centers of massive ellipticals.
@@
 
-Here we look at the merger history of 12 exemplary galaxies across the galaxy mass spectrum extracted from a cosmological simulation of hierarchical structure formation.
+Here we look at the merger history of 13 exemplary galaxies across the galaxy mass spectrum extracted from a cosmological simulation of hierarchical structure formation.
 We investigate how, after merging with incoming galaxies, SMBHs diffuse into the cores of the hosts and interact with the resident black hole.
@@
 \section{Results}\label{sec:results}
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{plots/Summary_Results_All_Galaxies.png}
+\caption{Histogram of merged, ejected, and orbiting SMBHs}
+\label{fig:meosmbh}
+\end{center}
+\end{figure}
+
 \begin{table*}

### 2018-08-19 paper.tex
Added reference to Middleton 2018, etc.

@@
 Combinations of these options are also possible with the spin induced kick at merger leading to an ejection or extended orbit of the merged black hole.
-We now know from pulsar timing measurements (ADD REFERENCES) that the gravitational wave background is probably too low for most galaxy mergers (mass-weighted) (BUT SEE MIDDLETON ET AL 2018) to lead to BH mergers, but the outcome remains uncertain.
+We now know from pulsar timing measurements (ADD REFERENCES) that the gravitational wave background is probably too low for most galaxy mergers (mass-weighted) (but see \cite{2018NatCo...9..573M}) to lead to BH mergers, but the outcome remains uncertain.
 We will argue in this paper that a very common outcome--especially for the lower mass black holes--is for the injected objects to remain as orbiting X-ray sources in normal massive galaxies waiting to be identified by current observational techniques.

### 2018-09-03 paper.tex
Added references.
Added pdf references to ‘Referenced Papers’ folder, reordered
references in second paragraph of Introduction.

@@
 For the galaxies themselves we know that mergers are frequent from the observed (VAN DOKKUM PAPERS??) evolution of the size and mass of these systems.
-But assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2015ApJ...799..178K}, \citet{2014ApJ...789..156M}, \citet{2008MNRAS.390..192S}, \citet{2013MNRAS.433L...1S}, \citet{2018ApJ...856...42S}, \citet{2009MNRAS.394.2255S}, \citet{2018arXiv180403143I}).
+But assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2008MNRAS.390..192S}, \citet{2009MNRAS.394.2255S}, \citet{2013MNRAS.433L...1S}, \citet{2014ApJ...789..156M}, \citet{2015ApJ...799..178K}, \citet{2018ApJ...856...42S}, \citet{2018arXiv180403143I}).
 But we do not often see multiple SMBHs at the centers of massive ellipticals.

### 2018-09-04 paper.tex
Various changes requested by Jerry.
Changes to text requested by Jerry; removed many of the original plots
we were going to use.  Modified Kravtsov plot.

@@
 
-A majority of all galaxies with masses $>10^8\msun$ at $z=0$ are believed to host super-massive black holes (SMBHs) in their cores.
-What is the ultimate fate of the supermassive black holes (SMBH) resident at the centers of these massive galaxies?
-For the galaxies themselves we know that mergers are frequent from the observed (VAN DOKKUM PAPERS??) evolution of the size and mass of these systems.
+How common are mergers of massive black holes?
+For the galaxies themselves we know that minor mergers are frequent from the observed (VAN DOKKUM PAPERS??) evolution of the size and mass of these systems.
 But assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2008MNRAS.390..192S}, \citet{2009MNRAS.394.2255S}, \citet{2013MNRAS.433L...1S}, \citet{2014ApJ...789..156M}, \citet{2015ApJ...799..178K}, \citet{2018ApJ...856...42S}, \citet{2018arXiv180403143I}).
@@
 The present paper also addresses this purported dynamical solution, focusing attention on the large fraction of lower mass black holes that remain to be detected as they orbit in massive galaxies.
-What we argue in this paper is that as a result of the N-body interactions among the infalling black holes some are ejected, some remain in extended orbits and some (the few most massive ones) do in fact merge but we do not exceed the PTA limits, and the orbiting ones should be detectable via their ability to accrete gas and emit radiation.
+What we argue in this paper is that as a result of the N-body interactions among the infalling black holes some are ejected, some remain in extended orbits and some (the few most massive ones) do in fact merge, but these do not exceed the PTA limits, and the orbiting ones should be detectable via their ability to accrete gas and emit radiation.
 
@@
 We investigate how, after merging with incoming galaxies, SMBHs diffuse into the cores of the hosts and interact with the resident black hole.
-We show that gravitational interactions of multiple SMBHs are most probable in high-mass galaxies with $10^{12} \msun < M < 10^{13} \msun$.
+We show that gravitational interactions of multiple SMBHs are most probable in high-mass galaxies with total mass $10^{12} \msun < M < 10^{13} \msun$.
 Galaxies with lower masses have too few mergers with SMBH hosting galaxies.
@@
 
-This paper is organized as follows: in Section \ref{sec:methods} we describe the cosmological simulation from which we use the merger history to set up our idealized numerical simulations.
+This paper is organized as follows: in Section \ref{sec:methods} we describe the cosmological simulations from which we use the merger history to set up our idealized numerical simulations.
 We present the few-body integration code, \textsc{AR-Chain} that we used for our simulations of SMBH dynamics, and the modifications we made to this code in order to deal with a host galaxy's gravitational potential.
@@
 We analyze how the SMBHs are driven into the core of their new host galaxies and how interaction with the host black hole leads to near-ejections or mergers.
-The final Section \ref{sec:conclusions} contains a discussion of the result and our conclusions.
+The final Section \ref{sec:conclusions} contains a discussion of the results and our conclusions.
 
@@
 Our simulations focus on elliptical galaxies with central SMBHs.
-The galaxies were given a background potential based on the Ostriker-Stone profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form.
+The galaxies were given a background potential based on the Stone-Ostriker profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form.
 The galaxies were evolved from $4 > z > 0$.
@@
 Compared with the expected range of $0.10 \lessapprox f_* \lessapprox 0.15$ that they referenced from \citet{2012ApJ...746...95L}, their stellar masses were a factor of roughly 4 times greater.
-We used observational data from \citet{2018AstL...44....8K}, in particular Figure 11, to rescale the stellar masses to the observed range.
+We used observational data from \citet{2018AstL...44....8K}, in particular Figure 11, to rescale the stellar masses to the observed range (see Figure \ref{fig:stellar1}).
 \begin{figure}[h!]
@@
 \includegraphics[width=0.45\textwidth]{plots/stellar_to_halo_ratio.png}
-\caption{Original and rescaled stellar masses}
+\caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.  X's shown is example of our rescaled stellar masses}
 \label{fig:stellar1}
@@
 At the moment of the merger, we assume that the spin vectors of the two SBHs are randomly aligned.
-This results in kick velocities of up to several thousand km\,s$^{-1}$, with a median kick of $\approx 290$\,km\,s$^{-1}$.
-Since our simulations focus on NSC with relatively low escape velocities, this implies that a majority of the merging SBHs escape from the NSCs.
 
 Black holes can also eject each other via strong three-body interactions.
-We remove SBHs from the simulations once they move beyond 1\,kpc from the NSC, assuming that it will take them more than a Hubble time to find their way back into the center of the host galaxy.
+We remove SBHs from the simulations once they move beyond $r_h$, assuming that it will take them more than a Hubble time to find their way back into the center of the host galaxy.
 
 \subsection{Simulation setup}
-Note to discuss:  Injection, merging, escape, effective radius, set of galaxies
-
 Using the merger tree data, orbiting black holes were injected into its host galaxy at redshift z, at a distance from the galactic center of $R_{e}$ (Eqn.
@@
 
-\begin{table*}
-\centering
-\caption{SMBH statistics}
-\begin{tabular}{c| c |c |c}
-Galaxy & Infalling SMBHs & SMBHs with $t_{fric}<100\,t_H$ & Mergers \\
-\hline
-A & 206 & 19 & 4 \\
-B & 29 & 12 & 4 \\
-C & 3 & 3 & 2 \\
-D & 4 & 4 & 2 \\
-\end{tabular}
-\end{table*}
-
-\begin{figure*}[htbp]
-\begin{center}
-\includegraphics[width=0.45\textwidth]{plots/radius_A.png}
-\includegraphics[width=0.45\textwidth]{plots/radius_B.png}\\
-\includegraphics[width=0.45\textwidth]{plots/radius_C.png}
-\includegraphics[width=0.45\textwidth]{plots/radius_D.png}\\
-\caption{default}
-\label{default2}
-\end{center}
-\end{figure*}
-
-\begin{figure*}[htbp]
-\begin{center}
-\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_1.png}
-\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_65.png}\\
-\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_187.png}
-\includegraphics[width=0.45\textwidth]{plots/orbiting_bh_mass_histogram_gal_217.png}\\
-\caption{default}
-\label{default3}
-\end{center}
-\end{figure*}
-
-\subsection{Mergers}
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.45\textwidth]{plots/masses_ABCD.png}
-\caption{default}
-\label{default4}
-\end{center}
-\end{figure}
-
-Note to work on:
-\noindent A: two mergers early on, and then two more at around 10-12 Gyr
-B: 4 mergers across the final 8 Gyr
-C: two mergers in the final Gyrs
-D: ?
-
-\subsection{Ejections}
-No complete ejections, but kicks to higher energy orbits.
-\noindent A: one in a three-body encoutner\\
-B: 7-ish kicks, some in nearly 4-body encounters\\
-C: none\\
-D: ?\\
-
-\subsection{Stalling SMBH binaries}
-A: two periods of BH binary in center for > Gyr, up to 6 Gyr\\
-B: two short periods of BHBs\\
-C: 2 classic BHB periods of about 1 Gyr each\\
-D: ?
-
-\subsection{Stalling SMBHs in the halo}
-\begin{figure*}[htbp]
-\begin{center}
-\includegraphics[width=0.45\textwidth]{plots/t_at_center_histogram_gal_1.png}
-\includegraphics[width=0.45\textwidth]{plots/t_at_center_histogram_gal_65.png}\\
-\includegraphics[width=0.45\textwidth]{plots/t_at_center_histogram_gal_187.png}
-\includegraphics[width=0.45\textwidth]{plots/t_at_center_histogram_gal_217.png}\\
-\caption{default}
-\label{default5}
-\end{center}
-\end{figure*}
-
-A: 95\% never make it into the central kpc\\
-B: still about 90\% are in the halo\\
-C: \\
-D: ?
-
 \section{Conclusions}\label{sec:conclusions}

### 2018-09-12 paper.tex
Enlarged Kravtsov plot labels
Added van Dokkum references to Introduction, and pdfs of papers

@@
 How common are mergers of massive black holes?
-For the galaxies themselves we know that minor mergers are frequent from the observed (VAN DOKKUM PAPERS??) evolution of the size and mass of these systems.
+For the galaxies themselves we know that minor mergers are frequent from the observed (\citet{2010ApJ...718L..73V}, \citet{2008ApJ...677L...5V}) evolution of the size and mass of these systems.
 But assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2008MNRAS.390..192S}, \citet{2009MNRAS.394.2255S}, \citet{2013MNRAS.433L...1S}, \citet{2014ApJ...789..156M}, \citet{2015ApJ...799..178K}, \citet{2018ApJ...856...42S}, \citet{2018arXiv180403143I}).
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{plots/stellar_to_halo_ratio.png}
+\includegraphics[width=1.0\columnwidth]{plots/stellar_to_halo_ratio.png}
 \caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.  X's shown is example of our rescaled stellar masses}

### 2018-09-17 paper.tex
Modified/added results plots

@@
 \section{Results}\label{sec:results}
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{"plots/Fractions All Galaxies".png}
+\caption{Fractions Merged/Ejected/Orbiting at z=0, by mass bin}
+\label{fig:fmeo}
+\end{center}
+\end{figure}
+
 \begin{figure}[H]
 \begin{center}
-\includegraphics[width=0.45\textwidth]{plots/Summary_Results_All_Galaxies.png}
+\includegraphics[width=0.45\textwidth]{plots/"Summary Results All Galaxies".png}
 \caption{Histogram of merged, ejected, and orbiting SMBHs}
 \label{fig:meosmbh}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{plots/"Final Luminosities of Oriting BHs".png}
+\caption{Luminosities of Orbiting BHs at z=0}
+\label{fig:loobhs}
 \end{center}

### 2018-10-06 paper.tex
Added 'dark matter' to section Overview of simulation

@@
 Our simulations focus on elliptical galaxies with central SMBHs.
-The galaxies were given a background potential based on the Stone-Ostriker profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form.
+The galaxies were given a dark matter background potential using the Stone-Ostriker profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form.
 The galaxies were evolved from $4 > z > 0$.

### 2018-10-10 paper.tex
Updates from ShareLaTeX

@@
 \subsection{Merger tree}
-Our merger tree data came from two sources:
+Our merger tree data came from two sources, each of which in turn used the large-scale hydrodynamical galaxy simulations outlined in \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C}:
 \begin{itemize}
-\item Galactic merger tree data from simulations of \citet{2012MNRAS.425..641L} (hereafter Lackner12), which was centered on galaxies at each redshift slice, providing information on the galaxies' stellar mass, dark matter mass, central BH, and any orbiting black holes within the galaxy.
-\item SMBH evolution simulations of \citet{2015ApJ...799..178K} (hereafter Kulier15), which used the large-scale hydrodynamical galaxy simulations outlined in \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C}.
+\item Galactic merger tree data from simulations of \citet{2012MNRAS.425..641L} (hereafter Lackner12).
+In this paper, the authors simulated and compared the properties of in situ and accreted stellar mass of galaxies at redshift snapshots between $4 > z > 0$.
+For our simulations, we only utilized total stellar mass, without regard for whether the mass was accreted or formed in situ.
+\item SMBH evolution simulations of \citet{2015ApJ...799..178K} (hereafter Kulier15).
 The data was centered around SMBHs at each redshift slice from $4 > z > 0$, giving information for each SMBH's seed mass, accreted and seed mass, its host galaxy (categorically defined), the stellar mass in its host galaxy, and time after z=4 at which the BH entered the host galaxy (if it is not the central BH).
@@
 
-The Kulier15 merger tree collected black holes entering galaxies during the simulation and noted the time after z=4 at which they entered their host galaxy.
-Nothing further was done with them, so each galaxy had a "running list" of other galaxies/BHs orbiting them at z=0.
-Clean up this paragraph.
+The above criteria narrowed the field of eligible galaxies down to 53.
 
-After finding our subject galaxies, we curve-fit their total masses as a function of time using a $7^{th}$-order polynomial fit, so as to be able to use their masses in the AR-Chain code.
-Additionally, we curve-fit each galaxy's accreted+seed central black hole mass to exponential functions of time.
+The following cosmological parameters were used in our simulations, consistent with both Lackner12 and Kulier15:   $\Omega_M = 0.28$, $\Omega_b = 0.046$, $\Omega_\Lambda = 0.72$, $\sigma_8 = 0.82$, $H_0 = 100h^{-1}Mpc^{-1} = 70 km s^{-1} Mpc^{-1}$, and $n = 0.96$.
 
-The following cosmological parameters were used in the simulations of both Lackner12 and Kulier15:   $\Omega_M = 0.28$, $\Omega_b = 0.046$, $\Omega_\Lambda = 0.72$, $\sigma_8 = 0.82$, $H_0 = 100h^{-1}Mpc^{-1} = 70 km s^{-1} Mpc^{-1}$, and $n = 0.96$.
-
-\subsubsection{Galactic Stellar Mass Adjustment}
+\subsubsection{Stellar Mass Adjustment}
 Lackner12 noted that the efficiency of star formation in their simulations, defined as $f_*=M_*/M_{DM}(\Omega_{DM}/\Omega_b)$, was approximately 0.6.
@@
 
-\begin{figure}[H]
+\begin{figure}[ht]
 \begin{center}

### 2018-10-11 paper.tex
Made changes to Merger Tree section

@@
 
-\subsection{Merger tree}
-Our merger tree data came from two sources, each of which in turn used the large-scale hydrodynamical galaxy simulations outlined in \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C}:
+\subsection{Merger tree Data}
+The merger tree data that was used as the input to our simulations is the result of previous work by \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C} (hereafter Cen11), \citet{2012MNRAS.425..641L} (hereafter Lackner12), and \citet{2015ApJ...799..178K} (hereafter Kulier15).
+A brief synopsis of the work that led to our input data is described below.
+
+Cen11 studied the "cosmic downsizing" effect (e.g., \citet{1996AJ....112..839C}) using high-resolution large-scale hydrodynamic galaxy formation simulations.
+His work produced physical parameters for galaxies such as position, velocity, total mass, stellar mass, gas mass, mean formation time, mean stellar metallicity, mean gas metallicity, SFR, luminosities, etc.
+
+Lackner12, using Cen11's work as a basis, created galactic merger trees that compared the properties of in situ and accreted stellar mass of galaxies at redshift snapshots between $4 > z > 0$.
+
+Kulier15 furthered the merger tree data produced by Lackner12 by estimating the evolution of the SMBH population, based on assumptions about the relationship between the properties of SMBHs and those of their host galaxies.
+
+The primary data we extracted from the above work was organized as follows:
 \begin{itemize}
-\item Galactic merger tree data from simulations of \citet{2012MNRAS.425..641L} (hereafter Lackner12).
-In this paper, the authors simulated and compared the properties of in situ and accreted stellar mass of galaxies at redshift snapshots between $4 > z > 0$.
-For our simulations, we only utilized total stellar mass, without regard for whether the mass was accreted or formed in situ.
-\item SMBH evolution simulations of \citet{2015ApJ...799..178K} (hereafter Kulier15).
-The data was centered around SMBHs at each redshift slice from $4 > z > 0$, giving information for each SMBH's seed mass, accreted and seed mass, its host galaxy (categorically defined), the stellar mass in its host galaxy, and time after z=4 at which the BH entered the host galaxy (if it is not the central BH).
+    \item Galactic properties - Each galaxy was distinguished by an id number, with properties such as stellar mass, dark matter mass, central black hole id number, and orbiting black hole id numbers, recorded at 37 redshift slices between $4 > z > 0$.
+    \item Black Holes properties - Each black hole was also distinguished by an id number, with properties such as seed mass, accreted mass, its host galaxy id number, and time after $z=4$ at which the black hole entered its host galaxy, if it was not the central black hole.
 \end{itemize}
@@
 \item The galaxies had to exist through the entire simulation ($4 > z > 0$).  If they merged with other galaxies, they had to have been the "surviving" galaxy at each merger.
-\item They had to have accumulated orbiting black holes by z = 0.
+\item They had to have accumulated orbiting black holes by $z = 0$.
 \end{itemize}
 
-The above criteria narrowed the field of eligible galaxies down to 53.
+The above criteria narrowed the field of eligible galaxies down to 51.
+In considering time and resources, we chose the top 13 galaxies in terms of number of black holes to run the simulations.
+These black holes in these galaxies accounted for nearly $84{\%}$ of all orbiting black holes across all the galaxies, so it represented a reasonable balance between completeness and efficiency.
 

### 2018-10-16 paper.tex
Modified Merger Tree Data and Stellar Mass Adjustments Sections

@@
 \usepackage{float}
-%\usepackage{siunitx}
+\usepackage{siunitx}
 %\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
@@
 In considering time and resources, we chose the top 13 galaxies in terms of number of black holes to run the simulations.
-These black holes in these galaxies accounted for nearly $84{\%}$ of all orbiting black holes across all the galaxies, so it represented a reasonable balance between completeness and efficiency.
+The black holes in these galaxies accounted for nearly $84{\%}$ of all orbiting black holes across all the galaxies, so it represented a reasonable balance between completeness and efficiency.
 
 The following cosmological parameters were used in our simulations, consistent with both Lackner12 and Kulier15:   $\Omega_M = 0.28$, $\Omega_b = 0.046$, $\Omega_\Lambda = 0.72$, $\sigma_8 = 0.82$, $H_0 = 100h^{-1}Mpc^{-1} = 70 km s^{-1} Mpc^{-1}$, and $n = 0.96$.
+
+\begin{table}[ht]
+\centering
+\caption{Galaxy characteristics at z=0}
+\begin{tabular} {|c | c | c|}
+\hline
+$M_{*}$ & $M_{DM}$ & $M_{CBH}$ \\
+\hline
+\num{1.75e13} & \num{9.18e13} & \num{2.19e9} \\ 
+\num{1.52e13} & \num{7.75e13} & \num{5.27e9} \\
+\num{4.46e12} & \num{2.29e13} & \num{1.22e9} \\
+\num{5.58e12} & \num{2.85e13} & \num{1.46e9} \\
+\num{2.32e12} & \num{1.18e13} & \num{3.62e9} \\
+\num{1.96e12} & \num{1.03e13} & \num{9.85e9} \\
+\num{4.80e12} & \num{2.48e13} & \num{2.40e9} \\
+\num{1.62e12} & \num{8.56e12} & \num{6.86e9} \\
+\num{1.74e12} & \num{8.92e12} & \num{5.60e9} \\
+\num{1.23e12} & \num{6.29e12} & \num{1.22e9} \\
+\num{1.72e12} & \num{6.94e12} & \num{2.02e9} \\
+\num{1.95e12} & \num{1.00e13} & \num{9.32e9} \\
+\num{5.52e11} & \num{1.84e12} & \num{2.21e9} \\
+\hline
+\end{tabular}
+\label{table:gal_char}
+\end{table}
 

### 2018-11-07 paper.tex
Added more text to Stellar Mass Adjustment section

--- 2018-10-11 paper.tex
@@
 In considering time and resources, we chose the top 13 galaxies in terms of number of black holes to run the simulations.
-These black holes in these galaxies accounted for nearly $84{\%}$ of all orbiting black holes across all the galaxies, so it represented a reasonable balance between completeness and efficiency.
+The black holes in these galaxies accounted for nearly $84{\%}$ of all orbiting black holes across all the galaxies, so it represented a reasonable balance between completeness and efficiency.
 
@@
 \subsubsection{Stellar Mass Adjustment}
-Lackner12 noted that the efficiency of star formation in their simulations, defined as $f_*=M_*/M_{DM}(\Omega_{DM}/\Omega_b)$, was approximately 0.6.
+As we will explain further in Section \ref{Galaxy background potential}, in our simulations orbiting black holes are inserted into the host galaxy at the effective radius, $R_e$, which is partially dependent on stellar mass, $M_*$ (see equation \ref{re}).
+For every doubling of the stellar mass, $M_*$, $R_e$ increases by a factor of 1.66.
+Additionally, the velocity dispersion at the effective radius, $\sigma(R_e)$, which is used to set the parameter $r_h$ of our dark matter profile, is also dependent on $M_*$.
+In this case, a doubling of $M_*$ would increase $\sigma(R_e)$ by a factor of 1.15.
+These variations have direct effects on the ability of the orbiting black holes to merge with the central black hole, and thus can affect our merger statistics and resulting characteristic strain calculations, and therefore it is important to estimate our stellar masses with reasonable accuracy.
+
+In cosmological simulations it is common to overproduce stellar mass, with a general over-efficiency in the range of 2-4 times those measured in observations (\citet{1996ApJS..105...19K}, \citet{2010MNRAS.404.1111G}, \citet{2010ApJ...725.2312O}).
+One typical reason cited for this overproduction is a lack or underestimation of supernova feedback effects in the form of thermal and/or kinetic energy.
+However, even when thermal energy from supernova feedback is considered, the effects may be reduced due to the energy being quickly radiated away by rapidly cooling surrounding gas (\citet{1996ApJS..105...19K}).
+A second common reason for overproduction of stars in cosmological simulations is a lack of modeling for AGN feedback, which may be responsible for a phenomenon called the "cooling flow paradox" (\citet{2001MNRAS.321L..20F}) that suppresses star formation.
+
+Lackner12, which is the source of our stellar masses, noted that the efficiency of star formation in their simulations, defined as $f_*=M_*/M_{DM}(\Omega_{DM}/\Omega_b)$, was approximately 0.6.
 Compared with the expected range of $0.10 \lessapprox f_* \lessapprox 0.15$ that they referenced from \citet{2012ApJ...746...95L}, their stellar masses were a factor of roughly 4 times greater.
-We used observational data from \citet{2018AstL...44....8K}, in particular Figure 11, to rescale the stellar masses to the observed range (see Figure \ref{fig:stellar1}).
-\begin{figure}[h!]
+
+We also compared the stellar masses from Lackner12 to  observational and abundance matching data from \citet{2018AstL...44....8K}.
+Figure \ref{fig:stellar1} is a partial, approximate, replication of their Figure 11 (abundance matching line).
+We rescaled our stellar masses at $z=0$ in a lognormal manner about the line in order to match the observed data.
+Table \ref{table:gal_char} shows the original and rescaled stellar masses.
+In some cases, the original masses were up to 30-40 times larger than the rescaled values, which would have large implications for the ability of the orbiting black holes to reach the center of their host galaxies.
+
+\begin{figure}[htbp]
 \begin{center}
 \includegraphics[width=1.0\columnwidth]{plots/stellar_to_halo_ratio.png}
-\caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.  X's shown is example of our rescaled stellar masses}
+\caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.  Purple dots shown is example of our rescaled stellar masses}
 \label{fig:stellar1}
@@
 
+\begin{table}[htbp]
+\centering
+\caption{Galaxy characteristics at z=0}
+\begin{tabular} {|c | c | c| c|}
+\hline
+$M_{DM}$ & $M_{CBH}$ & $M_{*} (orig.)$ & $M_{*} (rescaled)$ \\
+\hline
+ \num{9.18e13} 	&	 \num{2.19e9} 	&	\num{1.75e13} 	&	\num{5.14e11}  \\
+ \num{7.75e13} 	&	 \num{5.27e9}	&	\num{1.52e13} 	&	\num{4.00e11}  \\
+ \num{2.85e13} 	&	 \num{1.46e9}	&	\num{5.58e12} 	&	\num{3.30e11}  \\
+ \num{2.48e13} 	&	 \num{2.40e9}	&	\num{4.80e12} 	&	\num{2.25e11}  \\
+ \num{2.29e13} 	&	 \num{1.22e9}	&	\num{4.46e12} 	&	\num{2.68e11}  \\
+ \num{1.18e13} 	&	 \num{3.62e9}	&	\num{2.32e12} 	&	\num{2.83e11}  \\
+ \num{1.03e13} 	&	 \num{9.85e9}	&	\num{1.96e12} 	&	\num{1.62e11}  \\
+ \num{1.00e13} 	&	 \num{9.32e9}	&	\num{1.95e12} 	&	\num{2.49e11}  \\
+ \num{8.92e12} 	&	 \num{5.60e9}	&	\num{1.74e12} 	&	\num{3.20e11}  \\
+ \num{8.56e12} 	&	 \num{6.86e9}	&	\num{1.62e12} 	&	\num{1.83e11}  \\
+ \num{6.94e12} 	&	 \num{2.02e9}	&	\num{1.72e12} 	&	\num{1.51e11}  \\
+ \num{6.29e12} 	&	 \num{1.22e9}	&	\num{1.23e12} 	&	\num{1.87e11}  \\
+ \num{1.84e12} 	&	 \num{2.21e9}	&	\num{5.52e11} 	&	\num{6.42e10}  \\
+\hline
+\end{tabular}
+\label{table:gal_char}
+\end{table}
+
 \subsection{AR-Chain code}
@@
 
-\subsubsection{Galaxy background potential}
+\subsubsection{Galaxy background potential} \label{Galaxy background potential}
 For our simulations, the Stone-Ostriker profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form.
@@
 \section{Results}\label{sec:results}
-\begin{figure}[h!]
+\begin{figure}[ht]
 \begin{center}

### 2018-11-26 paper.tex
Started to add black hole luminosity section.

@@
 \usepackage{float}
+\usepackage{savesym}
+\savesymbol{tablenum}
 \usepackage{siunitx}
+\restoresymbol{SIX}{tablenum}
 %\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
@@
 \providecommand{\tabularnewline}{\\}
+% Alter some LaTeX defaults for better treatment of figures:
+    % See p.105 of "TeX Unbound" for suggested values.
+    % See pp. 199-200 of Lamport's "LaTeX" book for details.
+    %   General parameters, for ALL pages:
+    \renewcommand{\topfraction}{0.9}	% max fraction of floats at top
+    \renewcommand{\bottomfraction}{0.8}	% max fraction of floats at bottom
+    %   Parameters for TEXT pages (not float pages):
+    \setcounter{topnumber}{2}
+    \setcounter{bottomnumber}{2}
+    \setcounter{totalnumber}{4}     % 2 may work better
+    \setcounter{dbltopnumber}{2}    % for 2-column pages
+    \renewcommand{\dbltopfraction}{0.9}	% fit big float above 2-col. text
+    \renewcommand{\textfraction}{0.07}	% allow minimal text w. figs
+    %   Parameters for FLOAT pages (not text pages):
+    \renewcommand{\floatpagefraction}{0.7}	% require fuller float pages
+	% N.B.: floatpagefraction MUST be less than topfraction !!
+    \renewcommand{\dblfloatpagefraction}{0.7}	% require fuller float pages
+
+	% remember to use [htp] or [htpb] for placement
 
@@
 Here we look at the merger history of 13 exemplary galaxies across the galaxy mass spectrum extracted from a cosmological simulation of hierarchical structure formation.
-We investigate how, after merging with incoming galaxies, SMBHs diffuse into the cores of the hosts and interact with the resident black hole.
+We investigate how, after merging with incoming galaxies, SMBHs sink into the cores of the hosts and interact with the resident black hole.
 We show that gravitational interactions of multiple SMBHs are most probable in high-mass galaxies with total mass $10^{12} \msun < M < 10^{13} \msun$.
@@
 Our simulations focus on elliptical galaxies with central SMBHs.
-The galaxies were given a dark matter background potential using the Stone-Ostriker profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form.
+The galaxies were given a dark matter background potential using the Stone-Ostriker profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form, having a profile similar to that of a truncated isothermal sphere.
 The galaxies were evolved from $4 > z > 0$.
-Orbiting black holes were periodically introduced into the "host" galaxy and their dynamical interaction with the background potential and central SMBH were followed, as described further below.
+Orbiting black holes were periodically introduced into the "host" galaxy following mergers and their dynamical interaction with the background potential and central SMBH were followed, as described further below.
 
@@
     \item Galactic properties - Each galaxy was distinguished by an id number, with properties such as stellar mass, dark matter mass, central black hole id number, and orbiting black hole id numbers, recorded at 37 redshift slices between $4 > z > 0$.
-    \item Black Holes properties - Each black hole was also distinguished by an id number, with properties such as seed mass, accreted mass, its host galaxy id number, and time after $z=4$ at which the black hole entered its host galaxy, if it was not the central black hole.
+    \item Black Hole properties - Each black hole was also distinguished by an id number, with properties such as seed mass, accreted mass, its host galaxy id number, and time after $z=4$ at which the black hole entered its host galaxy, if it was not the central black hole.
 \end{itemize}
@@
 Table \ref{table:gal_char} shows the original and rescaled stellar masses.
-In some cases, the original masses were up to 30-40 times larger than the rescaled values, which would have large implications for the ability of the orbiting black holes to reach the center of their host galaxies.
 
@@
 \begin{table}[htbp]
-\centering
 \caption{Galaxy characteristics at z=0}
@@
 \end{tabular}
+
 \label{table:gal_char}
@@
 The core radius, $r_c$, is recalculated only if an orbiting black hole gets within $r_c$.
-The work done by diffusion, as described in Section \ref{psd} is calculated, the total potential energy is updated, and $r_c$ is solved for from Equation 8 in Stone-Ostriker.
+The work done by diffusion, as described in Section \ref{psd} is calculated, the total potential energy and dynamical friction are updated, and $r_c$ is solved for from Equation 8 in Stone-Ostriker.
 
@@
 We can identify Equation \ref{eq:df} as the dynamical friction term.
-The second term introduces a variance of the friction term, and even allows the SBHs to be accelerated when the velocity of a SBH gets sufficiently small.
+The second term introduces a variance of the friction term, and even allows the SBHs to be accelerated when the velocity of a SBH is sufficiently small.
 The third term introduces a change in velocity perpendicular to the direction of motion of the SBH.
@@
 We include gravitational wave recoils following the prescription outlined in Kulier15, which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.
-To save computational time, we assume that a merger will be inevitable when the separation between two SBHs becomes smaller than 1.0 Schwarzschild radius.
+We assume that a merger will be inevitable when the separation between two SBHs becomes smaller than 1.0 Schwarzschild radius.
 At the moment of the merger, we assume that the spin vectors of the two SBHs are randomly aligned.
@@
 Using the merger tree data, orbiting black holes were injected into its host galaxy at redshift z, at a distance from the galactic center of $R_{e}$ (Eqn.
-\ref{re}).
+\ref{re}) following galaxy mergers.
 Their initial velocity was arbitrarily chosen to be circular, $v_c = \sqrt{M(R_e)/R_e}$, with $v_x$, $v_y$, and $v_z$ randomly chosen.
 Note: we only inject the BHs into the simulation that have a $t_{fric}$ smaller than 100 times the Hubble time.
+
+\subsection{Black Hole Luminosity}
+The x-ray temperature versus sigma relation from Table 2 of  \citet{2018ApJ...857...32B} was fitted according to:
+\begin{equation}
+    T_x = 10^{(2.50*log \sigma - 6.06)}
+\end{equation}
+Central gas density, ${\rho}_0$ was also fitted from Table 3 of \citet{2018ApJ...857...32B} according to:
+\begin{equation}
+    \rho_0 = 10^{(0.6log(\sigma) - 25)}
+\end{equation}
+The core radius of the gas model, ${r_c}$ is:
+\begin{equation}
+    r_c = 10^{(15.09log(\sigma) - 35.77)}
+\end{equation}
+Local gas density ${\rho}$ is obtained from the isothermal beta model:
+\begin{equation}
+    \rho = \frac{\rho_0}{(1+r^2/r_c^2)^{1.5}}
+\end{equation}
+Gas sound speed, ${ss}_g$, was obtained from:
+\begin{equation}
+    {ss}_g = \sqrt{1.67T_x/m_p},
+\end{equation}
+where $m_p$ is the proton mass.
+
+The black hole mass accretion rate is approximated by:
+\begin{equation}
+    \dot{M}_{acc} = \frac{4{\pi}G^2M^2\rho}{({ss_g}^2+v^2)^{3/2}},
+\end{equation}
+where M is black hole mass, G is the gravitational constant, and v is the black hole velocity.
+
+Finally, the black hole luminosity is calculated from:
+\begin{equation}
+    L = 0.1\dot{M}_{acc}{ss_g}^2
+\end{equation}
+
+The Eddington limit is known to be:
+\begin{equation}
+    L_{edd} = \num{1.26e38} (M/M_{\odot}) erg/s
+\end{equation}
 

### 2018-12-11 paper.tex
Corrected Lx equations Black Hole Luminosity section
Minor changes; added t_fric equation

@@
 \subsection{Merger tree Data}
-The merger tree data that was used as the input to our simulations is the result of previous work by \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C} (hereafter Cen11), \citet{2012MNRAS.425..641L} (hereafter Lackner12), and \citet{2015ApJ...799..178K} (hereafter Kulier15).
+The merger tree data that was used as the input to our simulations is the result of previous work by \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C} (hereafter Cen(+11)), \citet{2012MNRAS.425..641L} (hereafter Lackner(+12)), and \citet{2015ApJ...799..178K} (hereafter Kulier(+15)).
 A brief synopsis of the work that led to our input data is described below.
 
-Cen11 studied the "cosmic downsizing" effect (e.g., \citet{1996AJ....112..839C}) using high-resolution large-scale hydrodynamic galaxy formation simulations.
+Cen(+11) studied the "cosmic downsizing" effect (e.g., \citet{1996AJ....112..839C}) using high-resolution large-scale hydrodynamic galaxy formation simulations.
 His work produced physical parameters for galaxies such as position, velocity, total mass, stellar mass, gas mass, mean formation time, mean stellar metallicity, mean gas metallicity, SFR, luminosities, etc.
 
-Lackner12, using Cen11's work as a basis, created galactic merger trees that compared the properties of in situ and accreted stellar mass of galaxies at redshift snapshots between $4 > z > 0$.
+Lackner(+12), using Cen(+11)'s work as a basis, created galactic merger trees that compared the properties of in situ and accreted stellar mass of galaxies at redshift snapshots between $4 > z > 0$.
 
-Kulier15 furthered the merger tree data produced by Lackner12 by estimating the evolution of the SMBH population, based on assumptions about the relationship between the properties of SMBHs and those of their host galaxies.
+Kulier(+15) furthered the merger tree data produced by Lackner(+12) by estimating the evolution of the SMBH population, based on assumptions about the relationship between the properties of SMBHs and those of their host galaxies.
 
@@
 
-The merger tree data from Lackner12 and Kulier15 provided 1,830 galaxies in total.  However, not all the galaxies were suitable for our simulations.  We placed further requirements as follows:
+The merger tree data from Lackner(+12) and Kulier(+15) provided 1,830 galaxies in total.  However, not all the galaxies were suitable for our simulations.  We placed further requirements as follows:
 \begin{itemize}
@@
 
-The following cosmological parameters were used in our simulations, consistent with both Lackner12 and Kulier15:   $\Omega_M = 0.28$, $\Omega_b = 0.046$, $\Omega_\Lambda = 0.72$, $\sigma_8 = 0.82$, $H_0 = 100h^{-1}Mpc^{-1} = 70 km s^{-1} Mpc^{-1}$, and $n = 0.96$.
+The following cosmological parameters were used in our simulations, consistent with both Lackner(+12) and Kulier(+15):   $\Omega_M = 0.28$, $\Omega_b = 0.046$, $\Omega_\Lambda = 0.72$, $\sigma_8 = 0.82$, $H_0 = 100h^{-1}Mpc^{-1} = 70 km s^{-1} Mpc^{-1}$, and $n = 0.96$.
 
@@
 
-Lackner12, which is the source of our stellar masses, noted that the efficiency of star formation in their simulations, defined as $f_*=M_*/M_{DM}(\Omega_{DM}/\Omega_b)$, was approximately 0.6.
+Lackner(+12), which is the source of our stellar masses, noted that the efficiency of star formation in their simulations, defined as $f_*=M_*/M_{DM}(\Omega_{DM}/\Omega_b)$, was approximately 0.6.
 Compared with the expected range of $0.10 \lessapprox f_* \lessapprox 0.15$ that they referenced from \citet{2012ApJ...746...95L}, their stellar masses were a factor of roughly 4 times greater.
 
-We also compared the stellar masses from Lackner12 to  observational and abundance matching data from \citet{2018AstL...44....8K}.
+We also compared the stellar masses from Lackner(+12) to  observational and abundance matching data from \citet{2018AstL...44....8K}.
 Figure \ref{fig:stellar1} is a partial, approximate, replication of their Figure 11 (abundance matching line).
@@
 \subsubsection{Galaxy background potential} \label{Galaxy background potential}
-For our simulations, the Stone-Ostriker profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form.
+In order to model the dark matter halo distribution in our simulations, we used the Stone-Ostriker profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair.
+Quantities such as density, potential, and binding energy can be written in closed form.
 It is essentially an analytic form of a finite, cored isothermal mass distribution:
@@
 To calculate $r_h$, we began by using the stellar mass to calculate the velocity dispersion at the galaxy's effective radius.
-In Kulier12, the galaxy's effective radius $R_{e}$ and velocity dispersion $\sigma(R_e)$ at the effective radius are:
+In Kulier(+15), the galaxy's effective radius $R_{e}$ and velocity dispersion $\sigma(R_e)$ at the effective radius are:
 \begin{equation} \label{re}
@@
 At each iteration in the code, $r_h$ is updated according to the stellar mass and Equations \ref{re} and \ref{sig}.
-The core radius, $r_c$, is recalculated only if an orbiting black hole gets within $r_c$.
+The core radius, $r_c$, is recalculated only if an orbiting black hole enters within $r_c$.
 The work done by diffusion, as described in Section \ref{psd} is calculated, the total potential energy and dynamical friction are updated, and $r_c$ is solved for from Equation 8 in Stone-Ostriker.
@@
 The SMBHs can therefore merge via gravitational wave emission.
-We include gravitational wave recoils following the prescription outlined in Kulier15, which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.
+We include gravitational wave recoils following the prescription outlined in Kulier(+15), which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.
 We assume that a merger will be inevitable when the separation between two SBHs becomes smaller than 1.0 Schwarzschild radius.
@@
 \subsection{Simulation setup}
-Using the merger tree data, orbiting black holes were injected into its host galaxy at redshift z, at a distance from the galactic center of $R_{e}$ (Eqn.
+For each galaxy in the simulations, we only used black holes that would theoretically have merged with the center of the host galaxy within a dynamical friction time, $t_{fric}$, of less than 100 times a Hubble time, with $t_{fric}$ defined from \citet{2008gady.book.....B} as:
+\begin{equation}\label{tfric}
+    t_{fric} = \frac{19}{6}Gyr\left(\frac{R_e}{5kpc}\right)^2\frac{\sigma_{eff}}{200km\,s^{-1}}\frac{10^8\,M_{\odot}}{M_{bh}}
+\end{equation}
+The orbiting black holes were injected into their host galaxy at redshift z, at a distance from the galactic center of $R_{e}$ (Eqn.
 \ref{re}) following galaxy mergers.
 Their initial velocity was arbitrarily chosen to be circular, $v_c = \sqrt{M(R_e)/R_e}$, with $v_x$, $v_y$, and $v_z$ randomly chosen.
-Note: we only inject the BHs into the simulation that have a $t_{fric}$ smaller than 100 times the Hubble time.
 
@@
 \end{equation}
-Gas sound speed, ${ss}_g$, was obtained from:
+Gas sound speed, $c_s$, was obtained from:
 \begin{equation}
-    {ss}_g = \sqrt{1.67T_x/m_p},
+    c_s = \sqrt{1.67T_x/m_p},
 \end{equation}
@@
 \begin{equation}
-    \dot{M}_{acc} = \frac{4{\pi}G^2M^2\rho}{({ss_g}^2+v^2)^{3/2}},
+    \dot{M}_{acc} = \frac{4{\pi}G^2M^2\rho}{(c_s^2+v^2)^{3/2}},
 \end{equation}
@@
 
-Finally, the black hole luminosity is calculated from:
+Finally, the black hole xray luminosity is calculated from:
 \begin{equation}
-    L = 0.1\dot{M}_{acc}{ss_g}^2
+    L_x = 0.01\dot{M}_{acc}c^2
 \end{equation}

### 2019-01-19 paper.tex
Added proper units to Black Hole Luminosity Section
Added Galaxy Gas X-Ray Luminosity section

@@
 \documentclass[english, apj]{emulateapj}
+\usepackage{amsbsy}
+\usepackage{amsmath}
+\usepackage{amstext}
 \usepackage[T1]{fontenc}
 \usepackage[latin9]{inputenc}
+%\usepackage[nobottomtitles]{titlesec}
 \usepackage{array}
@@
 \usepackage{textcomp}
-\usepackage{amsmath}
-\usepackage{amsbsy}
-\usepackage{amstext}
 \usepackage{graphicx}
@@
 
-The merger tree data from Lackner(+12) and Kulier(+15) provided 1,830 galaxies in total.  However, not all the galaxies were suitable for our simulations.  We placed further requirements as follows:
+The merger tree data from Lackner(+12) and Kulier\-(+15) provided 1,830 galaxies in total.  However, not all the galaxies were suitable for our simulations.  We placed further requirements as follows:
 \begin{itemize}
@@
 
-We also compared the stellar masses from Lackner(+12) to  observational and abundance matching data from \citet{2018AstL...44....8K}.
+We also compared the stellar masses from Lackner\-(+12) to  observational and abundance matching data from \citet{2018AstL...44....8K}.
 Figure \ref{fig:stellar1} is a partial, approximate, replication of their Figure 11 (abundance matching line).
@@
 
-\begin{figure}[htbp]
+\begin{figure}[htp]
 \begin{center}
@@
 
-\begin{table}[htbp]
+\begin{table}
 \caption{Galaxy characteristics at z=0}
@@
 \begin{equation}\label{tfric}
-    t_{fric} = \frac{19}{6}Gyr\left(\frac{R_e}{5kpc}\right)^2\frac{\sigma_{eff}}{200km\,s^{-1}}\frac{10^8\,M_{\odot}}{M_{bh}}
+    t_{fric} = \frac{19}{6}Gyr\left(\frac{R_e}{5kpc}\right)^2\frac{\sigma_{eff}}{200km\,s^{-1}}\frac{10^8\,M_{\odot}}{M_{bh}} \text{  s}
 \end{equation}
@@
 \begin{equation}
-    T_x = 10^{(2.50*log \sigma - 6.06)}
+    T_x = 10^{2.50*log(\sigma) - 6.06} \text{  kev}
 \end{equation}
@@
 \begin{equation}
-    \rho_0 = 10^{(0.6log(\sigma) - 25)}
+    \rho_0 = 10^{0.6*log(\sigma) - 25} \text{  g cm}^{-3}
 \end{equation}
@@
 \begin{equation}
-    r_c = 10^{(15.09log(\sigma) - 35.77)}
+    r_c = 10^{2.1*log(\sigma) - 5.3} \text{  cm}
 \end{equation}
 Local gas density ${\rho}$ is obtained from the isothermal beta model:
-\begin{equation}
-    \rho = \frac{\rho_0}{(1+r^2/r_c^2)^{1.5}}
+\begin{equation} \label{beta_model}
+    \rho = \frac{\rho_0}{(1+r^2/r_c^2)^{1.5}} \text{  g cm}^{-3}
 \end{equation}
@@
 \begin{equation}
-    c_s = \sqrt{1.67T_x/m_p},
+    c_s = \sqrt{1.67T_x/m_p} \text{  km s}^{-1},
 \end{equation}
@@
 \begin{equation}
-    \dot{M}_{acc} = \frac{4{\pi}G^2M^2\rho}{(c_s^2+v^2)^{3/2}},
+    \dot{M}_{acc} = \frac{4{\pi}G^2M^2\rho}{(c_s^2+v^2)^{3/2}} \text{  M}_\odot \text{ Myr}^{-1},
 \end{equation}
@@
 \begin{equation}
-    L_x = 0.01\dot{M}_{acc}c^2
+    L_x = 0.01\dot{M}_{acc}c^2 \text{  erg s}^{-1}
 \end{equation}
@@
 \begin{equation}
-    L_{edd} = \num{1.26e38} (M/M_{\odot}) erg/s
+    L_{edd} = \num{1.26e38} (M/M_{\odot}) \text{  erg s}^{-1}
 \end{equation}
+
+\subsection{Galaxy Gas X-Ray Luminosity}
+We compute the x-ray luminosity of the hot gas in the galaxies, adapting Equation 26 from \citet{2012ApJ...754..125C}.
+In lieu of summing over discrete particles, we use the beta model of the gas as defined in our equation \ref{beta_model} and integrate:
+\begin{equation}
+\begin{aligned}
+    L_x ={} \frac{\num{1.2e-24}}{(\mu m_p)^2}\left(\frac{kT_x}{1keV}\right)^{1/2}\rho_0^{2}\;4{\pi} \\
+    \int_{0}^{\infty}\frac{r^2}{(1+r^2/r_c^2)^{3}}\;dr\text{  erg s}^{-1}
+\end{aligned}
+\end{equation}
+The integral evaluates to ${\pi}r_c^3/16$.
+$m_p$ is the mass of a proton and $\mu$ is the mean molecular weight.
+To calculate $\mu$, we use metallicity $Z=2Z_{\odot}=0.0268$, mass fraction of Helium $Y=Y_{\odot}=0.2485$, and mass fraction of Hydrogen $X=0.7247$.
+This results in $\mu=0.606$.
 

### 2019-02-13 paper.tex
More corrections from Jerry.  Started abstract.

@@
 \begin{abstract}
-
+We perform N-body simulations on 13 galaxies extracted from a cosmological simulation of hierarchical structure formation with total mass $10^{12} \msun < M < 10^{13} \msun$ from $4 \ge z \ge 0$.
+We track the dynamical evolution of the orbiting black holes (BHs) around their host central BH.
+Of the 120 orbiting BHs, we find that 50 merge with their host central BHs, 11 are ejected from their respective host galaxies, and 59 are still orbiting at the end of the simulations.
+48 BHs are kicked to a higher orbit after close interaction with the central BH, after which none of them merge with their host.
+We calculate the x-ray luminosities of the orbiting BHs at z=0, and find a range of $10^{18}-10^{37}$ $erg\ s^{-1}$.
 \end{abstract}
@@
 We analyze how the SMBHs are driven into the core of their new host galaxies and how interaction with the host black hole leads to near-ejections or mergers.
+We then estimate the X-ray luminosities expected of the orbiting black holes.
 The final Section \ref{sec:conclusions} contains a discussion of the results and our conclusions.
@@
 \begin{equation} \label{jerry}
-\rho(r) = \frac{\rho_c}{(1+r^2/r_{c}^2)(1+r^2/r_{h}^2)}
+\rho(r) = \frac{\rho_c}{(1+r^2/r_{c}^2)(1+r^2/r_{h}^2)}.
 \end{equation}
@@
 
-In order to parametrize this profile, $r_c$ was given an initial value of 100 pc, which is reasonable for a cored massive system.
+In order to parameterize this profile, $r_c$ was given an initial value of 100 pc, which is reasonable for a cored massive system.
 To calculate $r_h$, we began by using the stellar mass to calculate the velocity dispersion at the galaxy's effective radius.
@@
 \begin{equation} \label{re}
-R_{e} = 2.5 kpc\left(\frac{M_*}{10^{11}M_{\odot}}\right)^{0.73}(1+z)^{-0.98}
+R_{e} = 2.5 kpc\left(\frac{M_*}{10^{11}M_{\odot}}\right)^{0.73}(1+z)^{-0.98},
 \end{equation}
 \begin{equation} \label{sig}
-\sigma(R_{e}) = 190km/s\left(\frac{M_{*}}{10^{11}M_{\odot}}\right)^{0.2}(1+z)^{0.47}
+\sigma(R_{e}) = 190km/s\left(\frac{M_{*}}{10^{11}M_{\odot}}\right)^{0.2}(1+z)^{0.47},
 \end{equation}
@@
 The core radius, $r_c$, is recalculated only if an orbiting black hole enters within $r_c$.
-The work done by diffusion, as described in Section \ref{psd} is calculated, the total potential energy and dynamical friction are updated, and $r_c$ is solved for from Equation 8 in Stone-Ostriker.
+The work done by diffusion, as described in Section \ref{psd} is calculated, the total potential energy and dynamical friction are updated, and $r_c$ is solved for from Equation 8 in Stone-Ostriker based on conservation of energy.
 
@@
 At the moment of the merger, we assume that the spin vectors of the two SBHs are randomly aligned.
+[STILL NEED TO DESCRIBE KICK AFTER MERGER].
 
 Black holes can also eject each other via strong three-body interactions.
-We remove SBHs from the simulations once they move beyond $r_h$, assuming that it will take them more than a Hubble time to find their way back into the center of the host galaxy.
+We remove SBHs from the simulations once they move beyond $r_h$, assuming that it will take them more than a Hubble time to find their way back into the center of the host galaxy, or that they have achieved escape velocity.
 
@@
 \begin{equation}\label{tfric}
-    t_{fric} = \frac{19}{6}Gyr\left(\frac{R_e}{5kpc}\right)^2\frac{\sigma_{eff}}{200km\,s^{-1}}\frac{10^8\,M_{\odot}}{M_{bh}} \text{  s}
+    t_{fric} = \frac{19}{6}Gyr\left(\frac{R_e}{5kpc}\right)^2\frac{\sigma_{eff}}{200km\,s^{-1}}\frac{10^8\,M_{\odot}}{M_{bh}} \text{  s}.
 \end{equation}
@@
 \begin{equation}
-    T_x = 10^{2.50*log(\sigma) - 6.06} \text{  kev}
+    T_x = 10^{2.50*log(\sigma) - 6.06} \text{  kev}.
 \end{equation}
@@
 \begin{equation}
-    \rho_0 = 10^{0.6*log(\sigma) - 25} \text{  g cm}^{-3}
+    \rho_0 = 10^{0.6*log(\sigma) - 25} \text{  g cm}^{-3}.
 \end{equation}
@@
 \begin{equation}
-    r_c = 10^{2.1*log(\sigma) - 5.3} \text{  cm}
+    r_c = 10^{2.1*log(\sigma) - 5.3} \text{  cm}.
 \end{equation}
-Local gas density ${\rho}$ is obtained from the isothermal beta model:
+Local gas density ${\rho}$ is obtained from the isothermal beta model [ADD REFERENCE]:
 \begin{equation} \label{beta_model}
-    \rho = \frac{\rho_0}{(1+r^2/r_c^2)^{1.5}} \text{  g cm}^{-3}
+    \rho = \frac{\rho_0}{(1+r^2/r_c^2)^{1.5}} \text{  g cm}^{-3}.
 \end{equation}
@@
 
-The black hole mass accretion rate is approximated by:
+The net black hole mass accretion rate is approximated by [DO I REFERENCE INAYOSHI, OR ANOTHER SOURCE?]:
 \begin{equation}
-    \dot{M}_{acc} = \frac{4{\pi}G^2M^2\rho}{(c_s^2+v^2)^{3/2}} \text{  M}_\odot \text{ Myr}^{-1},
+    \dot{M}_{acc} = \frac{4{\pi}G^2M^2\rho}{(c_s^2+v^2)^{3/2}} \frac{c_s^2+v^2}{c^2} \text{  M}_\odot \text{ Myr}^{-1},
 \end{equation}
@@
 
-Finally, the black hole xray luminosity is calculated from:
+Finally, the black hole xray luminosity is estimated from [NEED TO ADD INAYOSHI INEFFICIENCY--PLOTS AND BACKGROUND]:
 \begin{equation}
-    L_x = 0.01\dot{M}_{acc}c^2 \text{  erg s}^{-1}
+    L_x = 0.01\dot{M}_{acc}c^2 \text{  erg s}^{-1}.
 \end{equation}
@@
 \begin{equation}
-    L_{edd} = \num{1.26e38} (M/M_{\odot}) \text{  erg s}^{-1}
+    L_{edd} = \num{1.26e38} (M/M_{\odot}) \text{  erg s}^{-1}.
 \end{equation}
@@
     L_x ={} \frac{\num{1.2e-24}}{(\mu m_p)^2}\left(\frac{kT_x}{1keV}\right)^{1/2}\rho_0^{2}\;4{\pi} \\
-    \int_{0}^{\infty}\frac{r^2}{(1+r^2/r_c^2)^{3}}\;dr\text{  erg s}^{-1}
+    \int_{0}^{\infty}\frac{r^2}{(1+r^2/r_c^2)^{3}}\;dr\text{  erg s}^{-1}.
 \end{aligned}
@@
 This results in $\mu=0.606$.
+
+\begin{figure}[htp]
+\begin{center}
+\includegraphics[width=1.0\columnwidth]{plots/Galaxy_Gas_Compared_to_Babyk.png}
+\caption{X-ray luminosity of gas in our galaxies, compared to those from \citet{2018ApJ...857...32B}.}
+\label{fig:galgas1}
+\end{center}
+\end{figure}
 

### 2019-02-18 paper.tex
More edits

@@
 We track the dynamical evolution of the orbiting black holes (BHs) around their host central BH.
-Of the 120 orbiting BHs, we find that 50 merge with their host central BHs, 11 are ejected from their respective host galaxies, and 59 are still orbiting at the end of the simulations.
-48 BHs are kicked to a higher orbit after close interaction with the central BH, after which none of them merge with their host.
+Of the 120 orbiting BHs, we find that 50 merge with their host central BHs, 11 are ejected from their respective host galaxies, 59 are still orbiting at the end of the simulations.
+Across all galaxies, 48 BHs are kicked to a higher orbit after close interaction with the central BH, after which none of them merge with their hosts.
 We calculate the x-ray luminosities of the orbiting BHs at z=0, and find a range of $10^{18}-10^{37}$ $erg\ s^{-1}$.
@@
 How common are mergers of massive black holes?
-For the galaxies themselves we know that minor mergers are frequent from the observed (\citet{2010ApJ...718L..73V}, \citet{2008ApJ...677L...5V}) evolution of the size and mass of these systems.
-But assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2008MNRAS.390..192S}, \citet{2009MNRAS.394.2255S}, \citet{2013MNRAS.433L...1S}, \citet{2014ApJ...789..156M}, \citet{2015ApJ...799..178K}, \citet{2018ApJ...856...42S}, \citet{2018arXiv180403143I}).
-But we do not often see multiple SMBHs at the centers of massive ellipticals.
+For the galaxies themselves we know that minor mergers are frequent from the observed (\citet{2010ApJ...718L..73V}, \citet{2008ApJ...677L...5V}, \citet{2019MNRAS.484..595M}) evolution of the size and mass of these systems, but assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2008MNRAS.390..192S}, \citet{2009MNRAS.394.2255S}, \citet{2013MNRAS.433L...1S}, \citet{2014ApJ...789..156M}, \citet{2015ApJ...799..178K}, \citet{2018ApJ...856...42S}, \citet{2018arXiv180403143I}).
+However, we do not often see multiple SMBHs at the centers of massive ellipticals.
 So, what does happen?
@@
 The present paper also addresses this purported dynamical solution, focusing attention on the large fraction of lower mass black holes that remain to be detected as they orbit in massive galaxies.
-What we argue in this paper is that as a result of the N-body interactions among the infalling black holes some are ejected, some remain in extended orbits and some (the few most massive ones) do in fact merge, but these do not exceed the PTA limits, and the orbiting ones should be detectable via their ability to accrete gas and emit radiation.
+What we argue in this paper is that, as a result of the N-body interactions among the infalling black holes, some are ejected, some remain in extended orbits and some (the few most massive ones) do in fact merge, but these do not exceed the PTA limits, and the orbiting ones should be detectable via their ability to accrete gas and emit radiation.
 
@@
 
-The net black hole mass accretion rate is approximated by [DO I REFERENCE INAYOSHI, OR ANOTHER SOURCE?]:
+The net black hole mass accretion rate is approximated by \citet{2018MNRAS.476.1412I} and \citet{2019arXiv190202349I}:
 \begin{equation}
@@
 
-The Eddington limit is known to be:
+The Eddington limit is defined as:
 \begin{equation}
@@
 \begin{center}
-\includegraphics[width=1.0\columnwidth]{plots/Galaxy_Gas_Compared_to_Babyk.png}
+\includegraphics[width=1.0\columnwidth]{plots/Lx_our_Galaxies_compared_to_Babyk_data.png}
 \caption{X-ray luminosity of gas in our galaxies, compared to those from \citet{2018ApJ...857...32B}.}

### 2019-02-19 paper.tex
Added/change more BH plots.  Re-organized results sections.

@@
 
+\section{Results}\label{sec:results}
+
+\begin{figure}[ht]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{"plots/Fractions All Galaxies".png}
+\caption{Fractions Merged/Ejected/Orbiting at z=0, by mass bin}
+\label{fig:fmeo}
+\end{center}
+\end{figure}
+
+\begin{figure}[ht]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{plots/"Summary Results All Galaxies".png}
+\caption{Histogram of merged, ejected, and orbiting SMBHs}
+\label{fig:meosmbh}
+\end{center}
+\end{figure}
+
+\subsection{Galaxy Gas X-Ray Luminosity}
+We compute the x-ray luminosity of the hot gas in the galaxies, adapting Equation 26 from \citet{2012ApJ...754..125C}.
+In lieu of summing over discrete particles, we use the beta model of the gas as defined in our equation \ref{beta_model} and integrate:
+\begin{equation}
+\begin{aligned}
+    L_x ={} \frac{\num{1.2e-24}}{(\mu m_p)^2}\left(\frac{kT_x}{1keV}\right)^{1/2}\rho_0^{2}\;4{\pi} \\
+    \int_{0}^{\infty}\frac{r^2}{(1+r^2/r_c^2)^{3}}\;dr\text{  erg s}^{-1}.
+\end{aligned}
+\end{equation}
+The integral evaluates to ${\pi}r_c^3/16$.
+$m_p$ is the mass of a proton and $\mu$ is the mean molecular weight.
+To calculate $\mu$, we use metallicity $Z=2Z_{\odot}=0.0268$, mass fraction of Helium $Y=Y_{\odot}=0.2485$, and mass fraction of Hydrogen $X=0.7247$.
+This results in $\mu=0.606$.
+
+\begin{figure}[htp]
+\begin{center}
+\includegraphics[width=1.0\columnwidth]{plots/Lx_our_Galaxies_compared_to_Babyk_data.png}
+\caption{X-ray luminosity of gas in our galaxies, compared to those from \citet{2018ApJ...857...32B}.}
+\label{fig:galgas1}
+\end{center}
+\end{figure}
+
 \subsection{Black Hole Luminosity}
@@
 
-Finally, the black hole xray luminosity is estimated from [NEED TO ADD INAYOSHI INEFFICIENCY--PLOTS AND BACKGROUND]:
+Finally, the black hole xray luminosity is estimated from:
 \begin{equation}
@@
 
-\subsection{Galaxy Gas X-Ray Luminosity}
-We compute the x-ray luminosity of the hot gas in the galaxies, adapting Equation 26 from \citet{2012ApJ...754..125C}.
-In lieu of summing over discrete particles, we use the beta model of the gas as defined in our equation \ref{beta_model} and integrate:
-\begin{equation}
-\begin{aligned}
-    L_x ={} \frac{\num{1.2e-24}}{(\mu m_p)^2}\left(\frac{kT_x}{1keV}\right)^{1/2}\rho_0^{2}\;4{\pi} \\
-    \int_{0}^{\infty}\frac{r^2}{(1+r^2/r_c^2)^{3}}\;dr\text{  erg s}^{-1}.
-\end{aligned}
-\end{equation}
-The integral evaluates to ${\pi}r_c^3/16$.
-$m_p$ is the mass of a proton and $\mu$ is the mean molecular weight.
-To calculate $\mu$, we use metallicity $Z=2Z_{\odot}=0.0268$, mass fraction of Helium $Y=Y_{\odot}=0.2485$, and mass fraction of Hydrogen $X=0.7247$.
-This results in $\mu=0.606$.
-
 \begin{figure}[htp]
 \begin{center}
-\includegraphics[width=1.0\columnwidth]{plots/Lx_our_Galaxies_compared_to_Babyk_data.png}
-\caption{X-ray luminosity of gas in our galaxies, compared to those from \citet{2018ApJ...857...32B}.}
-\label{fig:galgas1}
-\end{center}
-\end{figure}
-
-\subsection{Description of Simulations}
-\begin{table*}
-\centering
-\caption{Galaxy characteristics}
-\begin{tabular}{c| c c| c c| c c}
- & \multicolumn{2}{c}{$M_{gal}$ [$M_{\odot}$]} & 
-\multicolumn{2}{c}{$M_{*}$ [$M_{\odot}$]} & 
-\multicolumn{2}{c}{$M_{BH}$ [$M_{\odot}$]} \\
-\hline
-Galaxy & Init & Final & Init & Final & Init & Final \\
- \hline
-A & $7.42\times10^{11}$ & $1.09\times10^{14}$  & $1.22\times10^{11}$ & $1.75\times10^{13}$ & $4.80\times10^{6}$ & $2.19\times10^{9}$\\
-B & $1.11\times10^{12}$ & $3.41\times10^{13}$ & $1.80\mathrm{3}{11}$ & $5.58\times10^{12}$ & $1.94\times10^{8}$ & $1.46\times10^{9}$\\
-C & $7.23\times10^{10}$ & $3.48\times10^{12}$ & $1.18\times10^{10}$ & $5.68\times10^{11}$ & $9.47\times10^{4}$ & $2.70\times10^{8}$\\
-D & $3.92\times10^{10}$ & $1.34\times10^{12}$ & $6.47\times10^{9}$ & $2.20\times10^{11}$ & $9.95\times10^{5}$ & $8.32\times10^{7}$\\
-\end{tabular}
-\end{table*}
-
-\section{Results}\label{sec:results}
-\begin{figure}[ht]
-\begin{center}
-\includegraphics[width=0.45\textwidth]{"plots/Fractions All Galaxies".png}
-\caption{Fractions Merged/Ejected/Orbiting at z=0, by mass bin}
-\label{fig:fmeo}
+\includegraphics[width=1.0\columnwidth]{plots/radiative_efficiency.png}
+\caption{Radiative efficiency of Orbiting Black Holes at z=0}
+\label{fig:rad_eff}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{plots/"Summary Results All Galaxies".png}
-\caption{Histogram of merged, ejected, and orbiting SMBHs}
-\label{fig:meosmbh}
-\end{center}
-\end{figure}
-
-\begin{figure}[ht]
-\begin{center}
-\includegraphics[width=0.45\textwidth]{plots/"Final Luminosities of Oriting BHs".png}
+\includegraphics[width=0.45\textwidth]{plots/"Final Luminosities of Orbiting BHs".png}
 \caption{Luminosities of Orbiting BHs at z=0}
@@
 \section{Conclusions}\label{sec:conclusions}
-What do we want to say?
 
-\section*{Acknowledgements}
-
+\section{Acknowledgements}
 The authors would like to thank Andrea Kulier and Claire Lackner for providing merger tree data.

### 2019-02-20 paper.tex
Worked mainly on Results section.

@@
 
-\subsection{AR-Chain code}
-Summary of the code and the modifications we made.
+\subsection{Simulation Physics}
+In this section, we describe the underlying physics of our simulations, including choice of galaxy background potential, BH diffusion through the galaxy, and gravitational wave kicks as a result of mergers.
 
@@
 \begin{equation}\label{tfric}
-    t_{fric} = \frac{19}{6}Gyr\left(\frac{R_e}{5kpc}\right)^2\frac{\sigma_{eff}}{200km\,s^{-1}}\frac{10^8\,M_{\odot}}{M_{bh}} \text{  s}.
+    t_{fric} = \frac{19}{6}\left(\frac{R_e}{5kpc}\right)^2\frac{\sigma_{eff}}{200km\,s^{-1}}\frac{10^8\,M_{\odot}}{M_{bh}} \text{  Gyr}.
 \end{equation}
-The orbiting black holes were injected into their host galaxy at redshift z, at a distance from the galactic center of $R_{e}$ (Eqn.
-\ref{re}) following galaxy mergers.
-Their initial velocity was arbitrarily chosen to be circular, $v_c = \sqrt{M(R_e)/R_e}$, with $v_x$, $v_y$, and $v_z$ randomly chosen.
+The orbiting black holes were injected into their host galaxy at redshift z, at a distance from the galactic center of $R_{e}$ (Equation \ref{re}) following galaxy mergers.
+Their initial velocity was arbitrarily chosen to be circular, $v_c = \sqrt{GM(R_e)/R_e}$, with $v_x$, $v_y$, and $v_z$ randomly chosen.
 
 \section{Results}\label{sec:results}
+Here we review the primary results of our simulations, focusing on the various interactions of the orbiting black holes with their host SMBHs and the final luminosity characteristics of those that did not merge.
+
+\subsection{Mergers, Ejections and Kicks}
+
+Figure \ref{fig:fmeo}
 
@@
 \label{fig:meosmbh}
+\end{center}
+\end{figure}
+
+\begin{figure}[ht]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{plots/"Final Radius v Mass of Orbiting BHs_corrected_".png}
+\caption{Final Radii of remaining orbital black holes at z=0}
+\label{fig:mvr}
 \end{center}
@@
 
-Finally, the black hole xray luminosity is estimated from:
+Finally, the black hole x-ray luminosity is estimated from:
 \begin{equation}

### 2019-03-05 paper.tex
Modified most plots to reflect removing galaxies 1 and 51.  Also included more Jerry edits.

@@
 \begin{abstract}
-We perform N-body simulations on 13 galaxies extracted from a cosmological simulation of hierarchical structure formation with total mass $10^{12} \msun < M < 10^{13} \msun$ from $4 \ge z \ge 0$.
+We perform N-body simulations on 13 galaxies extracted from a cosmological simulation of hierarchical structure formation with total mass in the range $10^{12} \msun < M < 10^{13} \msun$ from $4 \ge z \ge 0$.
 We track the dynamical evolution of the orbiting black holes (BHs) around their host central BH.
@@
 Across all galaxies, 48 BHs are kicked to a higher orbit after close interaction with the central BH, after which none of them merge with their hosts.
-We calculate the x-ray luminosities of the orbiting BHs at z=0, and find a range of $10^{18}-10^{37}$ $erg\ s^{-1}$.
+We calculate the x-ray luminosities of the orbiting massive BHs at z=0, and find a range of $10^{18}-10^{37}$ $erg\ s^{-1}$.
 \end{abstract}
@@
 We will argue in this paper that a very common outcome--especially for the lower mass black holes--is for the injected objects to remain as orbiting X-ray sources in normal massive galaxies waiting to be identified by current observational techniques.
+
+There is no "final parsec problem," and the opposite problem of too many BH mergers is also avoided when it is realized that we are dealing with a small N-body system rather than a series of two-body problems.
 
@@
 \hline
- \num{9.18e13} 	&	 \num{2.19e9} 	&	\num{1.75e13} 	&	\num{5.14e11}  \\
- \num{7.75e13} 	&	 \num{5.27e9}	&	\num{1.52e13} 	&	\num{4.00e11}  \\
  \num{2.85e13} 	&	 \num{1.46e9}	&	\num{5.58e12} 	&	\num{3.30e11}  \\
@@
 
-Figure \ref{fig:fmeo}
-
-\begin{figure}[ht]
-\begin{center}
-\includegraphics[width=0.45\textwidth]{"plots/Fractions All Galaxies".png}
-\caption{Fractions Merged/Ejected/Orbiting at z=0, by mass bin}
-\label{fig:fmeo}
-\end{center}
-\end{figure}
-
 \begin{figure}[ht]
@@
 \begin{center}
-\includegraphics[width=1.0\columnwidth]{plots/Lx_our_Galaxies_compared_to_Babyk_data.png}
+\includegraphics[width=1.0\columnwidth]{plots/"Lx of our Galaxies compared to Babyk data".png}
 \caption{X-ray luminosity of gas in our galaxies, compared to those from \citet{2018ApJ...857...32B}.}
@@
 \begin{center}
-\includegraphics[width=1.0\columnwidth]{plots/radiative_efficiency.png}
+\includegraphics[width=1.0\columnwidth]{plots/"radiative efficiency".png}
 \caption{Radiative efficiency of Orbiting Black Holes at z=0}

### 2019-03-09 paper.tex
Updates from Overleaf

@@
 \subsection{Mergers, Ejections and Kicks}
+Figure \ref{fig:meosmbh} shows the distribution of merged, ejected and orbiting black holes across all galaxy simulations as a function of guest black hole mass.
 
@@
 \label{fig:meosmbh}
+\end{center}
+\end{figure}
+
+\begin{figure}[ht]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{plots/q_merger_fraction.png}
+\caption{Fraction of mergers per BH mass ratio.
+Each point represents the fraction of galaxy mergers that led to BH mergers for each BH merger ratio bin.
+Note that a "bin" at each point is comprised of the mass ratio at that point up to, but not including, the next point on the x-axis.}
+\label{fig:q_merge_fraction}
 \end{center}

### 2019-03-10 paper.tex
Mostly additions to Results section.

@@
 Figure \ref{fig:meosmbh} shows the distribution of merged, ejected and orbiting black holes across all galaxy simulations as a function of guest black hole mass.
+Given the log distribution of masses and using $10^7\, M_{\odot}$ as the approximate midpoint, one can see the general trend of larger mass BHs tending to merge with their respective host BH, with     the lower mass BHs continuing to wander at $z=0$.
 
@@
 \includegraphics[width=0.45\textwidth]{plots/"Summary Results All Galaxies".png}
-\caption{Histogram of merged, ejected, and orbiting SMBHs}
+\caption{Histogram of merged, ejected, and orbiting SMBHs at z=0.}
 \label{fig:meosmbh}
@@
 \end{figure}
+
+\begin{figure}[ht]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{plots/kicked_stats.png}
+\caption{Histogram of kicked SMBHs at z=0.}
+\label{fig:kicked_stats}
+\end{center}
+\end{figure}
+
+As can be seen in Figure \ref{fig:kicked_stats}, the vast majority of larger SMBHs ($\gtrapprox\, 10^7\, M_{\odot}$) are not kicked to higher orbits nor ejected from their galaxies, which at least partly explains why most of the merged SMBHs are in the greater mass brackets.
+In contrast, most of the SMBHs below $10^7\, M_{\odot}$ are kicked (with a few of them being ejected).
+in our simulations, no black holes that are kicked to higher orbits ever merged with their central host SMBH.
 

### 2019-03-17 paper.tex
Added more plots and text to Results section.

--- 2019-03-09 paper.tex
@@
 \section{Methods}\label{sec:methods}
-%\begin{figure*}[htbp]
+%\begin{figure}[htbp]
 %\begin{center}
@@
 
-\begin{figure}[htp]
+\begin{figure}[htbp]
 \begin{center}
@@
 
-\begin{table}
+\begin{table}[htbp]
+\begin{center}
 \caption{Galaxy characteristics at z=0}
@@
 \end{tabular}
-
+\end{center}
 \label{table:gal_char}
@@
 
-\subsection{Mergers, Ejections and Kicks}
+\subsection{Mergers, Ejections/Kicks and Orbiting SMBHs}
+
+\subsubsection{Overview of Results}\label{sec:results_overview}
 Figure \ref{fig:meosmbh} shows the distribution of merged, ejected and orbiting black holes across all galaxy simulations as a function of guest black hole mass.
+
+Of the 86 SMBHs used for the simulations, 37 black holes merged with their respective host black hole within a Hubble time, 42 remained orbiting at the end of the simulations, and 7 were ejected from their galaxies as a result of sufficiently large kicks due to three-body interactions with the host and other black holes.
+
+Given the log distribution of masses, one can see the general trend of larger mass BHs ($\gtrapprox\, 10^7\, M_{\odot}$) tending to merge with their respective host BH, while lower mass BHs continue to wander at $z=0$.
+However, there is some overlap with some BHs greater than $10^7\, M_{\odot}$ still orbiting and those less than $10^7\, M_{\odot}$ having merged.
+
+\subsubsection{Mergers}\label{sec:mergers}
+The tendency of larger mass black holes to merge with their host can perhaps be more clearly seen by looking at the merger mass ratio between the incoming black hole and the host.
+Figure \ref{fig:q_merge_fraction} displays the fraction of galaxy mergers that result in black hole mergers versus the merger mass ratio, defined as $m_2/m_1$, where $m_2$ is the orbiting black hole and $m_1$ is the host black hole.
+The plot monotonically increases with increasing mass ratio, reaching nearly unity for mass ratio of $10^{-1}$, meaning nearly all galaxy mergers with a black hole mass ratio of $10^{-1}$ resulted in the orbiting black hole merging with the host.
+
+In figure \ref{fig:time_to_merge} we present the time it took for the merging guest black holes to merge with their host.
+As can be seen in the plot, although there is a fair amount of variation, the general trend is a decreasing time to merge as orbiting black hole mass increases.
+
+\subsubsection{Kicked, Ejected and Orbiting Black Holes}\label{sec:kicked_orbiting}
+Of the 34 orbiting black holes at $z=0$, all but 8 of them were kicked to higher orbits at some point in their traversal of their host galaxy.
+If one counts the 7 ejected black holes, then of the 41 SMBHs that had not eventually merged with their host, 33 of them were kicked out of the galactic core as a result of three-body interactions.
+If they didn't merge, it wasn't for a lack of effort.
+
+Figure \ref{fig:kicked_stats} shows the mass distribution of kicked and not-kicked black holes, including those that merged and those that did not merge.
+The vast majority of larger SMBHs ($\gtrapprox\, 10^7\, M_{\odot}$) were not kicked to higher orbits nor ejected from their galaxies, which at least partly explains why most of the merged SMBHs are in the greater mass range.
+In contrast, most of the SMBHs below $10^7\, M_{\odot}$ are kicked (with a few of them being ejected).
+In our simulations, no black holes that are kicked to higher orbits ever returned to merge with their central host SMBH.
+
+Figure \ref{fig:mvr} is a realization of the final radii of the remaining wandering black holes at $z=0$.
+There does not appear to be a correlation between mass and final radius.
+However, it is evident from the plot that all but one of the black holes that had not been kicked by $z=0$ have mostly approached and entered within the galactic core radius, $r_c$.
 
@@
 \begin{center}
+\includegraphics[width=0.45\textwidth]{plots/time_to_merge.png}
+\caption{Time required for BHs to merge with host SMBH}
+\label{fig:time_to_merge}
+\end{center}
+\end{figure}
+
+\begin{figure}[ht]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{plots/kicked_stats.png}
+\caption{Histogram of kicked and not-kicked SMBHs at z=0.}
+\label{fig:kicked_stats}
+\end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+\begin{center}
 \includegraphics[width=0.45\textwidth]{plots/"Final Radius v Mass of Orbiting BHs_corrected_".png}
@@
 \end{equation}
+
 The integral evaluates to ${\pi}r_c^3/16$.

### 2019-04-05 paper.tex
More Jerry edits; changed title of paper

@@
 
-\title{Cannibalism among the supermassive black holes}
+\title{Supermassive Black Hole Dynamics: A Proposal for a New Class of X-Ray Sources}
 
@@
 We perform N-body simulations on 13 galaxies extracted from a cosmological simulation of hierarchical structure formation with total mass in the range $10^{12} \msun < M < 10^{13} \msun$ from $4 \ge z \ge 0$.
-We track the dynamical evolution of the orbiting black holes (BHs) around their host central BH.
+We track the dynamical evolution of the orbiting black holes (BHs) around their host central BHs.
 Of the 120 orbiting BHs, we find that 50 merge with their host central BHs, 11 are ejected from their respective host galaxies, 59 are still orbiting at the end of the simulations.
-Across all galaxies, 48 BHs are kicked to a higher orbit after close interaction with the central BH, after which none of them merge with their hosts.
-We calculate the x-ray luminosities of the orbiting massive BHs at z=0, and find a range of $10^{18}-10^{37}$ $erg\ s^{-1}$.
+Across all galaxies, 48 BHs are kicked to a higher orbit after close interactions with the central BH, after which none of them merge with their hosts.
+These orbiting BHs should be detectable by their anomalous (not LMXRB) spectra.
+The x-ray luminosities of the orbiting massive BHs at z=0 are in the range $10^{23}-10^{37}$ $erg\ s^{-1}$, with median value $10^{29}$ $erg\ s^{-1}$.
 \end{abstract}
@@
 So, what does happen?
-One paper (\citet{2018MNRAS.473.3410R}) has indicated that dynamical interactions among multiple black holes, which eject a non-negligible fraction of the mass, may solve this problem.
+One paper (\citet{2018MNRAS.473.3410R}) has indicated that dynamical interactions among multiple orbiting black holes, which will eject a non-negligible fraction of the mass, may solve this problem.
 The present paper also addresses this purported dynamical solution, focusing attention on the large fraction of lower mass black holes that remain to be detected as they orbit in massive galaxies.
@@
 In Section \ref{sec:results}, we show the results of our XX exemplary simulations of galaxies growing with time and acquiring new SMBHs.
-We analyze how the SMBHs are driven into the core of their new host galaxies and how interaction with the host black hole leads to near-ejections or mergers.
+We analyze how the SMBHs spiral into the core of their new host galaxies due to dynamical friction, and how interactions with the host black hole and other orbiting BHs leads to near-ejections or mergers.
 We then estimate the X-ray luminosities expected of the orbiting black holes.
@@
 The third term introduces a change in velocity perpendicular to the direction of motion of the SBH.
-It is a randomly oriented vector, and hence causes the SBHs to execute a random walk in phase space.
+It is a randomly oriented vector, and hence causes the SBHs to depart from smooth orbits due to the small random velocity kicks.
 The last two terms will establish that the SBHs are ultimately in energy equipartition with the background stars.
@@
 The change of energy, $\mbox{d}E_{BH}$, of the orbiting black hole due to phase-space diffusion is given back to the stellar background potential, with $\mbox{d}E = -\mbox{d}E_{BH}$.
-As a consequence of this energy transfer, inspiralling black holes will cause an expansion of the NSC.
+As a consequence of this energy transfer, inspiralling black holes will cause an expansion of the stellar system.
 For this purpose we calculate the change in potential energy, $\mbox{d}W$, of the stellar system using
@@
 Figure \ref{fig:q_merge_fraction} displays the fraction of galaxy mergers that result in black hole mergers versus the merger mass ratio, defined as $m_2/m_1$, where $m_2$ is the orbiting black hole and $m_1$ is the host black hole.
-The plot monotonically increases with increasing mass ratio, reaching nearly unity for mass ratio of $10^{-1}$, meaning nearly all galaxy mergers with a black hole mass ratio of $10^{-1}$ resulted in the orbiting black hole merging with the host.
+The plot monotonically increases with increasing mass ratio, reaching nearly unity for mass ratio of $10^{-1}$, meaning nearly all galaxy mergers with a black hole mass ratio greater than $10^{-1}$ resulted in the orbiting black hole merging with the host.
 
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{plots/"Final Radius v Mass of Orbiting BHs_corrected_".png}
+\includegraphics[width=0.45\textwidth]{plots/"Final Radius v Mass of Orbiting BHs".png}
 \caption{Final Radii of remaining orbital black holes at z=0}

### 2019-08-11 paper.tex
Added Kohei plots (at end of paper).

@@
 We track the dynamical evolution of the orbiting black holes (BHs) around their host central BHs.
-Of the 120 orbiting BHs, we find that 50 merge with their host central BHs, 11 are ejected from their respective host galaxies, 59 are still orbiting at the end of the simulations.
-Across all galaxies, 48 BHs are kicked to a higher orbit after close interactions with the central BH, after which none of them merge with their hosts.
+Of the 120 orbiting BHs, we find that 50 merge with their host central BHs, 11 are ejected from their respective host galaxies, and 59 are still orbiting at the end of the simulations.
+Across all galaxies, 48 BHs are kicked to a higher orbit after close interactions with the central BHs, after which none of them merge with their hosts.
 These orbiting BHs should be detectable by their anomalous (not LMXRB) spectra.
@@
 We include gravitational wave recoils following the prescription outlined in Kulier(+15), which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.
-We assume that a merger will be inevitable when the separation between two SBHs becomes smaller than 1.0 Schwarzschild radius.
-At the moment of the merger, we assume that the spin vectors of the two SBHs are randomly aligned.
+We assume that a merger will be inevitable when the separation between two SMBHs becomes smaller than 1.0x the Schwarzschild radius.
+At the moment of the merger, we also assume that the spin vectors of the two SBHs are randomly aligned.
 [STILL NEED TO DESCRIBE KICK AFTER MERGER].
@@
 
+%\begin{figure}[ht]
+%\begin{center}
+%\includegraphics[width=0.45\%textwidth]{plots/"Final %Luminosities of Orbiting %BHs".png}
+%\caption{Luminosities of %Orbiting BHs at z=0}
+%\label{fig:loobhs}
+%\end{center}
+%\end{figure}
+
 \begin{figure}[ht]
 \begin{center}
-\includegraphics[width=0.45\textwidth]{plots/"Final Luminosities of Orbiting BHs".png}
-\caption{Luminosities of Orbiting BHs at z=0}
+\includegraphics[width=0.45\textwidth]{plots/"luminosities_final".png}
+\caption{Kohei Ratios of Orbiting BHs at z=0}
 \label{fig:loobhs}
+\end{center}
+\end{figure}
+
+\begin{figure}[ht]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{plots/"Final Luminosities using Kohei factor".png}
+\caption{Luminosity Distribution of Orbiting BHs at z=0}
+\label{fig:ldobhs}
 \end{center}

### 2019-09-18 paper.tex
Mostly enlarged figures, modified captions.

@@
 \begin{center}
-\includegraphics[width=1.0\columnwidth]{plots/stellar_to_halo_ratio.png}
+\includegraphics[width=0.5\textwidth]{plots/stellar_to_halo_ratio.png}
 \caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.  Purple dots shown is example of our rescaled stellar masses}
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{plots/"Summary Results All Galaxies".png}
-\caption{Histogram of merged, ejected, and orbiting SMBHs at z=0.}
+\includegraphics[width=0.5\textwidth]{plots/"Summary Results All Galaxies".png}
+\caption{Histogram of merged, ejected, and orbiting SMBHs at z=0 as a function of BH mass.}
 \label{fig:meosmbh}
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{plots/q_merger_fraction.png}
-\caption{Fraction of mergers per BH mass ratio.
+\includegraphics[width=0.5\textwidth]{plots/q_merger_fraction.png}
+\caption{Fraction of BHs that merge with the central BH as a function of the BH mass ratio.
 Each point represents the fraction of galaxy mergers that led to BH mergers for each BH merger ratio bin.
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{plots/time_to_merge.png}
-\caption{Time required for BHs to merge with host SMBH}
+\includegraphics[width=0.5\textwidth]{plots/time_to_merge.png}
+\caption{Time required for BHs to merge with host SMBH after galaxy merger.}
 \label{fig:time_to_merge}
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{plots/kicked_stats.png}
+\includegraphics[width=0.5\textwidth]{plots/kicked_stats.png}
 \caption{Histogram of kicked and not-kicked SMBHs at z=0.}
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{plots/"Final Radius v Mass of Orbiting BHs".png}
+\includegraphics[width=0.5\textwidth]{plots/"Final Radius v Mass of Orbiting BHs".png}
 \caption{Final Radii of remaining orbital black holes at z=0}
@@
 \includegraphics[width=1.0\columnwidth]{plots/"Lx of our Galaxies compared to Babyk data".png}
-\caption{X-ray luminosity of gas in our galaxies, compared to those from \citet{2018ApJ...857...32B}.}
+\caption{X-ray luminosity of hot gas in our galaxies, compared to those from \citet{2018ApJ...857...32B}.}
 \label{fig:galgas1}
@@
 
-\begin{figure}[htp]
-\begin{center}
-\includegraphics[width=1.0\columnwidth]{plots/"radiative efficiency".png}
-\caption{Radiative efficiency of Orbiting Black Holes at z=0}
-\label{fig:rad_eff}
-\end{center}
-\end{figure}
-
 %\begin{figure}[ht]
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{plots/"luminosities_final".png}
-\caption{Kohei Ratios of Orbiting BHs at z=0}
+\includegraphics[width=0.5\textwidth]{plots/"luminosities_final".png}
+\caption{Luminosity of orbiting BHs at z=0 as per Inayoshi (2019).}
 \label{fig:loobhs}
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{plots/"Final Luminosities using Kohei factor".png}
-\caption{Luminosity Distribution of Orbiting BHs at z=0}
+\includegraphics[width=0.5\textwidth]{plots/"Final Luminosities using Kohei factor".png}
+\caption{Xray Luminosity Distribution of Orbiting BHs at z=0.}
 \label{fig:ldobhs}

### 2019-10-19 paper.tex
Enlarged two plots.
Updated plots.  Added section describing wandering black holes within the influence radius of the central black hole.

@@
 \begin{abstract}
-We perform N-body simulations on 13 galaxies extracted from a cosmological simulation of hierarchical structure formation with total mass in the range $10^{12} \msun < M < 10^{13} \msun$ from $4 \ge z \ge 0$.
-We track the dynamical evolution of the orbiting black holes (BHs) around their host central BHs.
-Of the 120 orbiting BHs, we find that 50 merge with their host central BHs, 11 are ejected from their respective host galaxies, and 59 are still orbiting at the end of the simulations.
-Across all galaxies, 48 BHs are kicked to a higher orbit after close interactions with the central BHs, after which none of them merge with their hosts.
+We perform N-body simulations on 11 galaxies extracted from a cosmological simulation of hierarchical structure formation with total mass in the range $10^{12} \msun < M < 10^{13} \msun$ from $4 \ge z \ge 0$.
+After mergers, we track the dynamical evolution of the orbiting black holes (BHs) around their host central BHs.
+Of the 86 orbiting BHs, we find that 36 merge with their host central BHs, 13 are ejected from their respective host galaxies, and 37 are still orbiting at the end of the simulations.
+Across all galaxies, 33 BHs are kicked to a higher orbit after close interactions with the central BHs, after which only one of them merged with their hosts.
 These orbiting BHs should be detectable by their anomalous (not LMXRB) spectra.
-The x-ray luminosities of the orbiting massive BHs at z=0 are in the range $10^{23}-10^{37}$ $erg\ s^{-1}$, with median value $10^{29}$ $erg\ s^{-1}$.
+The x-ray luminosities of the orbiting massive BHs at z=0 are in the range $10^{25}-10^{43}$ $erg\ s^{-1}$, with median value $10^{32}$ $erg\ s^{-1}$.
 \end{abstract}
@@
 
-Here we look at the merger history of 13 exemplary galaxies across the galaxy mass spectrum extracted from a cosmological simulation of hierarchical structure formation.
+Here we look at the merger history of 11 exemplary galaxies across the galaxy mass spectrum extracted from a cosmological simulation of hierarchical structure formation.
 We investigate how, after merging with incoming galaxies, SMBHs sink into the cores of the hosts and interact with the resident black hole.
@@
 We present the few-body integration code, \textsc{AR-Chain} that we used for our simulations of SMBH dynamics, and the modifications we made to this code in order to deal with a host galaxy's gravitational potential.
-In Section \ref{sec:results}, we show the results of our XX exemplary simulations of galaxies growing with time and acquiring new SMBHs.
+In Section \ref{sec:results}, we show the results of our 11 exemplary simulations of galaxies growing with time and acquiring new SMBHs.
 We analyze how the SMBHs spiral into the core of their new host galaxies due to dynamical friction, and how interactions with the host black hole and other orbiting BHs leads to near-ejections or mergers.
@@
 
-Of the 86 SMBHs used for the simulations, 37 black holes merged with their respective host black hole within a Hubble time, 42 remained orbiting at the end of the simulations, and 7 were ejected from their galaxies as a result of sufficiently large kicks due to three-body interactions with the host and other black holes.
+Of the 86 SMBHs used for the simulations, 36 black holes merged with their respective host black hole within a Hubble time, 37 remained orbiting at the end of the simulations, and 13 were ejected from their galaxies as a result of sufficiently large kicks due to three-body interactions with the host and other black holes.
 
@@
 \subsubsection{Kicked, Ejected and Orbiting Black Holes}\label{sec:kicked_orbiting}
-Of the 34 orbiting black holes at $z=0$, all but 8 of them were kicked to higher orbits at some point in their traversal of their host galaxy.
-If one counts the 7 ejected black holes, then of the 41 SMBHs that had not eventually merged with their host, 33 of them were kicked out of the galactic core as a result of three-body interactions.
+Of the 37 orbiting black holes at $z=0$, 18 of them were kicked to higher orbits at some point in their traversal of their host galaxy.
+If one counts the 13 ejected black holes, then of the 50 SMBHs that had not eventually merged with their host, 32 of them were kicked out of the galactic core as a result of three-body interactions.
 If they didn't merge, it wasn't for a lack of effort.
@@
 
+\begin{figure}[htbp]
+\vspace{20pt}%
+\begin{center}
+\includegraphics[width=0.5\textwidth]{plots/"Lx of our Galaxies compared to Babyk data".png}
+\caption{X-ray luminosity of hot gas in our galaxies, compared to those from \citet{2018ApJ...857...32B}.}
+\label{fig:galgas1}
+\end{center}
+\end{figure}
+
 \subsection{Galaxy Gas X-Ray Luminosity}
@@
 
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=1.0\columnwidth]{plots/"Lx of our Galaxies compared to Babyk data".png}
-\caption{X-ray luminosity of hot gas in our galaxies, compared to those from \citet{2018ApJ...857...32B}.}
-\label{fig:galgas1}
-\end{center}
-\end{figure}
-
 \subsection{Black Hole Luminosity}
@@
 \begin{equation}
-    r_c = 10^{2.1*log(\sigma) - 5.3} \text{  cm}.
+    r_c = 10^{2.1*log(\sigma) - 5.3} \text{  kpc}.
 \end{equation}
@@
 \end{equation}
+
 Gas sound speed, $c_s$, was obtained from:
 \begin{equation}
-    c_s = \sqrt{1.67T_x/m_p} \text{  km s}^{-1},
+    C_s = \sqrt{1.67T_x/m_p} \text{  km s}^{-1},
 \end{equation}
@@
 \begin{equation}
-    \dot{M}_{acc} = \frac{4{\pi}G^2M^2\rho}{(c_s^2+v^2)^{3/2}} \frac{c_s^2+v^2}{c^2} \text{  M}_\odot \text{ Myr}^{-1},
+    \dot{M}_{acc} = \frac{4{\pi}G^2M^2\rho}{(C_s^2+v^2)^{3/2}} \text{  M}_\odot \text{ Myr}^{-1},
 \end{equation}
@@
 
+\subsection{Central Black Hole Influence}
+Within the influence radius of the central black hole, which is defined as the radius at which the total mass of the galaxy within that radius (stars + dark matter) equals the mass of the central black hole, the gas density is much higher than otherwise (NEED REFERENCES?).
+{WHAT DO WE SAY ABOUT THE VELOCITY FOLLOWING THE KEPLER PROFILE WITHIN THE INFLUENCE RADIUS?}.
+Starting with the equation for hydrostatic equilibrium,
+\begin{equation}
+    C_{s}^2\frac{dln\rho}{dr}= -\frac{GM(r)}{r^2},
+\end{equation}
+we can integrate with respect to r, leading to 
+\begin{equation}
+    ln\frac{\rho}{\rho_1} = \frac{GM}{C_{s}^2}\left(\frac{1}{r} - \frac{1}{r_1}\right),
+\end{equation}
+where $\rho$ is the gas density at the location of the wandering black hole, $\rho_1$ is the density at the radius where the central black hole mass equals the galaxy mass, $r$ is the distance of the wandering black hole from the center, and $r_1$ is the radius where the central black hole mass equals the galaxy mass.
+
+Figure \ref{fig:wui} shows the difference in luminosity when taking into account the influence of the central black hole for the wandering black holes that were within the influence radius.
+In all cases, the final luminosity is higher than the original luminosity.
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{plots/"Comparison of L_x versus radius with and without BH Influence".png}
+\caption{Difference in x-ray luminosity of wandering black holes within the influence radius of the central black hole.
+Red dots are the originally calculated luminosity, not taking the CBH influence into account.
+Green dots are the final luminosities, taking the central BH influence into account.}
+\label{fig:wui}
+\end{center}
+\end{figure}
+
 \section{Conclusions}\label{sec:conclusions}

### 2019-11-08 paper.tex
Edits from Jerry.  Also, last push before switching to MNRAS template.

@@
 
-\title{Supermassive Black Hole Dynamics: A Proposal for a New Class of X-Ray Sources}
+\title{The Fates of Merging Supermassive Black Holes and A Proposal for a New Class of X-Ray Sources}
 
@@
 These orbiting BHs should be detectable by their anomalous (not LMXRB) spectra.
-The x-ray luminosities of the orbiting massive BHs at z=0 are in the range $10^{25}-10^{43}$ $erg\ s^{-1}$, with median value $10^{32}$ $erg\ s^{-1}$.
+The x-ray luminosities of the orbiting massive BHs at z=0 are in the range $10^{25}-10^{43}$ $erg\ s^{-1}$, with an undetectable median value $10^{32}$ $erg\ s^{-1}$.
+However, the most luminous $\sim$$5\%$ should be detectable.
 \end{abstract}
@@
 Combinations of these options are also possible with the spin induced kick at merger leading to an ejection or extended orbit of the merged black hole.
-We now know from pulsar timing measurements (ADD REFERENCES) that the gravitational wave background is probably too low for most galaxy mergers (mass-weighted) (but see \cite{2018NatCo...9..573M}) to lead to BH mergers, but the outcome remains uncertain.
+We now know from pulsar timing measurements (\citet{2008MNRAS.390..192S}, \citet{2018ApJ...856...42S}, \citet{2016APS..APRR18003T}) that the gravitational wave background is probably too low for most galaxy mergers (mass-weighted) (but see \cite{2018NatCo...9..573M}) to lead to BH mergers, but the outcome remains uncertain.
 We will argue in this paper that a very common outcome--especially for the lower mass black holes--is for the injected objects to remain as orbiting X-ray sources in normal massive galaxies waiting to be identified by current observational techniques.
 
-There is no "final parsec problem," and the opposite problem of too many BH mergers is also avoided when it is realized that we are dealing with a small N-body system rather than a series of two-body problems.
+There is no "final parsec problem," and the opposite problem of too many BH mergers is also avoided when it is realized that we are dealing with a small N-body system rather than a series of two-body problems (cf \citet{2018MNRAS.473.3410R}).
 
@@
 For the galaxies themselves we know that minor mergers are frequent from the observed (\citet{2010ApJ...718L..73V}, \citet{2008ApJ...677L...5V}, \citet{2019MNRAS.484..595M}) evolution of the size and mass of these systems, but assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2008MNRAS.390..192S}, \citet{2009MNRAS.394.2255S}, \citet{2013MNRAS.433L...1S}, \citet{2014ApJ...789..156M}, \citet{2015ApJ...799..178K}, \citet{2018ApJ...856...42S}, \citet{2018arXiv180403143I}).
-However, we do not often see multiple SMBHs at the centers of massive ellipticals.
+However, we do not often see multiple SMBHs at the centers of massive ellipticals (but see \citet{2016MNRAS.463.2145C}).
 So, what does happen?
@@
 The present paper also addresses this purported dynamical solution, focusing attention on the large fraction of lower mass black holes that remain to be detected as they orbit in massive galaxies.
-What we argue in this paper is that, as a result of the N-body interactions among the infalling black holes, some are ejected, some remain in extended orbits and some (the few most massive ones) do in fact merge, but these do not exceed the PTA limits, and the orbiting ones should be detectable via their ability to accrete gas and emit radiation.
+What we argue in this paper is that, as a result of the N-body interactions among the infalling black holes, some are ejected, some remain in extended orbits and some (the few most massive ones) do in fact merge, but these do not exceed the PTA limits, and some of the orbiting ones might be detectable via their ability to accrete gas and emit radiation.
 
@@
 However, even when thermal energy from supernova feedback is considered, the effects may be reduced due to the energy being quickly radiated away by rapidly cooling surrounding gas (\citet{1996ApJS..105...19K}).
-A second common reason for overproduction of stars in cosmological simulations is a lack of modeling for AGN feedback, which may be responsible for a phenomenon called the "cooling flow paradox" (\citet{2001MNRAS.321L..20F}) that suppresses star formation.
+A second common reason for overproduction of stars in cosmological simulations is a lack of modeling for AGN feedback, which may be responsible for solving the phenomenon called the "cooling flow paradox" (\citet{2001MNRAS.321L..20F}) that suppresses star formation.
 
@@
 \includegraphics[width=0.5\textwidth]{plots/stellar_to_halo_ratio.png}
-\caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.  Purple dots shown is example of our rescaled stellar masses}
+\caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.  Purple dots shown are examples of our rescaled stellar masses}
 \label{fig:stellar1}
@@
 If one counts the 13 ejected black holes, then of the 50 SMBHs that had not eventually merged with their host, 32 of them were kicked out of the galactic core as a result of three-body interactions.
-If they didn't merge, it wasn't for a lack of effort.
+If they did not merge, it was not for a lack of effort.
 
@@
 \subsection{Central Black Hole Influence}
-Within the influence radius of the central black hole, which is defined as the radius at which the total mass of the galaxy within that radius (stars + dark matter) equals the mass of the central black hole, the gas density is much higher than otherwise (NEED REFERENCES?).
-{WHAT DO WE SAY ABOUT THE VELOCITY FOLLOWING THE KEPLER PROFILE WITHIN THE INFLUENCE RADIUS?}.
-Starting with the equation for hydrostatic equilibrium,
+Within the influence radius of the central black hole, which is defined as the radius at which the total mass of the galaxy within that radius (stars + dark matter) equals the mass of the central black hole, the gas density is much higher than otherwise, and equation \eqref{beta_model} cannot be used in the region where the BH Kepler potential dominates.
+Starting with the equation for hydrostatic equilibrium, assuming isothermality,
 \begin{equation}
@@
 \section{Conclusions}\label{sec:conclusions}
+We performed N-body simulations on 11 galaxies ranging in mass between $10^{12} \msun < M < 10^{13} \msun$, from $4 \ge z \ge 0$.
+We found that $42\%$ of the orbiting black holes merged with their host galaxy, while another $43\%$ remained in orbit at $z=0$.
+With an x-ray luminosity range of $10^{25}-10^{43}$ $erg\ s^{-1}$
 

### 2019-11-08 paper.tex
First push successfully compiling with MNRAS format

@@
-\documentclass[english, apj]{emulateapj}
+%\documentclass[english, apj]{emulateapj}
+\documentclass[english, backref,breaklinks,colorlinks,citecolor=blue, usenatbib]{mnras}
 \usepackage{amsbsy}
@@
 %\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
-\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
-\usepackage[all]{hypcap}
+\usepackage{hyperref}
+\usepackage{hypcap}
 
@@
 
-\author{Charles Zivancev\altaffilmark{1}, Jeremiah P. Ostriker\altaffilmark{1,3}, Andreas H.W. K\"upper\altaffilmark{1,2}}
-\altaffiltext{1}{Department of Astronomy, Columbia University, 550 West 120th Street, New York, NY 10027, USA}
-\altaffiltext{2}{Hubble Fellow}
-\altaffiltext{3}{Princeton University, New Jersey, USA}
-\email{Correspondence to: csz2104@columbia.edu}
+\author{Charles Zivancev,$^{1}$ 
+Jeremiah P. Ostriker,$^{1,3}$ 
+Andreas H.W. K\"upper$^{1,2}$
+\\
+$^{1}$Department of Astronomy, Columbia University, 550 West 120th Street, New York, NY 10027, USA\\
+$^{2}$Hubble Fellow\\
+$^{3}$Princeton University, New Jersey, USA}
+\thanks{Correspondence to: csz2104@columbia.edu}
 
@@
 
-\keywords{Galaxy: kinematics and dynamics}
+\begin{keywords}
+Galaxy: kinematics and dynamics
+\end{keywords}
 
@@
 \section{Methods}\label{sec:methods}
-%\begin{figure}[htbp]
+%\begin{figure}
 %\begin{center}
@@
 Lackner(+12), which is the source of our stellar masses, noted that the efficiency of star formation in their simulations, defined as $f_*=M_*/M_{DM}(\Omega_{DM}/\Omega_b)$, was approximately 0.6.
-Compared with the expected range of $0.10 \lessapprox f_* \lessapprox 0.15$ that they referenced from \citet{2012ApJ...746...95L}, their stellar masses were a factor of roughly 4 times greater.
+Compared with the expected range of $0.10 \loa f_* \loa 0.15$ that they referenced from \citet{2012ApJ...746...95L}, their stellar masses were a factor of roughly 4 times greater.
 
@@
 
-\begin{figure}[htbp]
-\begin{center}
+\begin{figure}
+%\begin{center}
 \includegraphics[width=0.5\textwidth]{plots/stellar_to_halo_ratio.png}
@@
 \label{fig:stellar1}
-\end{center}
+%\end{center}
 \end{figure}
 
-\begin{table}[htbp]
+\begin{table}
 \begin{center}
@@
 
-Given the log distribution of masses, one can see the general trend of larger mass BHs ($\gtrapprox\, 10^7\, M_{\odot}$) tending to merge with their respective host BH, while lower mass BHs continue to wander at $z=0$.
+Given the log distribution of masses, one can see the general trend of larger mass BHs ($\goa\, 10^7\, M_{\odot}$) tending to merge with their respective host BH, while lower mass BHs continue to wander at $z=0$.
 However, there is some overlap with some BHs greater than $10^7\, M_{\odot}$ still orbiting and those less than $10^7\, M_{\odot}$ having merged.
@@
 Figure \ref{fig:kicked_stats} shows the mass distribution of kicked and not-kicked black holes, including those that merged and those that did not merge.
-The vast majority of larger SMBHs ($\gtrapprox\, 10^7\, M_{\odot}$) were not kicked to higher orbits nor ejected from their galaxies, which at least partly explains why most of the merged SMBHs are in the greater mass range.
+The vast majority of larger SMBHs ($\goa\, 10^7\, M_{\odot}$) were not kicked to higher orbits nor ejected from their galaxies, which at least partly explains why most of the merged SMBHs are in the greater mass range.
 In contrast, most of the SMBHs below $10^7\, M_{\odot}$ are kicked (with a few of them being ejected).
@@
 
-\begin{figure}[htbp]
+\begin{figure}
 \begin{center}
@@
 
-\begin{figure}[htbp]
+\begin{figure}
 \vspace{20pt}%
@@
 
-\begin{figure}[ht]
+\begin{figure}
 \begin{center}
@@
 In all cases, the final luminosity is higher than the original luminosity.
-\begin{figure}[H]
+\begin{figure}
 \begin{center}

### 2019-11-09 paper.tex
Modified title page to use MNRAS template.  There's more to fix in order to get it MNRAS-ready

@@
-%\documentclass[english, apj]{emulateapj}
-\documentclass[english, backref,breaklinks,colorlinks,citecolor=blue, usenatbib]{mnras}
-\usepackage{amsbsy}
-\usepackage{amsmath}
-\usepackage{amstext}
+%\documentclass[english, backref,breaklinks,colorlinks,citecolor=blue, usenatbib]{mnras}
+%\usepackage{amsbsy}
+%\usepackage{amsmath}
+%\usepackage{amstext}
+%\usepackage[T1]{fontenc}
+%\usepackage[latin9]{inputenc}
+%%\usepackage[nobottomtitles]{titlesec}
+%\usepackage{array}
+%\usepackage{rotating}
+%\usepackage{units}
+%\usepackage{textcomp}
+%\usepackage{graphicx}
+%\usepackage{url}
+%\usepackage{babel}
+%\usepackage{float}
+%\usepackage{savesym}
+%\savesymbol{tablenum}
+%\usepackage{siunitx}
+%\restoresymbol{SIX}{tablenum}
+%%\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
+%\usepackage{hyperref}
+%\usepackage{hypcap}
+
+%\makeatletter
+
+%\newcommand{\msun}{\mbox{$\,{\rm M}_\odot$}}
+
+%\sloppy
+
+% mnras_guide.tex
+%
+% MNRAS LaTeX user guide
+%
+% v3.0 released 22 May 2015
+% (version numbers match those of mnras.cls)
+%
+% Copyright (C) Royal Astronomical Society 2015
+% Authors:
+% Keith T. Smith (Royal Astronomical Society)
+
+% Change log
+%
+% v3.0   September 2013 - May 2015
+%    First version: complete rewrite of the user guide
+%    Basic structure taken from mnras_template.tex by the same author
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Basic setup. Most papers should leave these options alone.
+\documentclass[fleqn,usenatbib,useAMS]{mnras}
+
+%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
+
+% Only include extra packages if you really need them. Common packages are:
+\usepackage{graphicx}	% Including figure files
+\usepackage{amsmath}	% Advanced maths commands
+\usepackage{amssymb}	% Extra maths symbols
+\usepackage{multicol}        % Multi-column entries in tables
+\usepackage{bm}		% Bold maths symbols, including upright Greek
+\usepackage{pdflscape}	% Landscape pages
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%%
+
+% Please keep new commands to a minimum, and use \newcommand not \def to avoid
+% overwriting existing commands. Example:
+%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
+\newcommand{\kms}{\,km\,s$^{-1}$} % kilometres per second
+\newcommand{\bibtex}{\textsc{Bib}\!\TeX} % bibtex. Not quite the correct typesetting, but close enough
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Use vector fonts, so it zooms properly in on-screen viewing software
+% Don't change these lines unless you know what you are doing
 \usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
-%\usepackage[nobottomtitles]{titlesec}
-\usepackage{array}
-\usepackage{rotating}
-\usepackage{units}
-\usepackage{textcomp}
-\usepackage{graphicx}
-\usepackage{url}
-\usepackage{babel}
-\usepackage{float}
-\usepackage{savesym}
-\savesymbol{tablenum}
-\usepackage{siunitx}
-\restoresymbol{SIX}{tablenum}
-%\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
-\usepackage{hyperref}
-\usepackage{hypcap}
+\usepackage{ae,aecompl}
 
-\makeatletter
+% MNRAS is set in Times font. If you don't have this installed (most LaTeX
+% installations will be fine) or prefer the old Computer Modern fonts, comment
+% out the following line
+\usepackage{newtxtext,newtxmath}
+% Depending on your LaTeX fonts installation, you might get better results with one of these:
+%\usepackage{mathptmx}
+%\usepackage{txfonts}
 
-\newcommand{\msun}{\mbox{$\,{\rm M}_\odot$}}
+%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
 
-\sloppy
+% Title of the paper, and the short title which is used in the headers.
+% Keep the title short and informative.
+\title[MNRAS]{The Fates of Merging Supermassive Black Holes and A Proposal for a New Class of X-Ray Sources}
 
-\providecommand{\tabularnewline}{\\}
-% Alter some LaTeX defaults for better treatment of figures:
-    % See p.105 of "TeX Unbound" for suggested values.
-    % See pp. 199-200 of Lamport's "LaTeX" book for details.
-    %   General parameters, for ALL pages:
-    \renewcommand{\topfraction}{0.9}	% max fraction of floats at top
-    \renewcommand{\bottomfraction}{0.8}	% max fraction of floats at bottom
-    %   Parameters for TEXT pages (not float pages):
-    \setcounter{topnumber}{2}
-    \setcounter{bottomnumber}{2}
-    \setcounter{totalnumber}{4}     % 2 may work better
-    \setcounter{dbltopnumber}{2}    % for 2-column pages
-    \renewcommand{\dbltopfraction}{0.9}	% fit big float above 2-col. text
-    \renewcommand{\textfraction}{0.07}	% allow minimal text w. figs
-    %   Parameters for FLOAT pages (not text pages):
-    \renewcommand{\floatpagefraction}{0.7}	% require fuller float pages
-	% N.B.: floatpagefraction MUST be less than topfraction !!
-    \renewcommand{\dblfloatpagefraction}{0.7}	% require fuller float pages
-
-	% remember to use [htp] or [htpb] for placement
-
-\begin{document}
-
-\title{The Fates of Merging Supermassive Black Holes and A Proposal for a New Class of X-Ray Sources}
-
-\author{Charles Zivancev,$^{1}$ 
-Jeremiah P. Ostriker,$^{1,3}$ 
-Andreas H.W. K\"upper$^{1,2}$
+% The list of authors, and the short list which is used in the headers.
+% If you need two or more lines of authors, add an extra line using \newauthor
+\author[]{
+Charles Zivancev$^{1}$\thanks{Contact e-mail: \href{mailto:csz2104@columbia.edu}{csz2104@columbia.edu}},
+Jeremiah Ostriker$^{1}$,
+Andreas H.W. K\"upper$^{2}$
 \\
+% List of institutions
 $^{1}$Department of Astronomy, Columbia University, 550 West 120th Street, New York, NY 10027, USA\\
 $^{2}$Hubble Fellow\\
-$^{3}$Princeton University, New Jersey, USA}
-\thanks{Correspondence to: csz2104@columbia.edu}
+}
+% These dates will be filled out by the publisher
+\date{Last updated 2019 Nov 09; in original form 2019 November 9}
+
+% Enter the current year, for the copyright statements etc.
+\pubyear{2019}
+
+% Don't change these lines
+\begin{document}
+\label{firstpage}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
+\maketitle
 

### 2019-11-09 paper.tex
Finished bringing paper into compliance with format for MNRAS.

@@
 \begin{abstract}
-We perform N-body simulations on 11 galaxies extracted from a cosmological simulation of hierarchical structure formation with total mass in the range $10^{12} \msun < M < 10^{13} \msun$ from $4 \ge z \ge 0$.
+We perform N-body simulations on 11 galaxies extracted from a cosmological simulation of hierarchical structure formation with total mass in the range $10^{12} M_{\sun} < M < 10^{13} M_{\sun}$ from 4 $\gid$ z $\gid$ 0.
 After mergers, we track the dynamical evolution of the orbiting black holes (BHs) around their host central BHs.
@@
 We investigate how, after merging with incoming galaxies, SMBHs sink into the cores of the hosts and interact with the resident black hole.
-We show that gravitational interactions of multiple SMBHs are most probable in high-mass galaxies with total mass $10^{12} \msun < M < 10^{13} \msun$.
+We show that gravitational interactions of multiple SMBHs are most probable in high-mass galaxies with total mass $10^{12} M_{\sun} < M < 10^{13} M_{\sun}$.
 Galaxies with lower masses have too few mergers with SMBH hosting galaxies.
@@
 \begin{center}
-\caption{Galaxy characteristics at z=0}
+\caption{Galaxy characteristics at z=0. Units are M$\sun$.}
 \begin{tabular} {|c | c | c| c|}
@@
 \hline
- \num{2.85e13} 	&	 \num{1.46e9}	&	\num{5.58e12} 	&	\num{3.30e11}  \\
- \num{2.48e13} 	&	 \num{2.40e9}	&	\num{4.80e12} 	&	\num{2.25e11}  \\
- \num{2.29e13} 	&	 \num{1.22e9}	&	\num{4.46e12} 	&	\num{2.68e11}  \\
- \num{1.18e13} 	&	 \num{3.62e9}	&	\num{2.32e12} 	&	\num{2.83e11}  \\
- \num{1.03e13} 	&	 \num{9.85e9}	&	\num{1.96e12} 	&	\num{1.62e11}  \\
- \num{1.00e13} 	&	 \num{9.32e9}	&	\num{1.95e12} 	&	\num{2.49e11}  \\
- \num{8.92e12} 	&	 \num{5.60e9}	&	\num{1.74e12} 	&	\num{3.20e11}  \\
- \num{8.56e12} 	&	 \num{6.86e9}	&	\num{1.62e12} 	&	\num{1.83e11}  \\
- \num{6.94e12} 	&	 \num{2.02e9}	&	\num{1.72e12} 	&	\num{1.51e11}  \\
- \num{6.29e12} 	&	 \num{1.22e9}	&	\num{1.23e12} 	&	\num{1.87e11}  \\
- \num{1.84e12} 	&	 \num{2.21e9}	&	\num{5.52e11} 	&	\num{6.42e10}  \\
+ 2.85 $\times 10^{13}$ 	&	 1.46 $\times 10^9$	&	5.58 $\times 10^{12}$ 	&	3.30 $\times 10^{11}$  \\
+ 2.48 $\times 10^{13}$ 	&	 2.40 $\times 10^9$	&	4.80 $\times 10^{12}$ 	&	2.25 $\times 10^{11}$  \\
+ 2.29 $\times 10^{13}$ 	&	 1.22 $\times 10^9$	&	4.46 $\times 10^{12}$ 	&	2.68 $\times 10^{11}$  \\
+ 1.18 $\times 10^{13}$ 	&	 3.62 $\times 10^9$	&	2.32 $\times 10^{12}$ 	&	2.83 $\times 10^{11}$  \\
+ 1.03 $\times 10^{13}$ 	&	 9.85 $\times 10^9$	&	1.96 $\times 10^{12}$ 	&	1.62 $\times 10^{11}$  \\
+ 1.00 $\times 10^{13}$ 	&	 9.32 $\times 10^9$	&	1.95 $\times 10^{12}$ 	&	2.49 $\times 10^{11}$  \\
+ 8.92 $\times 10^{12}$ 	&	 5.60 $\times 10^9$	&	1.74 $\times 10^{12}$ 	&	3.20 $\times 10^{11}$  \\
+ 8.56 $\times 10^{12}$ 	&	 6.86 $\times 10^9$	&	1.62 $\times 10^{12}$ 	&	1.83 $\times 10^{11}$  \\
+ 6.94 $\times 10^{12}$ 	&	 2.02 $\times 10^9$	&	1.72 $\times 10^{12}$ 	&	1.51 $\times 10^{11}$  \\
+ 6.29 $\times 10^{12}$ 	&	 1.22 $\times 10^9$	&	1.23 $\times 10^{12}$ 	&	1.87 $\times 10^{11}$  \\
+ 1.84 $\times 10^{12}$ 	&	 2.21 $\times 10^9$	&	5.52 $\times 10^{11}$ 	&	6.42 $\times 10^{10}$  \\
 \hline
@@
 \begin{aligned}
-    L_x ={} \frac{\num{1.2e-24}}{(\mu m_p)^2}\left(\frac{kT_x}{1keV}\right)^{1/2}\rho_0^{2}\;4{\pi} \\
+    L_x ={} \frac{1.2 \times 10^{-24}}{(\mu m_p)^2}\left(\frac{kT_x}{1keV}\right)^{1/2}\rho_0^{2}\;4{\pi} \\
     \int_{0}^{\infty}\frac{r^2}{(1+r^2/r_c^2)^{3}}\;dr\text{  erg s}^{-1}.
@@
 \begin{equation}
-    L_{edd} = \num{1.26e38} (M/M_{\odot}) \text{  erg s}^{-1}.
+    L_{edd} = 1.26 \times 10^{38} (M/M_{\odot}) \text{  erg s}^{-1}.
 \end{equation}
@@
 \section{Conclusions}\label{sec:conclusions}
-We performed N-body simulations on 11 galaxies ranging in mass between $10^{12} \msun < M < 10^{13} \msun$, from $4 \ge z \ge 0$.
-We found that $42\%$ of the orbiting black holes merged with their host galaxy, while another $43\%$ remained in orbit at $z=0$.
-With an x-ray luminosity range of $10^{25}-10^{43}$ $erg\ s^{-1}$
+We performed N-body simulations on 11 galaxies ranging in mass between $10^{12}$ M$_{\sun}$ < M < $10^{13}$ M$_{\sun}$, from 4 $\gid$ z $\gid$ 0.
+We found that 42$\%$ of the orbiting black holes merged with their host galaxy, while another 43$\%$ remained in orbit at $z=0$.
+With an x-ray luminosity range of $10^{25}-10^{43}$ $erg\ s^{-1}$.
 
@@
 
-\bibliographystyle{apj}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
+
+% The best way to enter references is to use BibTeX:
+
+\bibliographystyle{mnras}
 \bibliography{biblio}
 
-%\begin{thebibliography}{}
+% Don't change these lines
+\bsp	% typesetting comment
+\label{lastpage}
+\end{document}
 
-%\bibitem[\protect\citeauthoryear{Aarseth}{2003}]{Aarseth03}
-%Aarseth, S.~J., 2003, Gravitational N-Body Simulations (Cambridge University Press)
-
-%\bibitem[\protect\citeauthoryear{K{\"u}pper et al.}{2011}]{Kupper11} 
-%K{\"u}pper, A.~H.~W., Maschberger, T., Kroupa, P., Baumgardt, H., 2011, MNRAS, 417, 2300
-
-%\end{thebibliography}
-\end{document}
+% End of mnras_guide.tex

### 2019-11-12 paper.tex
Removed old document headings.
More edits to paper from previous meeting with Jerry.

@@
-%\documentclass[english, backref,breaklinks,colorlinks,citecolor=blue, usenatbib]{mnras}
-%\usepackage{amsbsy}
-%\usepackage{amsmath}
-%\usepackage{amstext}
-%\usepackage[T1]{fontenc}
-%\usepackage[latin9]{inputenc}
-%%\usepackage[nobottomtitles]{titlesec}
-%\usepackage{array}
-%\usepackage{rotating}
-%\usepackage{units}
-%\usepackage{textcomp}
-%\usepackage{graphicx}
-%\usepackage{url}
-%\usepackage{babel}
-%\usepackage{float}
-%\usepackage{savesym}
-%\savesymbol{tablenum}
-%\usepackage{siunitx}
-%\restoresymbol{SIX}{tablenum}
-%%\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
-%\usepackage{hyperref}
-%\usepackage{hypcap}
-
-%\makeatletter
-
-%\newcommand{\msun}{\mbox{$\,{\rm M}_\odot$}}
-
-%\sloppy
-
 % mnras_guide.tex
@@
 At the moment of the merger, we also assume that the spin vectors of the two SBHs are randomly aligned.
-[STILL NEED TO DESCRIBE KICK AFTER MERGER].
+
+A result of the anisotropic emission of gravitational waves is that the merged binary often experiences a linear kick in the opposite direction of the emission of the GW due to conservation of linear momentum.
+This kick can result in velocities of the merged binary from approximately $200-5000\ km s^{-1}$ (see \citet{2007PhRvL..98w1101G}, \citet{2007PhRvL..98i1101G}, \citet{2007PhRvL..98w1102C}, \citet{2011PhRvL.107w1102L}).
+In our simulations, the binaries never stray more than a few tens of parsecs from the nucleus of the host galaxies.
 
@@
 \end{equation}
-Local gas density ${\rho}$ is obtained from the isothermal beta model [ADD REFERENCE]:
+Local gas density ${\rho}$ is obtained from the isothermal beta model (\citet{1962AJ.....67..471K}, \citet{1976A&A....49..137C}, \citet{1978A&A....70..677C}):
 \begin{equation} \label{beta_model}
@@
 We performed N-body simulations on 11 galaxies ranging in mass between $10^{12}$ M$_{\sun}$ < M < $10^{13}$ M$_{\sun}$, from 4 $\gid$ z $\gid$ 0.
-We found that 42$\%$ of the orbiting black holes merged with their host galaxy, while another 43$\%$ remained in orbit at $z=0$.
-With an x-ray luminosity range of $10^{25}-10^{43}$ $erg\ s^{-1}$.
+A total of 86 orbiting black holes were followed in our simulations, resulting in 42$\%$ mergers with their host galaxy, while another 43$\%$ remained in orbit at $z=0$.
+Those remaining orbiting black holes had x-ray luminosities in the range of $10^{25}-10^{43}$ $erg\ s^{-1}$.
+The median luminosity of $10^{32} erg\ s^{-1}$ would be undetectable with present instruments, although the top $5\%$ most luminous from this set could be detectable.
 

### 2019-11-15 paper.tex
Final edits before sending to certain references for opinions

@@
 
-\begin{figure}[ht]
+\begin{figure}
 \begin{center}
 \includegraphics[width=0.5\textwidth]{plots/"Summary Results All Galaxies".png}
-\caption{Histogram of merged, ejected, and orbiting SMBHs at z=0 as a function of BH mass.}
+\caption{Histogram of merged, ejected, and orbiting SMBHs at z=0 as a function of BH mass.  Colored arrows along x-axis represent median masses of respective sets.}
 \label{fig:meosmbh}
@@
 
-\begin{figure}[ht]
+\begin{figure}
 \begin{center}
 \includegraphics[width=0.5\textwidth]{plots/time_to_merge.png}
-\caption{Time required for BHs to merge with host SMBH after galaxy merger.}
+\caption{Time required for BHs to merge with host SMBH after galaxy merger.  Form for fitted line is $-0.379M_{BH}+5.766$ in log-log space.}
 \label{fig:time_to_merge}
@@
 
-\begin{figure}[ht]
+\begin{figure}
 \begin{center}
 \includegraphics[width=0.5\textwidth]{plots/kicked_stats.png}
-\caption{Histogram of kicked and not-kicked SMBHs at z=0.}
+\caption{Histogram of kicked and not-kicked SMBHs at z=0.  Colored arrows along x-axis represent median masses of respective sets.}
 \label{fig:kicked_stats}
@@
 \includegraphics[width=0.5\textwidth]{plots/"Final Radius v Mass of Orbiting BHs".png}
-\caption{Final Radii of remaining orbital black holes at z=0}
+\caption{Final Radii of remaining orbital black holes at z=0.}
 \label{fig:mvr}
@@
 
-%\begin{figure}[ht]
+%\begin{figure}
 %\begin{center}

### 2019-12-07 paper.tex
Final final edit before sending to certain references for opinions.
Edits from people who sent feedback

@@
 How common are mergers of massive black holes?
-For the galaxies themselves we know that minor mergers are frequent from the observed (\citet{2010ApJ...718L..73V}, \citet{2008ApJ...677L...5V}, \citet{2019MNRAS.484..595M}) evolution of the size and mass of these systems, but assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2008MNRAS.390..192S}, \citet{2009MNRAS.394.2255S}, \citet{2013MNRAS.433L...1S}, \citet{2014ApJ...789..156M}, \citet{2015ApJ...799..178K}, \citet{2018ApJ...856...42S}, \citet{2018arXiv180403143I}).
+For the galaxies themselves we know that minor mergers are frequent from the observed (\citet{2010ApJ...718L..73V}, \citet{2008ApJ...677L...5V}, \citet{2019MNRAS.484..595M}) evolution of the size and mass of these systems, but assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2008MNRAS.390..192S}, \citet{2009MNRAS.394.2255S}, \citet{2013MNRAS.433L...1S}, \citet{2014ApJ...789..156M}, \citet{2015ApJ...799..178K}, \citet{2018ApJ...856...42S}, \citet{2018arXiv180403143I}, \citet{2018ApJ...863L..36I}).
 However, we do not often see multiple SMBHs at the centers of massive ellipticals (but see \citet{2016MNRAS.463.2145C}).
@@
 \subsection{Merger tree Data}
-The merger tree data that was used as the input to our simulations is the result of previous work by \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C} (hereafter Cen(+11)), \citet{2012MNRAS.425..641L} (hereafter Lackner(+12)), and \citet{2015ApJ...799..178K} (hereafter Kulier(+15)).
+The merger tree data that was used as the input to our simulations is the result of previous work by \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C} (hereafter Cen(+11) and known as the LAOZI simulations \citet{2014ApJ...781...38C}), as well as  \citet{2012MNRAS.425..641L} (hereafter Lackner(+12)), and \citet{2015ApJ...799..178K} (hereafter Kulier(+15)).
 A brief synopsis of the work that led to our input data is described below.
@@
 To calculate $r_h$, we began by using the stellar mass to calculate the velocity dispersion at the galaxy's effective radius.
-In Kulier(+15), the galaxy's effective radius $R_{e}$ and velocity dispersion $\sigma(R_e)$ at the effective radius are:
+In \citet{2014ApJ...789..156M}, the galaxy's effective radius $R_{e}$ and velocity dispersion $\sigma(R_e)$ at the effective radius are:
 \begin{equation} \label{re}
@@
 \includegraphics[width=0.5\textwidth]{plots/"Final Luminosities using Kohei factor".png}
-\caption{Xray Luminosity Distribution of Orbiting BHs at z=0.}
+\caption{Xray Luminosity Distribution of Orbiting BHs at z=0.  Green region under curve represents approximate range of detectable orbiting black holes.}
 \label{fig:ldobhs}

### 2019-12-18 paper.tex
Updated Inayoshi references

@@
 How common are mergers of massive black holes?
-For the galaxies themselves we know that minor mergers are frequent from the observed (\citet{2010ApJ...718L..73V}, \citet{2008ApJ...677L...5V}, \citet{2019MNRAS.484..595M}) evolution of the size and mass of these systems, but assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2008MNRAS.390..192S}, \citet{2009MNRAS.394.2255S}, \citet{2013MNRAS.433L...1S}, \citet{2014ApJ...789..156M}, \citet{2015ApJ...799..178K}, \citet{2018ApJ...856...42S}, \citet{2018arXiv180403143I}, \citet{2018ApJ...863L..36I}).
+For the galaxies themselves we know that minor mergers are frequent from the observed (\citet{2010ApJ...718L..73V}, \citet{2008ApJ...677L...5V}, \citet{2019MNRAS.484..595M}) evolution of the size and mass of these systems, but assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2008MNRAS.390..192S}, \citet{2009MNRAS.394.2255S}, \citet{2013MNRAS.433L...1S}, \citet{2014ApJ...789..156M}, \citet{2015ApJ...799..178K}, \citet{2018ApJ...856...42S}, \citet{2018MNRAS.479.4017I}, \citet{2018ApJ...863L..36I}).
 However, we do not often see multiple SMBHs at the centers of massive ellipticals (but see \citet{2016MNRAS.463.2145C}).
@@
 
-The net black hole mass accretion rate is approximated by \citet{2018MNRAS.476.1412I} and \citet{2019arXiv190202349I}:
+The net black hole mass accretion rate is approximated by \citet{2018MNRAS.476.1412I} and \citet{2019MNRAS.486.5377I}:
 \begin{equation}

### 2019-12-18 paper.tex
Updated equation 27 to include radiative efficiency factor epsilon.

@@
 \begin{equation}
-    \dot{M}_{acc} = \frac{4{\pi}G^2M^2\rho}{(C_s^2+v^2)^{3/2}} \text{  M}_\odot \text{ Myr}^{-1},
+    \dot{M}_{acc} = \epsilon\frac{4{\pi}G^2M^2\rho}{(C_s^2+v^2)^{3/2}} \text{  M}_\odot \text{ Myr}^{-1},
 \end{equation}
-where M is black hole mass, G is the gravitational constant, and v is the black hole velocity.
+where $\epsilon$ is the radiative efficiency as calculated in Equation 13 of \citet{2019MNRAS.486.5377I}, M is black hole mass, G is the gravitational constant, and v is the black hole velocity.
 

### 2020-01-02 paper.tex
Modified Black Hole Luminosity text and equations; uploaded modified L_x histogram and lognormal plot.

--- 2019-12-18 paper.tex
@@
 \subsubsection{Phase-space diffusion} \label{psd}
+THIS SECTION TAKEN VERBATIM FROM \citet{2017MNRAS.467.4180S}, SECTION E1.  NEED TO MODIFY.
 Weak encounters with background stars will let the SMBHs diffuse through phase space while they are orbiting within the gravitational potential of the galaxy.
@@
 \begin{equation}
-    \dot{M}_{acc} = \frac{4{\pi}G^2M^2\rho}{(C_s^2+v^2)^{3/2}} \text{  M}_\odot \text{ Myr}^{-1},
+    \dot{M}_{acc} = f\frac{4{\pi}G^2M^2\rho}{(C_s^2+v^2)^{3/2}} \text{  M}_\odot \text{ Myr}^{-1},
 \end{equation}
-where M is black hole mass, G is the gravitational constant, and v is the black hole velocity.
+where f is a factor giving the decline in accretion, interior to the BH radius due to convective (i.e., inefficient) accretion, as calculated \citet{2019MNRAS.486.5377I}, cf.
+eq 13.
+Additionally, $M$ is black hole mass, $G$ is the gravitational constant, and $v$ is the black hole velocity.
 
@@
 \begin{equation}
-    L_x = 0.01\dot{M}_{acc}c^2 \text{  erg s}^{-1}.
+    L_x = \epsilon_{rx}\dot{M}_{acc}c^2 \text{  erg s}^{-1},
 \end{equation}
-
+where the x-ray radiative efficiency ${\epsilon}_{rx}=0.01$, and we are assuming for the low-luminosity sources that $L_B{\sim}L_x$.
+For sources having $\dot{M}_B/\dot{M}_{Edd} > 10^{-3}$, we take $L_x=0.1L_{Bol}$.
 The Eddington limit is defined as:

### 2020-01-02 paper.tex
Fixed mysterious error with citations in Introduction

@@
 % Keep the title short and informative.
-\title[MNRAS]{The Fates of Merging Supermassive Black Holes and A Proposal for a New Class of X-Ray Sources}
+\title[MNRAS]{The Fates of Merging Supermassive Black Holes and a Proposal for a New Class of X-Ray Sources}
 
@@
 Jeremiah Ostriker$^{1}$,
-Andreas H.W. K\"upper$^{2}$
+Andreas H.W. K\"upper$^{2,3}$
 \\
@@
 $^{1}$Department of Astronomy, Columbia University, 550 West 120th Street, New York, NY 10027, USA\\
-$^{2}$Hubble Fellow\\
+$^{2}$QuantCo, 955 Massachusetts Avenue, Cambridge, MA 02139, USA
+$^{3}$Hubble Fellow\\
 }
@@
 \begin{abstract}
-We perform N-body simulations on 11 galaxies extracted from a cosmological simulation of hierarchical structure formation with total mass in the range $10^{12} M_{\sun} < M < 10^{13} M_{\sun}$ from 4 $\gid$ z $\gid$ 0.
-After mergers, we track the dynamical evolution of the orbiting black holes (BHs) around their host central BHs.
-Of the 86 orbiting BHs, we find that 36 merge with their host central BHs, 13 are ejected from their respective host galaxies, and 37 are still orbiting at the end of the simulations.
-Across all galaxies, 33 BHs are kicked to a higher orbit after close interactions with the central BHs, after which only one of them merged with their hosts.
+We perform follow-up N-body simulations on some of the most massive galaxies extracted from a cosmological simulation of hierarchical structure formation with total masses in the range $10^{12} M_{\sun} < M < 10^{14} M_{\sun}$ from 4 $\gid$ z $\gid$ 0.
+After galactic mergers, we track the dynamical evolution of the infalling black holes (BHs) around their host's central BHs.
+From 11 different simulations, we find that, of the 86 infalling BHs with masses > XYZ, 36 merge with their host's central BH, 13 are ejected from their host galaxy, and 37 are still orbiting at the end of the simulations.
+Across all galaxies, 33 BHs are kicked to a higher orbit after close interactions with the central BH binary or multiple, after which only one of them merged with their hosts.
 These orbiting BHs should be detectable by their anomalous (not LMXRB) spectra.
 The x-ray luminosities of the orbiting massive BHs at z=0 are in the range $10^{25}-10^{43}$ $erg\ s^{-1}$, with an undetectable median value $10^{32}$ $erg\ s^{-1}$.
-However, the most luminous $\sim$$5\%$ should be detectable.
+However, the most luminous $\sim$$5\%$ should be detectable by existing x-ray facilities.
 \end{abstract}
@@
 \section{Introduction}\label{sec:introduction}
-What happens to the massive black holes centrally located in galaxies when those galaxies merge with others?
-There are three possibilities: they merge, they are ejected, or they remain in orbit in the merged galaxy.
+Simulations of structure formation in a $\Lambda$CDM universe show us how the massive galaxies we see today were formed through a myriad of minor and major mergers between (proto) galaxies.
+As most galaxies are believed to contain central massive black holes even at high redshifts, each of these mergers sets the stage for a potential encounter between supermassive black holes.
+Here we are going to investigate what happened to those black holes over a timeframe of billions of years.
+
+What are possible outcomes for massive black holes during galaxy mergers?
+There are three possibilities: they merge with the central massive black hole of the galaxy, they get ejected, or they remain in orbit in the merged galaxy.
 Combinations of these options are also possible with the spin induced kick at merger leading to an ejection or extended orbit of the merged black hole.
@@
 
-There is no "final parsec problem," and the opposite problem of too many BH mergers is also avoided when it is realized that we are dealing with a small N-body system rather than a series of two-body problems (cf \citet{2018MNRAS.473.3410R}).
+There is no "final parsec problem," and the opposite problem of too many BH mergers is also avoided when it is realized that we are dealing with a small N-body system rather than a series of two-body problems (cf \citealt{2018MNRAS.473.3410R}).
 

### 2020-01-04 paper.tex
More edits throughout paper.  Standardized fonts in plots.

@@
 \newcommand{\bibtex}{\textsc{Bib}\!\TeX} % bibtex. Not quite the correct typesetting, but close enough
+\defcitealias{2011ApJ...741...99C}{Cen+11}
 
@@
 \begin{abstract}
-We perform follow-up N-body simulations on some of the most massive galaxies extracted from a cosmological simulation of hierarchical structure formation with total masses in the range $10^{12} M_{\sun} < M < 10^{14} M_{\sun}$ from 4 $\gid$ z $\gid$ 0.
+We perform follow-up N-body simulations on some of the most massive galaxies extracted from a cosmological simulation of hierarchical structure formation with total masses in the range $10^{12} M_{\sun} < M < 3\times 10^{13} M_{\sun}$ from $4\geq z \geq 0$.
 After galactic mergers, we track the dynamical evolution of the infalling black holes (BHs) around their host's central BHs.
-From 11 different simulations, we find that, of the 86 infalling BHs with masses > XYZ, 36 merge with their host's central BH, 13 are ejected from their host galaxy, and 37 are still orbiting at the end of the simulations.
+From 11 different simulations, we find that, of the 86 infalling BHs with masses > $10^4 M_{\sun}$, 36 merge with their host's central BH, 13 are ejected from their host galaxy, and 37 are still orbiting at $z=0$.
 Across all galaxies, 33 BHs are kicked to a higher orbit after close interactions with the central BH binary or multiple, after which only one of them merged with their hosts.
 These orbiting BHs should be detectable by their anomalous (not LMXRB) spectra.
-The x-ray luminosities of the orbiting massive BHs at z=0 are in the range $10^{25}-10^{43}$ $erg\ s^{-1}$, with an undetectable median value $10^{32}$ $erg\ s^{-1}$.
-However, the most luminous $\sim$$5\%$ should be detectable by existing x-ray facilities.
+The X-ray luminosities of the orbiting massive BHs at z=0 are in the range $10^{27}-10^{43}$ $\mathrm{erg}~\mathrm{s}^{-1}$, with an undetectable median value $10^{32}$ $\mathrm{erg}~\mathrm{s}^{-1}$.
+However, the most luminous $\sim$5\% should be detectable by existing X-ray facilities.
 \end{abstract}
@@
 Simulations of structure formation in a $\Lambda$CDM universe show us how the massive galaxies we see today were formed through a myriad of minor and major mergers between (proto) galaxies.
-As most galaxies are believed to contain central massive black holes even at high redshifts, each of these mergers sets the stage for a potential encounter between supermassive black holes.
-Here we are going to investigate what happened to those black holes over a timeframe of billions of years.
+As most galaxies are believed to contain central massive black holes even at high redshifts, each of these mergers set the stage for a potential encounter between massive black holes.
+Here we investigate what happened to those black holes over a timeframe of billions of years.
 
 What are possible outcomes for massive black holes during galaxy mergers?
-There are three possibilities: they merge with the central massive black hole of the galaxy, they get ejected, or they remain in orbit in the merged galaxy.
-Combinations of these options are also possible with the spin induced kick at merger leading to an ejection or extended orbit of the merged black hole.
-We now know from pulsar timing measurements (\citet{2008MNRAS.390..192S}, \citet{2018ApJ...856...42S}, \citet{2016APS..APRR18003T}) that the gravitational wave background is probably too low for most galaxy mergers (mass-weighted) (but see \cite{2018NatCo...9..573M}) to lead to BH mergers, but the outcome remains uncertain.
-We will argue in this paper that a very common outcome--especially for the lower mass black holes--is for the injected objects to remain as orbiting X-ray sources in normal massive galaxies waiting to be identified by current observational techniques.
+There are three possibilities: they merge or form a binary with the central massive black hole of their new host galaxy, they get ejected through three-body interactions with an existing central black-hole binary, or they remain in orbit in the merged galaxy.
+Combinations of these options are also possible with, e.g., the (spin-induced) kick at merger leading to an ejection or extended orbit of the merged black hole.
+We will argue in this paper that a very common outcome -- especially for lower-mass black holes -- is for the injected BHs to remain as orbiting X-ray sources in their host galaxies, waiting to be identified by current observational techniques.
+(check if X-1 and X-2 in NGC 1313 are candidates for such objects see https://arxiv.org/pdf/astro-ph/0608066.pdf )
 
-There is no "final parsec problem," and the opposite problem of too many BH mergers is also avoided when it is realized that we are dealing with a small N-body system rather than a series of two-body problems (cf \citealt{2018MNRAS.473.3410R}).
+But how common are encounters of massive black holes?
+For galaxies, we know that minor mergers are frequent from the observed evolution of the size and mass of these systems \citep{2010ApJ...718L..73V, 2008ApJ...677L...5V, 2019MNRAS.484..595M}.
+However, if we assume that all galaxy mergers lead to SMBH mergers we end up overpredicting the  gravitational wave background, as constrained by observations from pulsar timing arrays (PTAs, see \citealt{2008MNRAS.390..192S, 2009MNRAS.394.2255S, 2013MNRAS.433L...1S, 2014ApJ...789..156M, 2015ApJ...799..178K, 2016APS..APRR18003T, 2018ApJ...856...42S, 2018MNRAS.479.4017I, 2018ApJ...863L..36I, 2018NatCo...9..573M}).
+In fact, dynamical studies of black hole encounters have shown that most encounters between two supermassive black holes will result in a stalling binary, unable to get close enough for gravitational wave emission to drive the merger (cite some papers from David Meritt here).
 
-How common are mergers of massive black holes?
-For the galaxies themselves we know that minor mergers are frequent from the observed (\citet{2010ApJ...718L..73V}, \citet{2008ApJ...677L...5V}, \citet{2019MNRAS.484..595M}) evolution of the size and mass of these systems, but assuming that all galaxy mergers lead to SMBH mergers overpredicts the observations of gravitational waves from the pulsar timing arrays (PTAs) (\citet{2008MNRAS.390..192S}, \citet{2009MNRAS.394.2255S}, \citet{2013MNRAS.433L...1S}, \citet{2014ApJ...789..156M}, \citet{2015ApJ...799..178K}, \citet{2018ApJ...856...42S}, \citet{2018MNRAS.479.4017I}, \citet{2018ApJ...863L..36I}).
-However, we do not often see multiple SMBHs at the centers of massive ellipticals (but see \citet{2016MNRAS.463.2145C}).
+However, we do not often see SMBH binaries at the centers of massive ellipticals (but see \citealt{2016MNRAS.463.2145C}).
 So, what does happen?
-One paper (\citet{2018MNRAS.473.3410R}) has indicated that dynamical interactions among multiple orbiting black holes, which will eject a non-negligible fraction of the mass, may solve this problem.
-The present paper also addresses this purported dynamical solution, focusing attention on the large fraction of lower mass black holes that remain to be detected as they orbit in massive galaxies.
-What we argue in this paper is that, as a result of the N-body interactions among the infalling black holes, some are ejected, some remain in extended orbits and some (the few most massive ones) do in fact merge, but these do not exceed the PTA limits, and some of the orbiting ones might be detectable via their ability to accrete gas and emit radiation.
+\cite{2018MNRAS.473.3410R} indicate that dynamical interactions among multiple orbiting black holes, which will eject a non-negligible fraction of the mass, may solve this problem.
+The present paper also addresses this purported dynamical solution, focusing attention on the large fraction of lower-mass black holes that remain to be detected as they orbit in massive galaxies.
+We argue that, as a result of few-body interactions among the resident and infalling black holes, some are ejected, some remain in extended orbits, and some (the few most massive ones) do in fact merge.
+The merger rates we find do not exceed the PTA limits, and some of the orbiting BHs that our simulations predict to exist may actually be detectable via their ability to accrete gas and emit radiation.
 
-Here we look at the merger history of 11 exemplary galaxies across the galaxy mass spectrum extracted from a cosmological simulation of hierarchical structure formation.
+For this study, we look at the merger history of 11 exemplary galaxies across the galaxy mass spectrum extracted from a cosmological simulation of hierarchical structure formation.
 We investigate how, after merging with incoming galaxies, SMBHs sink into the cores of the hosts and interact with the resident black hole.
-We show that gravitational interactions of multiple SMBHs are most probable in high-mass galaxies with total mass $10^{12} M_{\sun} < M < 10^{13} M_{\sun}$.
+We show that gravitational interactions of multiple SMBHs are most probable in high-mass galaxies with total mass $10^{12} M_{\sun} < M < 3\times10^{13} M_{\sun}$.
 Galaxies with lower masses have too few mergers with SMBH hosting galaxies.
@@
 
-This paper is organized as follows: in Section \ref{sec:methods} we describe the cosmological simulations from which we use the merger history to set up our idealized numerical simulations.
+This paper is organized as follows: in Section\,\ref{sec:methods} we describe the cosmological simulations from which we use the merger history to set up our idealized numerical simulations.
 We present the few-body integration code, \textsc{AR-Chain} that we used for our simulations of SMBH dynamics, and the modifications we made to this code in order to deal with a host galaxy's gravitational potential.
-In Section \ref{sec:results}, we show the results of our 11 exemplary simulations of galaxies growing with time and acquiring new SMBHs.
+In Section\,\ref{sec:results}, we show the results of our 11 exemplary simulations of galaxies growing with time and acquiring new SMBHs.
 We analyze how the SMBHs spiral into the core of their new host galaxies due to dynamical friction, and how interactions with the host black hole and other orbiting BHs leads to near-ejections or mergers.
 We then estimate the X-ray luminosities expected of the orbiting black holes.
-The final Section \ref{sec:conclusions} contains a discussion of the results and our conclusions.
+The final Section\,\ref{sec:conclusions} contains a discussion of the results and our conclusions.
 
@@
 The galaxies were given a dark matter background potential using the Stone-Ostriker profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form, having a profile similar to that of a truncated isothermal sphere.
-The galaxies were evolved from $4 > z > 0$.
+The galaxies were evolved from $4\geq z \geq 0$.
 Orbiting black holes were periodically introduced into the "host" galaxy following mergers and their dynamical interaction with the background potential and central SMBH were followed, as described further below.
@@
 \subsection{Merger tree Data}
-The merger tree data that was used as the input to our simulations is the result of previous work by \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C} (hereafter Cen(+11) and known as the LAOZI simulations \citet{2014ApJ...781...38C}), as well as  \citet{2012MNRAS.425..641L} (hereafter Lackner(+12)), and \citet{2015ApJ...799..178K} (hereafter Kulier(+15)).
+The merger tree data that was used as the input to our simulations is the result of previous work by \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C}  (known as the LAOZI simulations \citet{2014ApJ...781...38C}), as well as  \citet{2012MNRAS.425..641L}, and \citet{2015ApJ...799..178K}.
 A brief synopsis of the work that led to our input data is described below.
 
-Cen(+11) studied the "cosmic downsizing" effect (e.g., \citet{1996AJ....112..839C}) using high-resolution large-scale hydrodynamic galaxy formation simulations.
-His work produced physical parameters for galaxies such as position, velocity, total mass, stellar mass, gas mass, mean formation time, mean stellar metallicity, mean gas metallicity, SFR, luminosities, etc.
+\citet{2011ApJ...741...99C} studied the "cosmic downsizing" effect (e.g., \citet{1996AJ....112..839C}) using high-resolution large-scale hydrodynamic galaxy formation simulations.
+His work produced physical parameters for galaxies such as position, velocity, total mass, stellar mass, gas mass, mean formation time, mean stellar metallicity, mean gas metallicity, star formation rate, luminosities, etc.
 
-Lackner(+12), using Cen(+11)'s work as a basis, created galactic merger trees that compared the properties of in situ and accreted stellar mass of galaxies at redshift snapshots between $4 > z > 0$.
+\citet{2012MNRAS.425..641L}, using \citet{2011ApJ...741...99C}'s work as a basis, created galactic merger trees that compared the properties of in situ and accreted stellar mass of galaxies at redshift snapshots between $4 > z > 0$.
 
-Kulier(+15) furthered the merger tree data produced by Lackner(+12) by estimating the evolution of the SMBH population, based on assumptions about the relationship between the properties of SMBHs and those of their host galaxies.
+\citet{2015ApJ...799..178K} furthered the merger tree data produced by \citet{2012MNRAS.425..641L} by estimating the evolution of the SMBH population, based on assumptions about the relationship between the properties of SMBHs and those of their host galaxies.
 
@@
 \begin{itemize}
-    \item Galactic properties - Each galaxy was distinguished by an id number, with properties such as stellar mass, dark matter mass, central black hole id number, and orbiting black hole id numbers, recorded at 37 redshift slices between $4 > z > 0$.
+    \item Galactic properties - Each galaxy was distinguished by an id number, with properties such as stellar mass, dark matter (DM) mass, central black hole id number, and orbiting black hole id numbers, recorded at 37 redshift slices between $4 > z > 0$.
     \item Black Hole properties - Each black hole was also distinguished by an id number, with properties such as seed mass, accreted mass, its host galaxy id number, and time after $z=4$ at which the black hole entered its host galaxy, if it was not the central black hole.
@@
 
-The merger tree data from Lackner(+12) and Kulier\-(+15) provided 1,830 galaxies in total.  However, not all the galaxies were suitable for our simulations.  We placed further requirements as follows:
+The merger tree data from \citet{2012MNRAS.425..641L} and \citet{2015ApJ...799..178K} provided 1,830 galaxies in total.
+However, not all the galaxies were suitable for our simulations.
+We placed further requirements as follows:
 \begin{itemize}
-\item The galaxies had to exist through the entire simulation ($4 > z > 0$).  If they merged with other galaxies, they had to have been the "surviving" galaxy at each merger.
+\item The galaxies had to exist through the entire simulation ($4\geq z \geq 0$).  If they merged with other galaxies, they had to have been the "surviving" galaxy at each merger.
 \item They had to have accumulated orbiting black holes by $z = 0$.
@@
 The above criteria narrowed the field of eligible galaxies down to 51.
-In considering time and resources, we chose the top 13 galaxies in terms of number of black holes to run the simulations.
+In considering time and resources, we chose the 13 galaxies that had the largest number black holes to run the simulations.
 The black holes in these galaxies accounted for nearly $84{\%}$ of all orbiting black holes across all the galaxies, so it represented a reasonable balance between completeness and efficiency.
 
-The following cosmological parameters were used in our simulations, consistent with both Lackner(+12) and Kulier(+15):   $\Omega_M = 0.28$, $\Omega_b = 0.046$, $\Omega_\Lambda = 0.72$, $\sigma_8 = 0.82$, $H_0 = 100h^{-1}Mpc^{-1} = 70 km s^{-1} Mpc^{-1}$, and $n = 0.96$.
+The following cosmological parameters were used in our simulations, consistent with both \citet{2012MNRAS.425..641L} and \citet{2015ApJ...799..178K}:   $\Omega_M = 0.28$, $\Omega_b = 0.046$, $\Omega_\Lambda = 0.72$, $\sigma_8 = 0.82$, $H_0 = 100h^{-1}\mathrm{Mpc}^{-1} = 70 \mathrm{km}\;\mathrm{s}^{-1} \mathrm{Mpc}^{-1}$, and $n = 0.96$.
 
 \subsubsection{Stellar Mass Adjustment}
-As we will explain further in Section \ref{Galaxy background potential}, in our simulations orbiting black holes are inserted into the host galaxy at the effective radius, $R_e$, which is partially dependent on stellar mass, $M_*$ (see equation \ref{re}).
-For every doubling of the stellar mass, $M_*$, $R_e$ increases by a factor of 1.66.
-Additionally, the velocity dispersion at the effective radius, $\sigma(R_e)$, which is used to set the parameter $r_h$ of our dark matter profile, is also dependent on $M_*$.
+As we will explain further in Section \ref{Galaxy background potential}, in our simulations orbiting black holes are inserted into the host galaxy at the effective radius, $R_e$, which is partially dependent on stellar mass, $M_*$ (see Eqn.
+\ref{re}).
+For every doubling of the stellar mass, $R_e$ increases by a factor of 1.66.
+Additionally, the velocity dispersion at the effective radius, $\sigma(R_e)$, which is used to set the parameter $r_h$ (see Eqn.
+\ref{jerry}) of our dark matter profile, is also dependent on $M_*$.
 In this case, a doubling of $M_*$ would increase $\sigma(R_e)$ by a factor of 1.15.
@@
 
-Lackner(+12), which is the source of our stellar masses, noted that the efficiency of star formation in their simulations, defined as $f_*=M_*/M_{DM}(\Omega_{DM}/\Omega_b)$, was approximately 0.6.
-Compared with the expected range of $0.10 \loa f_* \loa 0.15$ that they referenced from \citet{2012ApJ...746...95L}, their stellar masses were a factor of roughly 4 times greater.
+\citet{2012MNRAS.425..641L}, which is the source of our stellar masses, noted that the efficiency of star formation in their simulations, defined as $f_\mathrm{bary}=M_*/M_{\mathrm{DM}}(\Omega_\mathrm{DM}/\Omega_\mathrm{b})$ (where $M_\mathrm{DM}$ is the mass of the dark matter halo), was approximately 0.6.
+Compared with the expected range of $0.10 \loa f_\mathrm{bary} \loa 0.15$ that they referenced from \citet{2012ApJ...746...95L}, their stellar masses were a factor of roughly 4 times greater.
 
-We also compared the stellar masses from Lackner\-(+12) to  observational and abundance matching data from \citet{2018AstL...44....8K}.
+We also compared the stellar masses from \citet{2012MNRAS.425..641L} to  observational and abundance matching data from \citet{2018AstL...44....8K}.
 Figure \ref{fig:stellar1} is a partial, approximate, replication of their Figure 11 (abundance matching line).
@@
 \includegraphics[width=0.5\textwidth]{plots/stellar_to_halo_ratio.png}
-\caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.  Purple dots shown are examples of our rescaled stellar masses}
+\caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.
+$f_\mathrm{bary}$ is the universal baryon fraction as a function of total halo mass.
+Purple dots shown are examples of our rescaled stellar masses}
 \label{fig:stellar1}
@@
 \begin{center}
-\caption{Galaxy characteristics at z=0. Units are M$\sun$.}
+\caption{Galaxy characteristics at z=0. $M_\mathrm{DM}$ is dark matter mass.  $M_\mathrm{CBH}$ is central black hole mass.  Units are $M_{\odot}$.}
 \begin{tabular} {|c | c | c| c|}
 \hline
-$M_{DM}$ & $M_{CBH}$ & $M_{*} (orig.)$ & $M_{*} (rescaled)$ \\
+$M_\mathrm{DM}$ & $M_\mathrm{CBH}$ & $M_{*} \mathrm{(orig.)}$ & $M_{*} \mathrm{(rescaled)}$ \\
 \hline
@@
 \begin{equation} \label{re}
-R_{e} = 2.5 kpc\left(\frac{M_*}{10^{11}M_{\odot}}\right)^{0.73}(1+z)^{-0.98},
+R_{e} = 2.5 \mathrm{kpc}\left(\frac{M_*}{10^{11}M_{\odot}}\right)^{0.73}(1+z)^{-0.98},
 \end{equation}
 \begin{equation} \label{sig}
-\sigma(R_{e}) = 190km/s\left(\frac{M_{*}}{10^{11}M_{\odot}}\right)^{0.2}(1+z)^{0.47},
+\sigma(R_{e}) = 190\mathrm{km}\;\mathrm{s}^{-1}\left(\frac{M_{*}}{10^{11}M_{\odot}}\right)^{0.2}(1+z)^{0.47},
 \end{equation}
 
-We can then equate the value for $\sigma({R_e})$ obtained from Equation \ref{sig} to the analytic expressions for $\sigma(R_{e})$ in the Stone-Ostriker profile (Eqns 9 and A1-A4).
+We can then equate the value for $\sigma({R_e})$ obtained from Equation \ref{sig} to the analytic expressions for $\sigma$ in the Stone-Ostriker profile (cf.
+Eqns 9 and A1-A4).
 The only unknown is $r_h$, which we can solve for using a simple recursive Newton method.
@@
 \begin{equation} \label{rhoc}
-M_{tot} = \frac{2\pi^2r_{c}^2r_{h}^2\rho_c}{r_h+r_c},
+M_\mathrm{DM} = \frac{2\pi^2r_{c}^2r_{h}^2\rho_c}{r_h+r_c}.
 \end{equation}
-where $M_{tot}$ is the total dark matter mass.
 
@@
 The SMBHs can therefore merge via gravitational wave emission.
-We include gravitational wave recoils following the prescription outlined in Kulier(+15), which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.
+We include gravitational wave recoils following the prescription outlined in \citet{2015ApJ...799..178K}, which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.
 We assume that a merger will be inevitable when the separation between two SMBHs becomes smaller than 1.0x the Schwarzschild radius.
@@
 \begin{equation}\label{tfric}
-    t_{fric} = \frac{19}{6}\left(\frac{R_e}{5kpc}\right)^2\frac{\sigma_{eff}}{200km\,s^{-1}}\frac{10^8\,M_{\odot}}{M_{bh}} \text{  Gyr}.
+    t_{fric} = \frac{19}{6}\left(\frac{R_\mathrm{e}}{5\mathrm{kpc}}\right)^2\frac{\sigma(R_\mathrm{e})}{200\mathrm{km}\,\mathrm{s}^{-1}}\frac{10^8\,M_{\odot}}{M_\mathrm{BH}} \text{  Gyr},
 \end{equation}
@@
 
-In figure \ref{fig:time_to_merge} we present the time it took for the merging guest black holes to merge with their host.
+In figure \ref{fig:time_to_merge} we present the time it took for the guest black holes to merge with their host.
 As can be seen in the plot, although there is a fair amount of variation, the general trend is a decreasing time to merge as orbiting black hole mass increases.
@@
 \subsubsection{Kicked, Ejected and Orbiting Black Holes}\label{sec:kicked_orbiting}
-Of the 37 orbiting black holes at $z=0$, 18 of them were kicked to higher orbits at some point in their traversal of their host galaxy.
+Of the 37 orbiting black holes at $z=0$, 18 of them were kicked to higher orbits during traversal of their host galaxy.
 If one counts the 13 ejected black holes, then of the 50 SMBHs that had not eventually merged with their host, 32 of them were kicked out of the galactic core as a result of three-body interactions.
@@
 \includegraphics[width=0.5\textwidth]{plots/"Summary Results All Galaxies".png}
-\caption{Histogram of merged, ejected, and orbiting SMBHs at z=0 as a function of BH mass.  Colored arrows along x-axis represent median masses of respective sets.}
+\caption{Histogram of merged, ejected, and orbiting SMBHs at z=0 as a function of BH mass.  Colored arrows along upper x-axis represent median masses of respective sets.}
 \label{fig:meosmbh}
@@
 \includegraphics[width=0.5\textwidth]{plots/kicked_stats.png}
-\caption{Histogram of kicked and not-kicked SMBHs at z=0.  Colored arrows along x-axis represent median masses of respective sets.}
+\caption{Histogram of kicked and not-kicked SMBHs at z=0.  Colored arrows along upper x-axis represent median masses of respective sets.}
 \label{fig:kicked_stats}
@@
 \subsection{Black Hole Luminosity}
-The x-ray temperature versus sigma relation from Table 2 of  \citet{2018ApJ...857...32B} was fitted according to:
+The x-ray temperature versus central velocity dispersion relation from Table 2 of  \citet{2018ApJ...857...32B} was fitted according to:
 \begin{equation}
-    T_x = 10^{2.50*log(\sigma) - 6.06} \text{  kev}.
+    T_x = 10^{2.50*log(\sigma_c) - 6.06} \text{  keV}.
 \end{equation}
@@
 \begin{equation}
-    \rho_0 = 10^{0.6*log(\sigma) - 25} \text{  g cm}^{-3}.
+    \rho_0 = 10^{0.6*log(\sigma_c) - 25} \text{  g cm}^{-3}.
 \end{equation}
@@
 \begin{equation}
-    \dot{M}_{acc} = f\frac{4{\pi}G^2M^2\rho}{(C_s^2+v^2)^{3/2}} \text{  M}_\odot \text{ Myr}^{-1},
+    \dot{M}_{acc} = f\frac{4{\pi}G^2M_\mathrm{BH}^2\rho}{(C_s^2+v^2)^{3/2}} \text{  M}_\odot \text{ Myr}^{-1},
 \end{equation}
@@
 \section{Conclusions}\label{sec:conclusions}
-We performed N-body simulations on 11 galaxies ranging in mass between $10^{12}$ M$_{\sun}$ < M < $10^{13}$ M$_{\sun}$, from 4 $\gid$ z $\gid$ 0.
-A total of 86 orbiting black holes were followed in our simulations, resulting in 42$\%$ mergers with their host galaxy, while another 43$\%$ remained in orbit at $z=0$.
+We performed N-body simulations on 11 galaxies ranging in mass between $10^{12}$ M$_{\sun}$ < M < 3$\times$ $10^{13}$ M$_{\sun}$, from 4 $\gid$ z $\gid$ 0.
+A total of 86 orbiting black holes were followed in our simulations, resulting in 42$\%$ mergers with their host galaxy's resident black hole, while another 43$\%$ remained in orbit at $z=0$.
 Those remaining orbiting black holes had x-ray luminosities in the range of $10^{25}-10^{43}$ $erg\ s^{-1}$.

### 2020-01-12 paper.tex
Last commit before changing accretion rate methodology.

@@
 
-\subsection{Simulation setup}
+\subsection{Simulation setup}\label{subsec:simset}
 For each galaxy in the simulations, we only used black holes that would theoretically have merged with the center of the host galaxy within a dynamical friction time, $t_{fric}$, of less than 100 times a Hubble time, with $t_{fric}$ defined from \citet{2008gady.book.....B} as:
@@
 
-\subsection{Black Hole Luminosity}
+\subsection{Black Hole Xray Luminosity}
+\subsubsection{Calculations}
+As a black hole traverses through a host galaxy or other gaseous environment, it accretes
+
 The x-ray temperature versus central velocity dispersion relation from Table 2 of  \citet{2018ApJ...857...32B} was fitted according to:
@@
 \end{equation}
-where the x-ray radiative efficiency ${\epsilon}_{rx}=0.01$, and we are assuming for the low-luminosity sources that $L_B{\sim}L_x$.
+where the x-ray radiative efficiency ${\epsilon}_{rx}=0.01$, and we are assuming for the low-luminosity sources that $L_x{\sim}L_{Bol}$.
 For sources having $\dot{M}_B/\dot{M}_{Edd} > 10^{-3}$, we take $L_x=0.1L_{Bol}$.

### 2020-01-17 paper.tex
Significant rewrite of xray luminosity section.  Finished edits suggested by contributors.  All plots redone with seaborn style.

@@
 %\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
+\newcommand{\expnumber}[2]{{#1}\mathrm{e}{#2}}
 \newcommand{\kms}{\,km\,s$^{-1}$} % kilometres per second
@@
 Galaxies with higher masses are more extended, making dynamical friction processes less efficient and hence failing to drive SMBHs into the host galaxy core.
+\citep{2012MNRAS.422.1306K} and \citep{2018MNRAS.473.3410R} performed similar N-body simulations of merging galaxies and black holes, although their haloes were from dark matter-only merger trees from the Millennium Simulation \citet{2005Natur.435..629S}, which have very different merger histories compared to the hydrodynamical simulations in this study.
+Additionally, most of the halo masses in the \citep{2012MNRAS.422.1306K} simulations were of mass $M_{halo} > 10^{14} M_{\odot}$.
 
@@
 \includegraphics[width=0.5\textwidth]{plots/"Summary Results All Galaxies".png}
-\caption{Histogram of merged, ejected, and orbiting SMBHs at z=0 as a function of BH mass.  Colored arrows along upper x-axis represent median masses of respective sets.}
+\caption{Histogram of merged, ejected, and orbiting SMBHs at z=0 as a function of BH mass.
+Ejected black holes span almost the entire mass range, while lower-mass black holes are orbiting and higher mass black holes tended to merge.
+Colored arrows along upper x-axis represent median masses of respective sets.
+Histogram bars are not stacked.}
 \label{fig:meosmbh}
@@
 \includegraphics[width=0.5\textwidth]{plots/kicked_stats.png}
-\caption{Histogram of kicked and not-kicked SMBHs at z=0.  Colored arrows along upper x-axis represent median masses of respective sets.}
+\caption{Histogram of kicked and not-kicked SMBHs at z=0.  Colored arrows along upper x-axis represent median masses of respective sets.  Histograms are not stacked.}
 \label{fig:kicked_stats}
@@
 \subsection{Black Hole Xray Luminosity}
-\subsubsection{Calculations}
-As a black hole traverses through a host galaxy or other gaseous environment, it accretes
+\subsubsection{Assumptions and Method Employed}
+Since we model the black holes in this work as point particles for purposes of the simulations, we don't assume any particular structure to them.
+Therefore, we adopt the approach and assumptions from \citealt{2018MNRAS.476.1412I} and \citealt{2019MNRAS.486.5377I} in estimating the x-ray luminosities of the remaining black holes left wandering in our subject galaxies.
+Their approach assumes rotating accretion flows in a very low-density environment.
+Shear viscous forces transport angular momentum outwards, resulting in an accretion disc that forms at the bottom of the distribution.
+However, due to the low density of the gas, it does not cool, and convection limits the net accretion, and subsequent radiation luminosity, of the black hole.
 
-The x-ray temperature versus central velocity dispersion relation from Table 2 of  \citet{2018ApJ...857...32B} was fitted according to:
+\subsubsection{Gas Environment Surrounding Black Holes}
+In order to model the surrounding environment of the wandering black holes, we used the data and scaling relations from \citet{2018ApJ...857...32B}, which is based on Chandra X-ray Observatory observations of 94 early-type, gas poor galaxies of several morphological types (elliptical, lenticular, SB, BCGs, and cD galaxies).
+In particular, we used data from Tables 2 and 3 for temperature in xray ($T_X$) and central gas density ($\rho_0$)) to model the surrounding gas properties.
+Central velocity dispersion ($\sigma_c$) was used as the independent variable, as many galactic properties co-evolve with velocity dispersion (REFERENCES TO BACK THIS UP???).
+We estimate the central velocity dispersion in this work based on the potential-density profile in  \citet{2015ApJ...806L..28S} that was also used in modeling the potential in the simulations (cf their equation 11):
 \begin{equation}
-    T_x = 10^{2.50*log(\sigma_c) - 6.06} \text{  keV}.
+    \sigma^2 = \frac{6GM_{tot}(\frac{\pi^2}{8}-1)}{{\pi}r_h},
 \end{equation}
-Central gas density, ${\rho}_0$ was also fitted from Table 3 of \citet{2018ApJ...857...32B} according to:
-\begin{equation}
-    \rho_0 = 10^{0.6*log(\sigma_c) - 25} \text{  g cm}^{-3}.
+where G is the gravitational constant, $M_{tot}$ is the total galaxy mass (stars + DM), and $r_h$ is the outer halo radius as defined in the Stone-Ostriker profile (cf. equation 1).
+
+Figures \ref{fig:rho0_vs_sigma} and \ref{fig:Tx_vs_sigma} present the data from \citet{2018ApJ...857...32B}, along with the simple linear fits (in log-log space) and resulting gas properties used for our galaxies (red x's):
+\begin{subequations} \label{eq:gas_properties}
+\begin{eqnarray}
+    \rho_0 = 10^{0.6*log\left(\frac{\sigma_c}{g\ cm^{-3}}\right) - 25} \text{  g cm}^{-3},\\
+    T_x = 10^{2.50*log\left(\frac{\sigma_c}{g\ cm^{-3}}\right) - 6.06} \text{  keV}.
+\end{eqnarray}
+\end{subequations}
+
+The dispersion of the data around the fit for $\rho_0$ is at most 1.5-2.0 orders of magnitude.
+This leads to a similar variation in the gas density surrounding the black hole, in addition to the ultimate accretion rate of the black hole, due to both having a linear dependence on the central gas density (see Eqns \eqref{beta_model} and \eqref{net_accretion} below).
+
+The dispersion of the xray temperature data around the fit is approximately 1-1.5 orders of magnitude.
+The gas sound speed (see Equation \eqref{gas_sound_speed} below) has a $C_s{\sim}T_x^{0.5}$ dependence on temperature.
+However, given the dependence of the accretion rate (see Equation \eqref{net_accretion} below) on gas sound speed of $\dot{M}_{acc}{\sim}C_s^3$, the accretion rate is dependent on temperature to the order of $T_x^{3/2}$.
+This is another source of variation in our estimate of accretion rate.
+
+\begin{figure}
+\vspace{20pt}%
+\begin{center}
+\includegraphics[width=0.5\textwidth]{plots/"rho_0 vs sigma with errors".png}
+\caption{Central gas density versus central velocity dispersion.
+Purple X's represent central gas densities of the galaxies in this study.
+Fit in log space is $\rho_0 = 10^{0.6*log\left(\frac{\sigma_c}{g\ cm^{-3}}\right) - 25} \text{  g cm}^{-3}$.}
+\label{fig:rho0_vs_sigma}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\vspace{20pt}%
+\begin{center}
+\includegraphics[width=0.5\textwidth]{plots/"Tx vs sigma with errors".png}
+\caption{X-ray temperature versus central velocity dispersion.
+Purple X's represent temperatures of the galaxies in this study.
+Fit in log space is $T_x = 10^{2.50*log\left(\frac{\sigma_c}{g\ cm^{-3}}\right) - 6.06} \text{  keV}$.}
+\label{fig:Tx_vs_sigma}
+\end{center}
+\end{figure}
+
+The local gas density ${\rho}$ surrounding the black hole is obtained from a simple isothermal beta model (\citet{1962AJ.....67..471K}, \citet{1976A&A....49..137C}, \citet{1978A&A....70..677C}):
+\begin{equation} \label{beta_model}
+    \rho = \frac{\rho_0}{(1+r^2/r_c^2)^{1.5}} \text{  g cm}^{-3},
 \end{equation}
-The core radius of the gas model, ${r_c}$ is:
-\begin{equation}
-    r_c = 10^{2.1*log(\sigma) - 5.3} \text{  kpc}.
+where $\rho_0$ is as defined above, r is the black hole's distance from the center of the galaxy, and $r_c$ is the core radius.
+
+The sound speed of the gas, $C_s$, is derived from the ideal gas law:
+\begin{equation}\label{gas_sound_speed}
+    C_s = \sqrt{1.67T_x*\expnumber{1.602}{-16}/m_p} \text{  km s}^{-1},
 \end{equation}
-Local gas density ${\rho}$ is obtained from the isothermal beta model (\citet{1962AJ.....67..471K}, \citet{1976A&A....49..137C}, \citet{1978A&A....70..677C}):
-\begin{equation} \label{beta_model}
-    \rho = \frac{\rho_0}{(1+r^2/r_c^2)^{1.5}} \text{  g cm}^{-3}.
-\end{equation}
+where $m_p$ is the proton mass in kilograms.  Since $T_x$ is in keV, the factor of $\expnumber{1.602}{-16}$ is added to convert the temperature to Joules.
 
-Gas sound speed, $c_s$, was obtained from:
-\begin{equation}
-    C_s = \sqrt{1.67T_x/m_p} \text{  km s}^{-1},
-\end{equation}
-where $m_p$ is the proton mass.
-
-The net black hole mass accretion rate is approximated by \citet{2018MNRAS.476.1412I} and \citet{2019MNRAS.486.5377I}:
-\begin{equation}
+The resulting net black hole mass accretion rate is approximated by \citet{2018MNRAS.476.1412I} and \citet{2019MNRAS.486.5377I}:
+\begin{equation}\label{net_accretion}
     \dot{M}_{acc} = f\frac{4{\pi}G^2M_\mathrm{BH}^2\rho}{(C_s^2+v^2)^{3/2}} \text{  M}_\odot \text{ Myr}^{-1},
@@
 eq 13.
-Additionally, $M$ is black hole mass, $G$ is the gravitational constant, and $v$ is the black hole velocity.
+Additionally, $M_{BH}$ is black hole mass, $G$ is the gravitational constant, and $v$ is the black hole velocity.
 
@@
 where the x-ray radiative efficiency ${\epsilon}_{rx}=0.01$, and we are assuming for the low-luminosity sources that $L_x{\sim}L_{Bol}$.
-For sources having $\dot{M}_B/\dot{M}_{Edd} > 10^{-3}$, we take $L_x=0.1L_{Bol}$.
+For sources having $\dot{M}_B/\dot{M}_{Edd} > 10^{-3}$, we take $L_x=0.1L_{Bol}$, due to the higher net accretion onto the black hole as a result of cooling of the accretion disc and hence higher gas density.
 The Eddington limit is defined as:
@@
 
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=0.45\%textwidth]{plots/"Final %Luminosities of Orbiting %BHs".png}
-%\caption{Luminosities of %Orbiting BHs at z=0}
-%\label{fig:loobhs}
-%\end{center}
-%\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.5\textwidth]{plots/"luminosities_final".png}
-\caption{Luminosity of orbiting BHs at z=0 as per Inayoshi (2019).}
-\label{fig:loobhs}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.5\textwidth]{plots/"Final Luminosities using Kohei factor".png}
-\caption{Xray Luminosity Distribution of Orbiting BHs at z=0.  Green region under curve represents approximate range of detectable orbiting black holes.}
-\label{fig:ldobhs}
-\end{center}
-\end{figure}
-
-\subsection{Central Black Hole Influence}
+\subsubsection{Central Black Hole Influence}
 Within the influence radius of the central black hole, which is defined as the radius at which the total mass of the galaxy within that radius (stars + dark matter) equals the mass of the central black hole, the gas density is much higher than otherwise, and equation \eqref{beta_model} cannot be used in the region where the BH Kepler potential dominates.
@@
 
-Figure \ref{fig:wui} shows the difference in luminosity when taking into account the influence of the central black hole for the wandering black holes that were within the influence radius.
+Figure \ref{fig:wui} shows the difference in luminosity when taking into account the influence of the central black hole for the 17 wandering black holes that were within the influence radius.
 In all cases, the final luminosity is higher than the original luminosity.
@@
 \caption{Difference in x-ray luminosity of wandering black holes within the influence radius of the central black hole.
-Red dots are the originally calculated luminosity, not taking the CBH influence into account.
-Green dots are the final luminosities, taking the central BH influence into account.}
+For each vertical line, red (lower) dots are the originally calculated luminosity, not taking the CBH influence into account.
+Green (upper) dots are the final luminosities, taking the central BH influence into account.}
 \label{fig:wui}
@@
 \end{figure}
+
+\subsubsection{Final X-ray Luminosities of Wandering Black Holes, and Expected Detection Spectra}
+Figure \ref{fig:loobhs} is an approximation of Figure 12 from \cite{2019MNRAS.486.5377I}, along with the final $L_{Bol}/L_{Edd}$ ratio of the wandering black holes from this study, although extended below $10^{-6}$ $\dot{M}_{B}/\dot{M}_{Edd}$ for the very low accretion-rate sources.
+Indeed, such low luminosity sources are common, with some estimates of $L_{Bol}/L_{Edd}$ as low as $10^{-10}$ ( e.g., \citealt{2003ApJ...598..301Y}, \citealt{2004ApJ...613..322Q}, \citealt{2008ARA&A..46..475H}, \citealt{2009ApJ...699..626H}, \citealt{2018MNRAS.476.1412I}).
+ANY REFERENCES TO SUPPORT HIGHER MdotB/MdotEdd and LBOL/LEDD???
+NOT SURE WHAT ELSE TO ADD HERE REGARDING POTENTIAL FOR DETECTION.
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.5\textwidth]{plots/"luminosities_final".png}
+\caption{Approximation of Figure 12 from \citealt{2019MNRAS.486.5377I}. Black "X"s represent black holes in this study.}
+\label{fig:loobhs}
+\end{center}
+\end{figure}
+
+Figure \ref{fig:ldobhs} represents a histogram of the final x-ray luminosities of the black holes, overlaid by a lognormal distribution.  
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.5\textwidth]{plots/"Final Luminosities using Kohei factor".png}
+\caption{Xray Luminosity Distribution of Orbiting BHs at z=0.  Green region under curve represents approximate range of detectable orbiting black holes.}
+\label{fig:ldobhs}
+\end{center}
+\end{figure}
+
+The orbiting black holes should be detectable via their anomalous soft x-ray spectra.
+Sgr A*, the black hole at the center of the Milky Way Galaxy, has been observed to fit a power law spectrum with photon index $\Gamma\sim2.7^{+1.3}_{-1.9}$ \citet{2003ApJ...591..891B}.
+Conversely low-mass x-ray binaries (LMXRB) have been fit to a power law spectrum with $\Gamma\sim1.5-2.0$ (\citet{2018Natur.556...70H}.
 
@@
 The authors would like to thank Andrea Kulier and Claire Lackner for providing merger tree data.
+We also thank Renyue Cen, Pieter van Dokkum, Charles Hailey, Zoltan Haiman, Kohei Inayoshi, Sean McWilliams, and Taeho Ryu for useful discussions and insights.
 AHWK acknowledges support by NASA through Hubble Fellowship grant HST-HF-51323.01-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS 5-26555.

### 2020-01-27 paper.tex
More edits between Andreas and Charles

@@
 $^{1}$Department of Astronomy, Columbia University, 550 West 120th Street, New York, NY 10027, USA\\
-$^{2}$QuantCo, 955 Massachusetts Avenue, Cambridge, MA 02139, USA
+$^{2}$QuantCo, Inc., 955 Massachusetts Avenue, Cambridge, MA 02139, USA\\
 $^{3}$Hubble Fellow\\
@@
 % These dates will be filled out by the publisher
-\date{Last updated 2019 Nov 09; in original form 2019 November 9}
+\date{Last updated 2020 Jan 16; in original form 2020 Jan 16}
 
@@
 These orbiting BHs should be detectable by their anomalous (not LMXRB) spectra.
-The X-ray luminosities of the orbiting massive BHs at z=0 are in the range $10^{27}-10^{43}$ $\mathrm{erg}~\mathrm{s}^{-1}$, with an undetectable median value $10^{32}$ $\mathrm{erg}~\mathrm{s}^{-1}$.
+The X-ray luminosities of the orbiting massive BHs at z=0 are in the range $10^{27}-10^{43}$ $\mathrm{erg}~\mathrm{s}^{-1}$, with a currently undetectable median value of $10^{33}$ $\mathrm{erg}~\mathrm{s}^{-1}$.
 However, the most luminous $\sim$5\% should be detectable by existing X-ray facilities.
@@
 We will argue in this paper that a very common outcome -- especially for lower-mass black holes -- is for the injected BHs to remain as orbiting X-ray sources in their host galaxies, waiting to be identified by current observational techniques.
-(check if X-1 and X-2 in NGC 1313 are candidates for such objects see https://arxiv.org/pdf/astro-ph/0608066.pdf )
+
+%(check if X-1 and X-2 in NGC 1313 are candidates for such objects see https://arxiv.org/pdf/astro-ph/0608066.pdf )
 
@@
 However, if we assume that all galaxy mergers lead to SMBH mergers we end up overpredicting the  gravitational wave background, as constrained by observations from pulsar timing arrays (PTAs, see \citealt{2008MNRAS.390..192S, 2009MNRAS.394.2255S, 2013MNRAS.433L...1S, 2014ApJ...789..156M, 2015ApJ...799..178K, 2016APS..APRR18003T, 2018ApJ...856...42S, 2018MNRAS.479.4017I, 2018ApJ...863L..36I, 2018NatCo...9..573M}).
-In fact, dynamical studies of black hole encounters have shown that most encounters between two supermassive black holes will result in a stalling binary, unable to get close enough for gravitational wave emission to drive the merger (cite some papers from David Meritt here).
+In fact, dynamical studies of black hole encounters have shown that most encounters between two supermassive black holes will result in a stalling binary, unable to get close enough for gravitational wave emission to drive the merger \citep{1980Natur.287..307B, 2003AIPC..686..201M}.
 
@@
 Galaxies with higher masses are more extended, making dynamical friction processes less efficient and hence failing to drive SMBHs into the host galaxy core.
-\citep{2012MNRAS.422.1306K} and \citep{2018MNRAS.473.3410R} performed similar N-body simulations of merging galaxies and black holes, although their haloes were from dark matter-only merger trees from the Millennium Simulation \citet{2005Natur.435..629S}, which have very different merger histories compared to the hydrodynamical simulations in this study.
-Additionally, most of the halo masses in the \citep{2012MNRAS.422.1306K} simulations were of mass $M_{halo} > 10^{14} M_{\odot}$.
+\cite{2012MNRAS.422.1306K} and \cite{2018MNRAS.473.3410R} performed similar N-body simulations of merging galaxies and black holes, although their haloes were from dark matter-only merger trees from the Millennium Simulation \citep{2005Natur.435..629S}, which have very different merger histories compared to the hydrodynamical simulations in this study.
+Additionally, most of the halo masses in the \cite{2012MNRAS.422.1306K} simulations were of mass $M_{halo} > 10^{14} M_{\odot}$.
 
@@
 \subsection{Overview of simulation}
+The computational challenge of this investigation is a wide range of time-scales.
+Galactic evolution and galactic orbits take hundreds of millions to billions of years, while orbital times of BH binaries may require times steps of years for accurate integration.
+We overcome this challenge by simplifying the model where possible, and by focussing on the main drivers of BH dynamics: the galactic background potential, dynamical friction, and strong BH-BH encounters.
+
 Our simulations focus on elliptical galaxies with central SMBHs.
-The galaxies were given a dark matter background potential using the Stone-Ostriker profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form, having a profile similar to that of a truncated isothermal sphere.
+The galaxies were given a dark matter background potential using the Stone-Ostriker profile \citep{2015ApJ...806L..28S}, which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form, having a profile similar to that of a truncated isothermal sphere.
 The galaxies were evolved from $4\geq z \geq 0$.
@@
 \subsection{Merger tree Data}
-The merger tree data that was used as the input to our simulations is the result of previous work by \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C}  (known as the LAOZI simulations \citet{2014ApJ...781...38C}), as well as  \citet{2012MNRAS.425..641L}, and \citet{2015ApJ...799..178K}.
+The merger tree data we used as the input to our simulations is the result of previous work by \citet{2011ApJ...741...99C, 2011ApJ...742L..33C, 2012ApJ...753...17C, 2012ApJ...748..121C, 2013ApJ...770..139C}  (known as the LAOZI simulations \citealt{2014ApJ...781...38C}), as well as  \citet{2012MNRAS.425..641L}, and \citet{2015ApJ...799..178K}.
 A brief synopsis of the work that led to our input data is described below.
 
-\citet{2011ApJ...741...99C} studied the "cosmic downsizing" effect (e.g., \citet{1996AJ....112..839C}) using high-resolution large-scale hydrodynamic galaxy formation simulations.
+\citet{2011ApJ...741...99C} studied the "cosmic downsizing" effect (e.g., \citealt{1996AJ....112..839C}) using high-resolution large-scale hydrodynamic galaxy formation simulations.
 His work produced physical parameters for galaxies such as position, velocity, total mass, stellar mass, gas mass, mean formation time, mean stellar metallicity, mean gas metallicity, star formation rate, luminosities, etc.
 
-\citet{2012MNRAS.425..641L}, using \citet{2011ApJ...741...99C}'s work as a basis, created galactic merger trees that compared the properties of in situ and accreted stellar mass of galaxies at redshift snapshots between $4 > z > 0$.
+\citet{2012MNRAS.425..641L}, using \citet{2011ApJ...741...99C}'s work as a basis, created galactic merger trees that compared the properties of in-situ and accreted stellar mass of galaxies at redshift snapshots between $4 \geq z \geq 0$.
 
@@
 The above criteria narrowed the field of eligible galaxies down to 51.
-In considering time and resources, we chose the 13 galaxies that had the largest number black holes to run the simulations.
+In considering time and resources, we chose the 11 galaxies that had the largest number black holes to run the simulations.
 The black holes in these galaxies accounted for nearly $84{\%}$ of all orbiting black holes across all the galaxies, so it represented a reasonable balance between completeness and efficiency.
@@
 
-In cosmological simulations it is common to overproduce stellar mass, with a general over-efficiency in the range of 2-4 times those measured in observations (\citet{1996ApJS..105...19K}, \citet{2010MNRAS.404.1111G}, \citet{2010ApJ...725.2312O}).
-One typical reason cited for this overproduction is a lack or underestimation of supernova feedback effects in the form of thermal and/or kinetic energy.
-However, even when thermal energy from supernova feedback is considered, the effects may be reduced due to the energy being quickly radiated away by rapidly cooling surrounding gas (\citet{1996ApJS..105...19K}).
-A second common reason for overproduction of stars in cosmological simulations is a lack of modeling for AGN feedback, which may be responsible for solving the phenomenon called the "cooling flow paradox" (\citet{2001MNRAS.321L..20F}) that suppresses star formation.
+In cosmological simulations, it is common to overproduce stellar mass, with a general over-efficiency in the range of 2-4 times those measured in observations \citep{1996ApJS..105...19K, 2010MNRAS.404.1111G, 2010ApJ...725.2312O}.
+One cited reason for this overproduction is a lack or underestimation of supernova feedback effects in the form of thermal and/or kinetic energy.
+However, even when thermal energy from supernova feedback is considered, the effects may be reduced due to the energy being quickly radiated away by rapidly cooling surrounding gas \citep{1996ApJS..105...19K}.
+A second common reason for overproduction of stars in cosmological simulations is a lack of modeling for AGN feedback, which may be responsible for solving the phenomenon called the "cooling flow paradox" \citep{2001MNRAS.321L..20F} that suppresses star formation.
 
@@
 \subsubsection{Galaxy background potential} \label{Galaxy background potential}
-In order to model the dark matter halo distribution in our simulations, we used the Stone-Ostriker profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair.
-Quantities such as density, potential, and binding energy can be written in closed form.
+To model the dark matter halo distribution in our simulations, we used the Stone-Ostriker profile \citep{2015ApJ...806L..28S}, which is a three-parameter potential-density pair.
+Quantities such as density, potential, and binding energy can be written in closed form, which speeds up computations.
 It is essentially an analytic form of a finite, cored isothermal mass distribution:
@@
 
-In order to parameterize this profile, $r_c$ was given an initial value of 100 pc, which is reasonable for a cored massive system.
-To calculate $r_h$, we began by using the stellar mass to calculate the velocity dispersion at the galaxy's effective radius.
-In \citet{2014ApJ...789..156M}, the galaxy's effective radius $R_{e}$ and velocity dispersion $\sigma(R_e)$ at the effective radius are:
+The central density, $\rho_c$, can be found from inverting Equation 5 for the galaxy's total mass in Stone-Ostriker:
+
+\begin{equation} \label{rhoc}
+M_{DM} = \frac{2\pi^2r_{c}^2r_{h}^2\rho_c}{r_h+r_c}.
+\end{equation}
+
+In order to parameterize $r_c$ and $r_h$, we can utilize the relationship between the distribution of light and stellar velocity dispersion at the effective radius, and the shape of the dark matter profile.
+The effective radius $R_{e}$ and velocity dispersion at the effective radius $\sigma(R_e)$, respectively, can be obtained from (\citet{2009ApJ...706L..86N}, \citet{2010ApJ...725.2312O}, \citet{2014ApJ...789..156M}):
+
 \begin{equation} \label{re}
@@
 
+We also give $r_c$ an initial value of 100 pc, which is reasonable for a cored massive system.
 We can then equate the value for $\sigma({R_e})$ obtained from Equation \ref{sig} to the analytic expressions for $\sigma$ in the Stone-Ostriker profile (cf.
@@
 
-The central density, $\rho_c$, can be found from Equation 5 in Stone-Ostriker:
-\begin{equation} \label{rhoc}
-M_\mathrm{DM} = \frac{2\pi^2r_{c}^2r_{h}^2\rho_c}{r_h+r_c}.
-\end{equation}
-
-At each iteration in the code, $r_h$ is updated according to the stellar mass and Equations \ref{re} and \ref{sig}.
+At each timestep in the code, $r_h$ is updated according to the stellar mass and Equations \ref{re} and \ref{sig}.
 The core radius, $r_c$, is recalculated only if an orbiting black hole enters within $r_c$.
@@
 \subsubsection{Phase-space diffusion} \label{psd}
-THIS SECTION TAKEN VERBATIM FROM \citet{2017MNRAS.467.4180S}, SECTION E1.  NEED TO MODIFY.
-Weak encounters with background stars will let the SMBHs diffuse through phase space while they are orbiting within the gravitational potential of the galaxy.
+Much of this subsection was borrowed from \citet{2017MNRAS.467.4180S}, Section E1, which made use the same modified version of \textsc{AR-Chain}.
+
+Weak encounters with background stars and dark-matter particles will let the SMBHs diffuse through phase space while they are orbiting within the gravitational potential of the galaxy.
 The diffusion can be expressed as change in velocity of an SMBH by $\Delta \vec{v}$ per unit time.
@@
 \begin{eqnarray}\label{eq:df}
-D[\Delta v_\parallel] & = & -\frac{4\pi G^2\rho(r)M_\bullet\ln\Lambda}{\sigma^2}f(\chi),\\
-D[(\Delta v_\parallel)^2] & = & \frac{4\sqrt{2}\pi G^2\rho(r)M_\bullet\ln\Lambda}{\sigma}\frac{f(\chi)}{\chi},\\
-D[(\Delta \vec{v}_\bot)^2] & = & \frac{4\sqrt{2}\pi G^2\rho(r)M_\bullet\ln\Lambda}{\sigma}\left[\frac{\mbox{erf}(\chi)-f(\chi)}{\chi}\right],
+D[\Delta v_\parallel] & = & -\frac{4\pi G^2\rho(r)M_{BH}\ln\Lambda}{\sigma^2}f(\chi),\\
+D[(\Delta v_\parallel)^2] & = & \frac{4\sqrt{2}\pi G^2\rho(r)M_{BH}\ln\Lambda}{\sigma}\frac{f(\chi)}{\chi},\\
+D[(\Delta \vec{v}_\bot)^2] & = & \frac{4\sqrt{2}\pi G^2\rho(r)M_{BH}\ln\Lambda}{\sigma}\left[\frac{\mbox{erf}(\chi)-f(\chi)}{\chi}\right],
 \end{eqnarray} 
 where $\Delta v_\parallel \equiv \Delta \vec{v}\cdot\vec{v}/v$ is the velocity change in direction of motion, and $\Delta \vec{v}_\bot \equiv \Delta \vec{v} - \Delta v_\parallel \cdot\vec{v}/v$ is the velocity change perpendicular to the direction of motion.
-Here, $M_\bullet$ is the mass of the black hole, and $\chi = \frac{v}{\sqrt{2}\sigma(r)}$.
+Here, $M_{BH}$ is the mass of the black hole, and $\chi = \frac{v}{\sqrt{2}\sigma(r)}$.
 The function $f(\chi)$ is given by
@@
 \begin{equation}
-\Lambda \equiv \left(\frac{M_{NSC}}{M_\bullet}\right)\left(\frac{r}{r_h}\right).
+\Lambda \equiv \left(\frac{M_{M_{DM}}}{M_{BH}}\right)\left(\frac{r}{r_h}\right).
 \end{equation}
 We can identify Equation \ref{eq:df} as the dynamical friction term.
-The second term introduces a variance of the friction term, and even allows the SBHs to be accelerated when the velocity of a SBH is sufficiently small.
-The third term introduces a change in velocity perpendicular to the direction of motion of the SBH.
-It is a randomly oriented vector, and hence causes the SBHs to depart from smooth orbits due to the small random velocity kicks.
-The last two terms will establish that the SBHs are ultimately in energy equipartition with the background stars.
+The second term introduces a variance of the friction term, and even allows the BHs to be accelerated when the velocity of a BH is sufficiently small.
+The third term introduces a change in velocity perpendicular to the direction of motion of the BH.
+It is a randomly oriented vector, and hence causes the BHs to depart from smooth orbits due to the small random velocity kicks.
+The last two terms will establish that the BHs are ultimately in energy equipartition with the background stars.
 The velocity changes $\Delta v_\parallel$ and $\Delta\vec{v}_\bot$ per unit time $\Delta t$ can be computed with the above equations.
@@
 We compute the diffusion coefficients for each black hole at each time step, and modify its velocity on a Monte Carlo basis.
-For each time step we draw a random orientation before adding the perpendicular velocity change to the respective SBH.
-Hence, the SBH's modified velocity, $v_f$, is computed using
+For each time step we draw a random orientation before adding the perpendicular velocity change to the respective BH.
+Hence, the BH's modified velocity, $v_f$, is computed using
 \begin{eqnarray}
@@
 \end{eqnarray}
-The change of energy, $\mbox{d}E_{BH}$, of the orbiting black hole due to phase-space diffusion is given back to the stellar background potential, with $\mbox{d}E = -\mbox{d}E_{BH}$.
-As a consequence of this energy transfer, inspiralling black holes will cause an expansion of the stellar system.
-For this purpose we calculate the change in potential energy, $\mbox{d}W$, of the stellar system using
+The change of energy, $\mbox{d}E_{BH}$, of the orbiting black hole due to phase-space diffusion is given back to the galactic background potential, with $\mbox{d}E = -\mbox{d}E_{BH}$.
+As a consequence of this energy transfer, inspiralling black holes will cause an expansion of the galactic mass distribution.
+For this purpose we calculate the change in potential energy, $\mbox{d}W$, of the host galaxy using
 \begin{eqnarray}
@@
 where we made use of the virial theorem $2T+W =0$.
-With this change in potential energy we can calculate a new radius for the stellar background potential at each integration step.
-For the Plummer sphere the new scale radius can be calculated as
-\begin{equation}
-a_{new} = a\left(1+\frac{32a\,\mbox{d}W}{3\pi GM_{NSC}^2}\right)^{-1}.
-\end{equation}
+With this change in potential energy we can calculate a new radius for the galactic background potential at each integration step.
+For simplicity, we assumed that the relatively low mass of the infalling black holes compared to the core mass of the host galaxies would only affect the size of the core radius, and hence ignored the feedback effect when the black holes were outside of the core radius.
 
-\subsubsection{Gravitational wave recoils}
+\subsubsection{Gravitational wave recoils and escape}
 The code \textsc{AR-Chain} includes post-Newtonian terms up to order 2.5.
@@
 A result of the anisotropic emission of gravitational waves is that the merged binary often experiences a linear kick in the opposite direction of the emission of the GW due to conservation of linear momentum.
-This kick can result in velocities of the merged binary from approximately $200-5000\ km s^{-1}$ (see \citet{2007PhRvL..98w1101G}, \citet{2007PhRvL..98i1101G}, \citet{2007PhRvL..98w1102C}, \citet{2011PhRvL.107w1102L}).
+This kick can result in velocities of the merged binary from approximately $200-5000\ km s^{-1}$ (see \citealt{2007PhRvL..98w1101G, 2007PhRvL..98i1101G, 2007PhRvL..98w1102C, 2011PhRvL.107w1102L}.
 In our simulations, the binaries never stray more than a few tens of parsecs from the nucleus of the host galaxies.
@@
 
-\section{Results}\label{sec:results}
-Here we review the primary results of our simulations, focusing on the various interactions of the orbiting black holes with their host SMBHs and the final luminosity characteristics of those that did not merge.
+\section{Simulation Results}\label{sec:results}\label{sec:results_overview}
+Here we review the primary results of our simulations, focusing on the various interactions of the orbiting black holes with their host SMBHs.
+In the next section, we will investigate the luminosity characteristics of the orbiting black holes that did not merge at $z=0$.
 
-\subsection{Mergers, Ejections/Kicks and Orbiting SMBHs}
-
-\subsubsection{Overview of Results}\label{sec:results_overview}
-Figure \ref{fig:meosmbh} shows the distribution of merged, ejected and orbiting black holes across all galaxy simulations as a function of guest black hole mass.
+Figure \ref{fig:meosmbh} shows the distribution of merged, ejected and orbiting black holes (stacked) across all galaxy simulations as a function of the mass of the infalling black holes.
 
@@
 
-\subsubsection{Mergers}\label{sec:mergers}
+\subsection{Mergers}\label{sec:mergers}
 The tendency of larger mass black holes to merge with their host can perhaps be more clearly seen by looking at the merger mass ratio between the incoming black hole and the host.
@@
 
-\subsubsection{Kicked, Ejected and Orbiting Black Holes}\label{sec:kicked_orbiting}
+Approximately 50\% of the mergers appeared to have been directly assisted by a hard three-body encounter with a third rendezvousing black hole, which as a consequence got kicked to a higher orbit (and in a few instances ejected).
+A large fraction of the remaining BH mergers were accelerated through soft encounters with infalling black holes.
+Our simulations suggest that few-body encounters are in fact a significant driver of BH-BH mergers in galactic centers.
+
+\subsection{Kicked, Ejected and Orbiting Black Holes}\label{sec:kicked_orbiting}
 Of the 37 orbiting black holes at $z=0$, 18 of them were kicked to higher orbits during traversal of their host galaxy.
@@
 
-Figure \ref{fig:kicked_stats} shows the mass distribution of kicked and not-kicked black holes, including those that merged and those that did not merge.
+Figure \ref{fig:kicked_stats} shows the mass distribution (stacked) of kicked and not-kicked black holes, including those that merged and those that did not merge.
 The vast majority of larger SMBHs ($\goa\, 10^7\, M_{\odot}$) were not kicked to higher orbits nor ejected from their galaxies, which at least partly explains why most of the merged SMBHs are in the greater mass range.
@@
 Figure \ref{fig:mvr} is a realization of the final radii of the remaining wandering black holes at $z=0$.
-There does not appear to be a correlation between mass and final radius.
-However, it is evident from the plot that all but one of the black holes that had not been kicked by $z=0$ have mostly approached and entered within the galactic core radius, $r_c$.
+There is a slight inverse relationship between black hole mass and final radius (solid line), but with a wide dispersion.
+It is also evident from the plot that all but two of the black holes that had not been kicked by $z=0$ have mostly approached and entered within the galactic core radius, $r_c$ (which never exceeded 1 kpc in any of the galaxies).
 
@@
 Colored arrows along upper x-axis represent median masses of respective sets.
-Histogram bars are not stacked.}
+Histogram bars are stacked.}
 \label{fig:meosmbh}
@@
 \includegraphics[width=0.5\textwidth]{plots/kicked_stats.png}
-\caption{Histogram of kicked and not-kicked SMBHs at z=0.  Colored arrows along upper x-axis represent median masses of respective sets.  Histograms are not stacked.}
+\caption{Histogram of kicked and not-kicked SMBHs at z=0.  Colored arrows along upper x-axis represent median masses of respective sets.  Histograms are stacked.}
 \label{fig:kicked_stats}
@@
 \includegraphics[width=0.5\textwidth]{plots/"Final Radius v Mass of Orbiting BHs".png}
-\caption{Final Radii of remaining orbital black holes at z=0.}
+\caption{Final Radii of remaining orbital black holes at z=0.
+Kicked black holes generally had a low likelihood of finding their way back to the center by z=0.
+There is a slight inverse relationship between BH mass and final distance from center (solid line).}
 \label{fig:mvr}
@@
 
+\section{Signatures of Orbiting Black Holes}
+The large fraction of orbiting black holes predicted by our simulations motivates a back-of-the-envelope calculation to see if orbiting black holes produce detectable signatures.
+In the following section, we estimate the X-ray luminosities of gas accreted by these BHs while orbiting through their host galaxies.
+
 \subsection{Galaxy Gas X-Ray Luminosity}
-We compute the x-ray luminosity of the hot gas in the galaxies, adapting Equation 26 from \citet{2012ApJ...754..125C}.
+First, we construct realistic X-ray luminosities for our host galaxies.
+We compute the X-ray luminosity of the hot gas in these galaxies, adapting Equation 26 from \citet{2012ApJ...754..125C}.
 In lieu of summing over discrete particles, we use the beta model of the gas as defined in our equation \ref{beta_model} and integrate:
@@
 This results in $\mu=0.606$.
+The resulting X-ray luminosities are shown in Figures \ref{fig:galgas1} and compared against a sample from \citet{2018ApJ...857...32B}.
 
-\subsection{Black Hole Xray Luminosity}
+\subsection{Black Hole X-Ray Luminosity}
 \subsubsection{Assumptions and Method Employed}
-Since we model the black holes in this work as point particles for purposes of the simulations, we don't assume any particular structure to them.
-Therefore, we adopt the approach and assumptions from \citealt{2018MNRAS.476.1412I} and \citealt{2019MNRAS.486.5377I} in estimating the x-ray luminosities of the remaining black holes left wandering in our subject galaxies.
+Since we model the black holes in this work as point particles for purposes of the simulations, we do not assume any particular structure to them.
+Therefore, we adopt the approach and assumptions from \citealt{2018MNRAS.476.1412I} and \citealt{2019MNRAS.486.5377I} in estimating the X-ray luminosities of the remaining black holes left wandering in our subject galaxies.
 Their approach assumes rotating accretion flows in a very low-density environment.
@@
 \subsubsection{Gas Environment Surrounding Black Holes}
-In order to model the surrounding environment of the wandering black holes, we used the data and scaling relations from \citet{2018ApJ...857...32B}, which is based on Chandra X-ray Observatory observations of 94 early-type, gas poor galaxies of several morphological types (elliptical, lenticular, SB, BCGs, and cD galaxies).
-In particular, we used data from Tables 2 and 3 for temperature in xray ($T_X$) and central gas density ($\rho_0$)) to model the surrounding gas properties.
-Central velocity dispersion ($\sigma_c$) was used as the independent variable, as many galactic properties co-evolve with velocity dispersion (REFERENCES TO BACK THIS UP???).
+In order to model the surrounding environment of the wandering black holes, we used the data and scaling relations from \citet{2018ApJ...857...32B}, which are based on Chandra X-ray observations of 94 early-type, gas poor galaxies of several morphological types (elliptical, lenticular, SB, BCGs, and cD galaxies).
+In particular, we used data from Tables 2 and 3 for temperature in X-ray ($T_X$) and central gas density ($\rho_0$) to model the surrounding gas properties.
+Central velocity dispersion ($\sigma_c$) was used as the independent variable.
 We estimate the central velocity dispersion in this work based on the potential-density profile in  \citet{2015ApJ...806L..28S} that was also used in modeling the potential in the simulations (cf their equation 11):
@@
 
-Figures \ref{fig:rho0_vs_sigma} and \ref{fig:Tx_vs_sigma} present the data from \citet{2018ApJ...857...32B}, along with the simple linear fits (in log-log space) and resulting gas properties used for our galaxies (red x's):
+Figures \ref{fig:rho0_vs_sigma} and \ref{fig:Tx_vs_sigma} present the data from \citet{2018ApJ...857...32B}, along with the simple linear fits (in log-log space) and resulting gas properties used for our galaxies:
 \begin{subequations} \label{eq:gas_properties}
 \begin{eqnarray}
-    \rho_0 = 10^{0.6*log\left(\frac{\sigma_c}{g\ cm^{-3}}\right) - 25} \text{  g cm}^{-3},\\
-    T_x = 10^{2.50*log\left(\frac{\sigma_c}{g\ cm^{-3}}\right) - 6.06} \text{  keV}.
+    \rho_0 = 10^{0.6*\log\left(\frac{\sigma_c}{g\ cm^{-3}}\right) - 25} \text{  g cm}^{-3},\\
+    T_x = 10^{2.50*\log\left(\frac{\sigma_c}{g\ cm^{-3}}\right) - 6.06} \text{  keV}.
 \end{eqnarray}
@@
 
-The dispersion of the xray temperature data around the fit is approximately 1-1.5 orders of magnitude.
+The dispersion of the X-ray temperature data around the fit is approximately 1-1.5 orders of magnitude.
 The gas sound speed (see Equation \eqref{gas_sound_speed} below) has a $C_s{\sim}T_x^{0.5}$ dependence on temperature.
@@
 Purple X's represent central gas densities of the galaxies in this study.
-Fit in log space is $\rho_0 = 10^{0.6*log\left(\frac{\sigma_c}{g\ cm^{-3}}\right) - 25} \text{  g cm}^{-3}$.}
+Fit in log space is $\rho_0 = 10^{0.6*\log\left(\frac{\sigma_c}{g\ cm^{-3}}\right) - 25} \text{  g cm}^{-3}$.}
 \label{fig:rho0_vs_sigma}
@@
 Purple X's represent temperatures of the galaxies in this study.
-Fit in log space is $T_x = 10^{2.50*log\left(\frac{\sigma_c}{g\ cm^{-3}}\right) - 6.06} \text{  keV}$.}
+Fit in log space is $T_x = 10^{2.50*\log\left(\frac{\sigma_c}{g\ cm^{-3}}\right) - 6.06} \text{  keV}$.}
 \label{fig:Tx_vs_sigma}
@@
 
-The local gas density ${\rho}$ surrounding the black hole is obtained from a simple isothermal beta model (\citet{1962AJ.....67..471K}, \citet{1976A&A....49..137C}, \citet{1978A&A....70..677C}):
+The local gas density ${\rho}$ surrounding the black hole is obtained from a simple isothermal beta model \citep{1962AJ.....67..471K, 1976A&A....49..137C, 1978A&A....70..677C}:
 \begin{equation} \label{beta_model}
@@
 eq 13.
-Additionally, $M_{BH}$ is black hole mass, $G$ is the gravitational constant, and $v$ is the black hole velocity.
+Additionally, $M_{BH}$ is the black hole mass, $G$ is the gravitational constant, and $v$ is the black hole velocity.
 
-Finally, the black hole x-ray luminosity is estimated from:
+Finally, the black hole X-ray luminosity is estimated from:
 \begin{equation}
@@
 \end{equation}
-where the x-ray radiative efficiency ${\epsilon}_{rx}=0.01$, and we are assuming for the low-luminosity sources that $L_x{\sim}L_{Bol}$.
+where the X-ray radiative efficiency ${\epsilon}_{rx}=0.01$, and we are assuming for the low-luminosity sources that $L_x{\sim}L_{Bol}$.
 For sources having $\dot{M}_B/\dot{M}_{Edd} > 10^{-3}$, we take $L_x=0.1L_{Bol}$, due to the higher net accretion onto the black hole as a result of cooling of the accretion disc and hence higher gas density.
-The Eddington limit is defined as:
+The corresponding Eddington limit is defined as:
 \begin{equation}
@@
 \includegraphics[width=0.5\textwidth]{plots/"Comparison of L_x versus radius with and without BH Influence".png}
-\caption{Difference in x-ray luminosity of wandering black holes within the influence radius of the central black hole.
+\caption{Difference in X-ray luminosity of wandering black holes within the influence radius of the central black hole.
 For each vertical line, red (lower) dots are the originally calculated luminosity, not taking the CBH influence into account.
@@
 \subsubsection{Final X-ray Luminosities of Wandering Black Holes, and Expected Detection Spectra}
-Figure \ref{fig:loobhs} is an approximation of Figure 12 from \cite{2019MNRAS.486.5377I}, along with the final $L_{Bol}/L_{Edd}$ ratio of the wandering black holes from this study, although extended below $10^{-6}$ $\dot{M}_{B}/\dot{M}_{Edd}$ for the very low accretion-rate sources.
+Figure \ref{fig:loobhs} is an approximation to Figure 12 from \cite{2019MNRAS.486.5377I}, along with the final $L_{Bol}/L_{Edd}$ ratio of the wandering black holes from this study, although extended below $10^{-6}$ $\dot{M}_{B}/\dot{M}_{Edd}$ for the very low accretion-rate sources.
 Indeed, such low luminosity sources are common, with some estimates of $L_{Bol}/L_{Edd}$ as low as $10^{-10}$ ( e.g., \citealt{2003ApJ...598..301Y}, \citealt{2004ApJ...613..322Q}, \citealt{2008ARA&A..46..475H}, \citealt{2009ApJ...699..626H}, \citealt{2018MNRAS.476.1412I}).
-ANY REFERENCES TO SUPPORT HIGHER MdotB/MdotEdd and LBOL/LEDD???
-NOT SURE WHAT ELSE TO ADD HERE REGARDING POTENTIAL FOR DETECTION.
 \begin{figure}
@@
 \includegraphics[width=0.5\textwidth]{plots/"luminosities_final".png}
-\caption{Approximation of Figure 12 from \citealt{2019MNRAS.486.5377I}. Black "X"s represent black holes in this study.}
+\caption{Approximation to Figure 12 from \citealt{2019MNRAS.486.5377I}. Black "o"s represent black holes in this study.  We also include observational results for Sgr A*, and BHs in M31 and M87.}
 \label{fig:loobhs}
@@
 
-Figure \ref{fig:ldobhs} represents a histogram of the final x-ray luminosities of the black holes, overlaid by a lognormal distribution.  
+Figure \ref{fig:ldobhs} represents a histogram of the final X-ray luminosities of the black holes, overlaid by a lognormal distribution.  
 \begin{figure}
@@
 \includegraphics[width=0.5\textwidth]{plots/"Final Luminosities using Kohei factor".png}
-\caption{Xray Luminosity Distribution of Orbiting BHs at z=0.  Green region under curve represents approximate range of detectable orbiting black holes.}
+\caption{X-ray Luminosity Distribution of Orbiting BHs at z=0.
+Green region under curve represents approximate range of detectable orbiting black holes.
+The dashed, red vertical line is the median X-ray luminosity of our sources.}
 \label{fig:ldobhs}
@@
 
-The orbiting black holes should be detectable via their anomalous soft x-ray spectra.
+The orbiting black holes should be detectable via their anomalous soft X-ray spectra.
 Sgr A*, the black hole at the center of the Milky Way Galaxy, has been observed to fit a power law spectrum with photon index $\Gamma\sim2.7^{+1.3}_{-1.9}$ \citet{2003ApJ...591..891B}.
-Conversely low-mass x-ray binaries (LMXRB) have been fit to a power law spectrum with $\Gamma\sim1.5-2.0$ (\citet{2018Natur.556...70H}.
+Conversely low-mass X-ray binaries (LMXRB) have been fit to a power law spectrum with $\Gamma\sim1.5-2.0$ (\citet{2018Natur.556...70H}, and we expect our orbiting sources to be more similar to Sgr A* than to normal LMXRBs.
 
 \section{Conclusions}\label{sec:conclusions}
-We performed N-body simulations on 11 galaxies ranging in mass between $10^{12}$ M$_{\sun}$ < M < 3$\times$ $10^{13}$ M$_{\sun}$, from 4 $\gid$ z $\gid$ 0.
+We performed N-body simulations on 11 galaxies ranging in mass between $10^{12}$ M$_{\sun}$ < M < 3$\times$ $10^{13}$ M$_{\sun}$, from 4 $\geq$ z $\geq$ 0.
 A total of 86 orbiting black holes were followed in our simulations, resulting in 42$\%$ mergers with their host galaxy's resident black hole, while another 43$\%$ remained in orbit at $z=0$.
-Those remaining orbiting black holes had x-ray luminosities in the range of $10^{25}-10^{43}$ $erg\ s^{-1}$.
-The median luminosity of $10^{32} erg\ s^{-1}$ would be undetectable with present instruments, although the top $5\%$ most luminous from this set could be detectable.
+Those remaining orbiting black holes had X-ray luminosities in the range of $10^{28}-10^{43}\mathrm{erg}~\mathrm{s}^{-1}$.
+The median luminosity of $10^{33}\mathrm{erg}~\mathrm{s}^{-1}$ would be undetectable with present instruments, although the top $5\%$ most luminous from this set could be detectable.
 
@@
 The authors would like to thank Andrea Kulier and Claire Lackner for providing merger tree data.
-We also thank Renyue Cen, Pieter van Dokkum, Charles Hailey, Zoltan Haiman, Kohei Inayoshi, Sean McWilliams, and Taeho Ryu for useful discussions and insights.
+We also thank Renyue Cen, Pieter van Dokkum, Charles Hailey, Zoltan Haiman, Kohei Inayoshi, Sean McWilliams, Taeho Ryu and Nick Stone for useful discussions and insights.
 AHWK acknowledges support by NASA through Hubble Fellowship grant HST-HF-51323.01-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS 5-26555.

### 2020-03-08 paper.tex
Last commit prior to changing text regarding calculation of luminosities (Section 4.2.2).

@@
 % These dates will be filled out by the publisher
-\date{Last updated 2020 Jan 16; in original form 2020 Jan 16}
+\date{Last updated 2020 Jan 27; in original form 2020 Jan 27}
 
@@
 These orbiting BHs should be detectable by their anomalous (not LMXRB) spectra.
-The X-ray luminosities of the orbiting massive BHs at z=0 are in the range $10^{27}-10^{43}$ $\mathrm{erg}~\mathrm{s}^{-1}$, with a currently undetectable median value of $10^{33}$ $\mathrm{erg}~\mathrm{s}^{-1}$.
+The X-ray luminosities of the orbiting massive BHs at z=0 are in the range $10^{28}-10^{43}$ $\mathrm{erg}~\mathrm{s}^{-1}$, with a currently undetectable median value of $10^{33}$ $\mathrm{erg}~\mathrm{s}^{-1}$.
 However, the most luminous $\sim$5\% should be detectable by existing X-ray facilities.
@@
 
-The resulting net black hole mass accretion rate is approximated by \citet{2018MNRAS.476.1412I} and \citet{2019MNRAS.486.5377I}:
+The resulting net black hole mass accretion rate is approximated by \citet{1944MNRAS.104..273B} and \citet{1952MNRAS.112..195B}:
 \begin{equation}\label{net_accretion}
@@
 \end{equation}
-where f is a factor giving the decline in accretion, interior to the BH radius due to convective (i.e., inefficient) accretion, as calculated \citet{2019MNRAS.486.5377I}, cf.
+where the additional factor $f$ (see \cite{2018MNRAS.476.1412I} and \cite{2019MNRAS.486.5377I}) gives the decline in accretion, interior to the BH radius due to convective (i.e., inefficient) accretion, as calculated in \citet{2019MNRAS.486.5377I}, cf.
 eq 13.
@@
 \end{equation}
-where the X-ray radiative efficiency ${\epsilon}_{rx}=0.01$, and we are assuming for the low-luminosity sources that $L_x{\sim}L_{Bol}$.
+where the X-ray radiative efficiency ${\epsilon}_{rx}=0.01$ , and we are assuming for the low-luminosity sources that $L_x{\sim}L_{Bol}$.
 For sources having $\dot{M}_B/\dot{M}_{Edd} > 10^{-3}$, we take $L_x=0.1L_{Bol}$, due to the higher net accretion onto the black hole as a result of cooling of the accretion disc and hence higher gas density.

### 2020-03-11 paper.tex
Rewrote Black Hole Accretion and Luminosity Section ($4.2.3)

@@
 \usepackage{pdflscape}	% Landscape pages
+\usepackage{comment}
 
@@
 \begin{abstract}
-We perform follow-up N-body simulations on some of the most massive galaxies extracted from a cosmological simulation of hierarchical structure formation with total masses in the range $10^{12} M_{\sun} < M < 3\times 10^{13} M_{\sun}$ from $4\geq z \geq 0$.
+We perform N-body simulations on some of the most massive galaxies extracted from a cosmological simulation of hierarchical structure formation with total masses in the range $10^{12} M_{\sun} < M_{tot} < 3\times 10^{13} M_{\sun}$ from $4\geq z \geq 0$.
 After galactic mergers, we track the dynamical evolution of the infalling black holes (BHs) around their host's central BHs.
@@
 Across all galaxies, 33 BHs are kicked to a higher orbit after close interactions with the central BH binary or multiple, after which only one of them merged with their hosts.
-These orbiting BHs should be detectable by their anomalous (not LMXRB) spectra.
+These orbiting BHs should be detectable by their anomalous (not Low Mass X-ray Binary) spectra.
 The X-ray luminosities of the orbiting massive BHs at z=0 are in the range $10^{28}-10^{43}$ $\mathrm{erg}~\mathrm{s}^{-1}$, with a currently undetectable median value of $10^{33}$ $\mathrm{erg}~\mathrm{s}^{-1}$.
@@
 The computational challenge of this investigation is a wide range of time-scales.
-Galactic evolution and galactic orbits take hundreds of millions to billions of years, while orbital times of BH binaries may require times steps of years for accurate integration.
+Galactic evolution and galactic orbits take hundreds of millions to billions of years, while orbital times of BH binaries may require time steps of years for accurate integration.
 We overcome this challenge by simplifying the model where possible, and by focussing on the main drivers of BH dynamics: the galactic background potential, dynamical friction, and strong BH-BH encounters.
@@
 It uses algorithmic chain regularization for high-precision integration of few-body dynamics, and is capable of handling velocity-dependent forces efficiently.
-It includes relativistic post-Newtonian terms up to order PN2.5 \citep{2008AJ....135.2398M}.
+It includes relativistic post-Newtonian terms up to order 2.5 \citep{2008AJ....135.2398M}.
 
@@
 
-\citet{2012MNRAS.425..641L}, using \citet{2011ApJ...741...99C}'s work as a basis, created galactic merger trees that compared the properties of in-situ and accreted stellar mass of galaxies at redshift snapshots between $4 \geq z \geq 0$.
+\citet{2012MNRAS.425..641L}, using \citet{2011ApJ...741...99C}'s work as a basis, created galactic merger trees that compared the properties of in-situ and accreted stellar mass of galaxies at redshift snapshots between $4\geq z \geq0$.
 
@@
 \subsubsection{Stellar Mass Adjustment}
-As we will explain further in Section \ref{Galaxy background potential}, in our simulations orbiting black holes are inserted into the host galaxy at the effective radius, $R_e$, which is partially dependent on stellar mass, $M_*$ (see Eqn.
-\ref{re}).
+As we will explain further in Section \ref{Galaxy background potential}, in our simulations orbiting black holes are inserted into the host galaxy at the effective radius, $R_e$, which is partially dependent on stellar mass, $M_*$ (see Equation \ref{re}).
 For every doubling of the stellar mass, $R_e$ increases by a factor of 1.66.
-Additionally, the velocity dispersion at the effective radius, $\sigma(R_e)$, which is used to set the parameter $r_h$ (see Eqn.
-\ref{jerry}) of our dark matter profile, is also dependent on $M_*$.
+Additionally, the velocity dispersion at the effective radius, $\sigma(R_e)$, which is used to set the parameter $r_h$ (see Equation \ref{jerry}) of our dark matter profile, is also dependent on $M_*$.
 In this case, a doubling of $M_*$ would increase $\sigma(R_e)$ by a factor of 1.15.
@@
 \subsection{Simulation Physics}
-In this section, we describe the underlying physics of our simulations, including choice of galaxy background potential, BH diffusion through the galaxy, and gravitational wave kicks as a result of mergers.
+In this section, we describe the underlying physics of our simulations, including choice of galaxy background potential, BH diffusion through the galaxy, and gravitational wave kicks as a result of black hole mergers.
 
@@
 
-The central density, $\rho_c$, can be found from inverting Equation 5 for the galaxy's total mass in Stone-Ostriker:
+The central density, $\rho_c$, can be found from inverting Equation 5 in Stone and Ostriker 2015 for the galaxy's total mass:
 
@@
 We can then equate the value for $\sigma({R_e})$ obtained from Equation \ref{sig} to the analytic expressions for $\sigma$ in the Stone-Ostriker profile (cf.
-Eqns 9 and A1-A4).
+Equations 9 and A1-A4).
 The only unknown is $r_h$, which we can solve for using a simple recursive Newton method.
@@
 We include gravitational wave recoils following the prescription outlined in \citet{2015ApJ...799..178K}, which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.
-We assume that a merger will be inevitable when the separation between two SMBHs becomes smaller than 1.0x the Schwarzschild radius.
+We assume that a merger will be inevitable when the separation between two SMBHs becomes smaller than the Schwarzschild radius.
 At the moment of the merger, we also assume that the spin vectors of the two SBHs are randomly aligned.
@@
 A result of the anisotropic emission of gravitational waves is that the merged binary often experiences a linear kick in the opposite direction of the emission of the GW due to conservation of linear momentum.
-This kick can result in velocities of the merged binary from approximately $200-5000\ km s^{-1}$ (see \citealt{2007PhRvL..98w1101G, 2007PhRvL..98i1101G, 2007PhRvL..98w1102C, 2011PhRvL.107w1102L}.
+This kick can result in velocities of the merged binary from approximately $200-5000\ km\ s^{-1}$ (see \citealt{2007PhRvL..98w1101G, 2007PhRvL..98i1101G, 2007PhRvL..98w1102C, 2011PhRvL.107w1102L}).
 In our simulations, the binaries never stray more than a few tens of parsecs from the nucleus of the host galaxies.
@@
 \end{equation}
-The orbiting black holes were injected into their host galaxy at redshift z, at a distance from the galactic center of $R_{e}$ (Equation \ref{re}) following galaxy mergers.
+The orbiting black holes were injected into their host galaxy at redshift $z$, at a distance from the galactic center of $R_{e}$ (Equation \ref{re}) following galaxy mergers.
 Their initial velocity was arbitrarily chosen to be circular, $v_c = \sqrt{GM(R_e)/R_e}$, with $v_x$, $v_y$, and $v_z$ randomly chosen.
@@
 In order to model the surrounding environment of the wandering black holes, we used the data and scaling relations from \citet{2018ApJ...857...32B}, which are based on Chandra X-ray observations of 94 early-type, gas poor galaxies of several morphological types (elliptical, lenticular, SB, BCGs, and cD galaxies).
-In particular, we used data from Tables 2 and 3 for temperature in X-ray ($T_X$) and central gas density ($\rho_0$) to model the surrounding gas properties.
+In particular, we used data from Tables 2 and 3 for temperature in X-ray ($T_x$) and central gas density ($\rho_0$) to model the surrounding gas properties.
 Central velocity dispersion ($\sigma_c$) was used as the independent variable.
@@
 \begin{eqnarray}
-    \rho_0 = 10^{0.6*\log\left(\frac{\sigma_c}{g\ cm^{-3}}\right) - 25} \text{  g cm}^{-3},\\
-    T_x = 10^{2.50*\log\left(\frac{\sigma_c}{g\ cm^{-3}}\right) - 6.06} \text{  keV}.
+    \rho_0 = 10^{0.6*\log\left(\frac{\sigma_c}{km\ s^{-1}}\right) - 25} \text{  g cm}^{-3},\\
+    T_x = 10^{2.50*\log\left(\frac{\sigma_c}{km\ s^{-1}}\right) - 6.06} \text{  keV}.
 \end{eqnarray}
@@
 The dispersion of the data around the fit for $\rho_0$ is at most 1.5-2.0 orders of magnitude.
-This leads to a similar variation in the gas density surrounding the black hole, in addition to the ultimate accretion rate of the black hole, due to both having a linear dependence on the central gas density (see Eqns \eqref{beta_model} and \eqref{net_accretion} below).
+This leads to a similar variation in the gas density surrounding the black hole, in addition to the ultimate accretion rate of the black hole, due to both having a linear dependence on the central gas density (see Equations \eqref{beta_model} and \eqref{net_accretion} below).
 
 The dispersion of the X-ray temperature data around the fit is approximately 1-1.5 orders of magnitude.
-The gas sound speed (see Equation \eqref{gas_sound_speed} below) has a $C_s{\sim}T_x^{0.5}$ dependence on temperature.
-However, given the dependence of the accretion rate (see Equation \eqref{net_accretion} below) on gas sound speed of $\dot{M}_{acc}{\sim}C_s^3$, the accretion rate is dependent on temperature to the order of $T_x^{3/2}$.
+The gas sound speed (see Equation \eqref{gas_sound_speed} below) has a $C_s{\propto}T_x^{0.5}$ dependence on temperature.
+However, given the dependence of the accretion rate (see Equation \eqref{net_accretion} below) on gas sound speed of $\dot{M}_{acc}{\propto}C_s^3$, the accretion rate is dependent on temperature to the order of $T_x^{3/2}$.
 This is another source of variation in our estimate of accretion rate.
@@
 \begin{equation}\label{gas_sound_speed}
-    C_s = \sqrt{1.67T_x*\expnumber{1.602}{-16}/m_p} \text{  km s}^{-1},
+    C_s = \sqrt{1.67T_x*1.602\times10^{-16}/m_p} \text{  km s}^{-1},
 \end{equation}
-where $m_p$ is the proton mass in kilograms.  Since $T_x$ is in keV, the factor of $\expnumber{1.602}{-16}$ is added to convert the temperature to Joules.
+where $m_p$ is the proton mass in kilograms.  Since $T_x$ is in keV, the factor of $1.602\times10^{-16}$ is added to convert the temperature to Joules.
 
+\subsubsection{Black Hole Mass Accretion and Luminosity}
+In theory, the black hole mass accretion rate is governed by the Bondi-Hoyle formula (\citet{1944MNRAS.104..273B} and \citet{1952MNRAS.112..195B}):
+\begin{equation}\label{net_accretion}
+    \dot{M}_{B} = f\frac{4{\pi}G^2M_\mathrm{BH}^2\rho}{(C_s^2+v^2)^{3/2}} \text{  g}\text{ s}^{-1},
+\end{equation}
+where $\rho$ is the density of the surrounding gas, $C_s$ is the gas sound speed, and $v$ is the velocity of the black hole.
+
+However, due to convective (i.e., inefficient) accretion interior to the Bondi radius (see \cite{2018MNRAS.476.1412I} and \cite{2019MNRAS.486.5377I}), the net accretion to the black hole is often substantially lower than the Bondi-Hoyle accretion.
+It can be inferred from the fitting relation given in Equation 31 of \cite{2019MNRAS.486.5377I}:
+\begin{equation}\label{inayoshi_accretion}
+    \frac{\dot{M}_{\bullet}}{\dot{M}_{Edd}} \simeq 1.5\times10^{-6}T_7^{-4/5}\times\left(\frac{\alpha}{0.01}\right)^{0.37}\left(\frac{\dot{m}_B}{10^{-3}}\right)^{3/5}\left(\frac{f_c}{0.1}\right)^{2/5},
+\end{equation}
+where $\dot{M}_{\bullet}$ is the net accretion to the black hole, $T_7$ is the temperature of the ambient gas in units of $10^7\;K$, $\alpha$ is the strength of viscosity (generally accepted to be 0.01; see \citet{1973A&A....24..337S}, \citet{1991ApJ...376..214B}, \citet{1995ApJ...445..767M}, \citet{1996ApJ...463..656S}, \citet{1998RvMP...70....1B}, \citet{2004PThPS.155..409S}, \cite{2018MNRAS.476.1412I}), and $f_c$ is the conductivity suppression factor (generally accepted to be 0.1; see \citet{2001ApJ...562L.129N}, \citet{2004PhRvL..92d5001M}, and \cite{2019MNRAS.486.5377I}).
+The Eddington accretion rate, $\dot{M}_{Edd}$, is calculated from the Eddington luminosity, $L_{Edd}$, as follows:
+\begin{subequations}
+    \begin{equation}\label{edd_lum}
+        L_{Edd} = 1.26\times10^{38}\left(\frac{M_{BH}}{M_{\odot}}\right)\;\text{erg}\;\text{s}^{-1}
+    \end{equation}
+    \begin{equation}\label{edd_acc}
+        \dot{M}_{Edd} = \frac{L_{Edd}}{0.1c^2} \text{  g} \text{ s}^{-1},
+    \end{equation}
+\end{subequations}
+where $c$ is the speed of light.  Finally, we can define $\dot{m}_{B}$ in Equation \ref{inayoshi_accretion} as  $\dot{m}_{B} = \dot{M}_{B}/\dot{M}_{Edd}$.
+
+Given the above, we estimate the bolometric luminosity of the black holes as $L_{Bol} = \epsilon\dot{M}_{\bullet}c^2$, where $\epsilon$ is the radiative efficiency (cf.
+Equation 13 in \citet{2019MNRAS.486.5377I}).
+For sources having $\dot{M}_B/\dot{M}_{Edd} > 10^{-3}$, we take $L_x=0.1L_{Bol}$, due to the higher net accretion onto the black hole as a result of cooling of the accretion disc and hence higher gas density.
+For those having $\dot{M}_B/\dot{M}_{Edd} < 10^{-3}$, we take $L_x=L_{Bol}$.
+
+\begin{comment}
 The resulting net black hole mass accretion rate is approximated by \citet{1944MNRAS.104..273B} and \citet{1952MNRAS.112..195B}:
@@
 \end{equation}
+\end{comment}
 
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{plots/"luminosities_final".png}
+\includegraphics[width=0.5\textwidth]{plots/"luminosities_final_final".png}
 \caption{Approximation to Figure 12 from \citealt{2019MNRAS.486.5377I}. Black "o"s represent black holes in this study.  We also include observational results for Sgr A*, and BHs in M31 and M87.}

### 2020-03-30 paper.tex
Final edits from  Taeho's second set of suggestions.

@@
 % These dates will be filled out by the publisher
-\date{Last updated 2020 Jan 27; in original form 2020 Jan 27}
+\date{Last updated \today; in original form \today}
 
@@
 But how common are encounters of massive black holes?
-For galaxies, we know that minor mergers are frequent from the observed evolution of the size and mass of these systems \citep{2010ApJ...718L..73V, 2008ApJ...677L...5V, 2019MNRAS.484..595M}.
+For massive galaxies, we know that minor mergers are frequent from the observed evolution of the size and mass of these systems \citep{2010ApJ...718L..73V, 2008ApJ...677L...5V, 2019MNRAS.484..595M}.
 However, if we assume that all galaxy mergers lead to SMBH mergers we end up overpredicting the  gravitational wave background, as constrained by observations from pulsar timing arrays (PTAs, see \citealt{2008MNRAS.390..192S, 2009MNRAS.394.2255S, 2013MNRAS.433L...1S, 2014ApJ...789..156M, 2015ApJ...799..178K, 2016APS..APRR18003T, 2018ApJ...856...42S, 2018MNRAS.479.4017I, 2018ApJ...863L..36I, 2018NatCo...9..573M}).
@@
 
-\citet{2015ApJ...799..178K} furthered the merger tree data produced by \citet{2012MNRAS.425..641L} by estimating the evolution of the SMBH population, based on assumptions about the relationship between the properties of SMBHs and those of their host galaxies.
+\citet{2015ApJ...799..178K} furthered the merger tree data produced by \citet{2012MNRAS.425..641L} by estimating the evolution of the SMBH population.
+They assume growth of SMBHs to be proportional to that of the bulge stellar mass of the galaxies.
+They further assume a constant relation between bulge and total stellar mass at all redshifts, although some observations suggest that the bulge mass fraction for a fixed stellar mass should increase with decreasing redshift (\citet{2012MNRAS.423.1992S}, \citet{2013MNRAS.428.1351G}, \citet{2014MNRAS.441..417A}), with the result that their SMBHs grow faster at high redshift than would be expected in reality.
 
@@
 \begin{itemize}
-    \item Galactic properties - Each galaxy was distinguished by an id number, with properties such as stellar mass, dark matter (DM) mass, central black hole id number, and orbiting black hole id numbers, recorded at 37 redshift slices between $4 > z > 0$.
+    \item Galactic properties - Each galaxy was distinguished by an id number, with properties such as stellar mass, dark matter (DM) mass, central black hole id number, and orbiting black hole id numbers, recorded at 37 redshift slices between $4\geq z \geq0$.
     \item Black Hole properties - Each black hole was also distinguished by an id number, with properties such as seed mass, accreted mass, its host galaxy id number, and time after $z=4$ at which the black hole entered its host galaxy, if it was not the central black hole.
@@
 In this case, a doubling of $M_*$ would increase $\sigma(R_e)$ by a factor of 1.15.
-These variations have direct effects on the ability of the orbiting black holes to merge with the central black hole, and thus can affect our merger statistics and resulting characteristic strain calculations, and therefore it is important to estimate our stellar masses with reasonable accuracy.
+These variations have direct effects on the ability of the orbiting black holes to merge with the central black hole, and thus can affect our merger statistics.
+Therefore, it is important to estimate our stellar masses with reasonable accuracy.
 
@@
 
-We also compared the stellar masses from \citet{2012MNRAS.425..641L} to  observational and abundance matching data from \citet{2018AstL...44....8K}.
-Figure \ref{fig:stellar1} is a partial, approximate, replication of their Figure 11 (abundance matching line).
-We rescaled our stellar masses at $z=0$ in a lognormal manner about the line in order to match the observed data.
+Given the overestimate of stellar mass in the merger tree data, we rescaled our stellar masses in order to match the observational and abundance matching data from \citet{2018AstL...44....8K}.
+In their study, they estimated star formation efficiency and the stellar mass-halo mass relation in massive haloes.
+They obtained their data from two sources: a study of nine nearby clusters ($z<0.1$) using Chandra X-ray observations \citep{2009ApJ...692.1033V}, and one of 12 cluters from \citet{2013ApJ...778...14G}.
+
+Figure \ref{fig:stellar1} is a partial, approximate, replication of Figure 11 from \citet{2018AstL...44....8K} (abundance matching line).
+We rescaled our stellar masses at $z=0$ by using a lognormal distribution.
+For a given galaxy's dark matter mass, the mean of the distribution, $\mu$, was taken to be the point on the abundance matching line at that dark matter mass.
+The standard deviation was assumed arbitrarily to be $0.3\mu$.
 Table \ref{table:gal_char} shows the original and rescaled stellar masses.
@@
 $f_\mathrm{bary}$ is the universal baryon fraction as a function of total halo mass.
-Purple dots shown are examples of our rescaled stellar masses}
+Purple dots shown are examples of our rescaled stellar masses.
+We rescaled our stellar masses at $z=0$ by using a lognormal distribution.
+For a given galaxy's dark matter mass, the mean of the distribution was taken to be the point on the abundance matching line at that dark matter mass.
+The standard deviation of that mean was taken arbitrarily to be 0.3.}
 \label{fig:stellar1}
@@
 We can then equate the value for $\sigma({R_e})$ obtained from Equation \ref{sig} to the analytic expressions for $\sigma$ in the Stone-Ostriker profile (cf.
-Equations 9 and A1-A4).
+Equations 9 and A1-A4 in \cite{2015ApJ...806L..28S}).
 The only unknown is $r_h$, which we can solve for using a simple recursive Newton method.
@@
 The large fraction of orbiting black holes predicted by our simulations motivates a back-of-the-envelope calculation to see if orbiting black holes produce detectable signatures.
-In the following section, we estimate the X-ray luminosities of gas accreted by these BHs while orbiting through their host galaxies.
+In the following section, we estimate the X-ray thermal luminosities due to gas accreted by these BHs while orbiting through their host galaxies.
 
@@
 This results in $\mu=0.606$.
-The resulting X-ray luminosities are shown in Figures \ref{fig:galgas1} and compared against a sample from \citet{2018ApJ...857...32B}.
+The resulting X-ray thermal luminosities are shown in Figures \ref{fig:galgas1} and compared against a sample from \citet{2018ApJ...857...32B}.
 
@@
 However, due to the low density of the gas, it does not cool, and convection limits the net accretion, and subsequent radiation luminosity, of the black hole.
+In such a convective infall, the gas finally accreted onto the black hole is much less than the initially infalling gravitationally bound gas.
 
@@
 \begin{equation}
-    \sigma^2 = \frac{6GM_{tot}(\frac{\pi^2}{8}-1)}{{\pi}r_h},
+    \sigma_c^2 = \frac{6GM_{tot}(\frac{\pi^2}{8}-1)}{{\pi}r_h},
 \end{equation}
@@
 The gas sound speed (see Equation \eqref{gas_sound_speed} below) has a $C_s{\propto}T_x^{0.5}$ dependence on temperature.
-However, given the dependence of the accretion rate (see Equation \eqref{net_accretion} below) on gas sound speed of $\dot{M}_{acc}{\propto}C_s^3$, the accretion rate is dependent on temperature to the order of $T_x^{3/2}$.
+However, given the dependence of the accretion rate (see Equation \eqref{net_accretion} below) on gas sound speed of $\dot{M}_{acc}{\propto}C_s^{-3}$, the accretion rate is dependent on temperature to the order of $T_x^{-3/2}$.
 This is another source of variation in our estimate of accretion rate.
@@
 Purple X's represent central gas densities of the galaxies in this study.
-Fit in log space is $\rho_0 = 10^{0.6*\log\left(\frac{\sigma_c}{g\ cm^{-3}}\right) - 25} \text{  g cm}^{-3}$.}
+Fit in log space is $\rho_0 = 10^{0.6*\log\left(\frac{\sigma_c}{km\ s^{-1}}\right) - 25} \text{  g cm}^{-3}$.}
 \label{fig:rho0_vs_sigma}
@@
 Purple X's represent temperatures of the galaxies in this study.
-Fit in log space is $T_x = 10^{2.50*\log\left(\frac{\sigma_c}{g\ cm^{-3}}\right) - 6.06} \text{  keV}$.}
+Fit in log space is $T_x = 10^{2.50*\log\left(\frac{\sigma_c}{km\ s^{-1}}\right) - 6.06} \text{  keV}$.}
 \label{fig:Tx_vs_sigma}
@@
 where $\rho_0$ is as defined above, r is the black hole's distance from the center of the galaxy, and $r_c$ is the core radius.
+Since the orbiting black hole masses are $10^{-5}-10^{-2}M_{tot}$, we assume there is no change in $M_{tot}$ after black holes are ejected.
 
@@
 \subsubsection{Black Hole Mass Accretion and Luminosity}
-In theory, the black hole mass accretion rate is governed by the Bondi-Hoyle formula (\citet{1944MNRAS.104..273B} and \citet{1952MNRAS.112..195B}):
+At large distances, the black hole mass accretion rate is governed by the Bondi-Hoyle formula (\citet{1944MNRAS.104..273B} and \citet{1952MNRAS.112..195B}):
 \begin{equation}\label{net_accretion}
-    \dot{M}_{B} = f\frac{4{\pi}G^2M_\mathrm{BH}^2\rho}{(C_s^2+v^2)^{3/2}} \text{  g}\text{ s}^{-1},
+    \dot{M}_{B} = \frac{4{\pi}G^2M_\mathrm{BH}^2\rho}{(C_s^2+v^2)^{3/2}} \text{  g}\text{ s}^{-1},
 \end{equation}
@@
 It can be inferred from the fitting relation given in Equation 31 of \cite{2019MNRAS.486.5377I}:
+\begin{subequations}
     \begin{equation}\label{inayoshi_accretion}
@@
     \end{equation}
-where $\dot{M}_{\bullet}$ is the net accretion to the black hole, $T_7$ is the temperature of the ambient gas in units of $10^7\;K$, $\alpha$ is the strength of viscosity (generally accepted to be 0.01; see \citet{1973A&A....24..337S}, \citet{1991ApJ...376..214B}, \citet{1995ApJ...445..767M}, \citet{1996ApJ...463..656S}, \citet{1998RvMP...70....1B}, \citet{2004PThPS.155..409S}, \cite{2018MNRAS.476.1412I}), and $f_c$ is the conductivity suppression factor (generally accepted to be 0.1; see \citet{2001ApJ...562L.129N}, \citet{2004PhRvL..92d5001M}, and \cite{2019MNRAS.486.5377I}).
-The Eddington accretion rate, $\dot{M}_{Edd}$, is calculated from the Eddington luminosity, $L_{Edd}$, as follows:
-\begin{subequations}
-    \begin{equation}\label{edd_lum}
-        L_{Edd} = 1.26\times10^{38}\left(\frac{M_{BH}}{M_{\odot}}\right)\;\text{erg}\;\text{s}^{-1}
+    \begin{equation}\label{mdotb}
+        \dot{m}_{B} = \dot{M}_{B}/\dot{M}_{Edd},
     \end{equation}
@@
     \end{equation}
+    \begin{equation}\label{edd_lum}
+        L_{Edd} = 1.26\times10^{38}\left(\frac{M_{BH}}{M_{\odot}}\right)\;\text{erg}\;\text{s}^{-1}.
+    \end{equation}
 \end{subequations}
-where $c$ is the speed of light.  Finally, we can define $\dot{m}_{B}$ in Equation \ref{inayoshi_accretion} as  $\dot{m}_{B} = \dot{M}_{B}/\dot{M}_{Edd}$.
+$\dot{M}_{\bullet}$ is the net accretion to the black hole, $T_7$ is the temperature of the ambient gas in units of $10^7\;K$, $\alpha$ is the strength of viscosity (generally accepted to be 0.01; see \citet{1973A&A....24..337S}, \citet{1991ApJ...376..214B}, \citet{1995ApJ...445..767M}, \citet{1996ApJ...463..656S}, \citet{1998RvMP...70....1B}, \citet{2004PThPS.155..409S}, \cite{2018MNRAS.476.1412I}), and $f_c$ is the conductivity suppression factor (generally accepted to be 0.1; see \citet{2001ApJ...562L.129N}, \citet{2004PhRvL..92d5001M}, and \cite{2019MNRAS.486.5377I}).
+The Eddington accretion rate is $\dot{M}_{Edd}$, $c$ is the speed of light, and $L_{Edd}$ is the Eddington luminosity.
 
-Given the above, we estimate the bolometric luminosity of the black holes as $L_{Bol} = \epsilon\dot{M}_{\bullet}c^2$, where $\epsilon$ is the radiative efficiency (cf.
+Given the above, we estimate the bolometric luminosity of the black holes as:
+\begin{subequations}
+    \begin{equation}\label{bol_lum}
+        L_{Bol} = \epsilon\dot{M}_{\bullet}c^2,
+    \end{equation}
+    \begin{equation}\label{rad_eff}
+        \begin{split}
+        \text{log}\;\epsilon = \begin{cases}
+                        -1.0-(0.0162/\dot{m})^{4}\;\;\text{for 0.023}\;\leq\;\dot{m}, \\
+                        \sum_{n}{}a_{n}(log\;\dot{m})^{n}\;\;\;\;\;\;\;\;\;\text{for}\;10^{-4} <\;\dot{m}\;<\;0.023, \\
+                        \sum_{n}{}b_{n}(log\;\dot{m})^{n}\;\;\;\;\;\;\;\;\;\text{for}\;10^{-8} <\;\dot{m}\;\leq\;10^{-4},
+                               \end{cases}
+        \end{split}
+    \end{equation}
+\end{subequations}
+where $\dot{m}=\dot{M_{\bullet}}/\dot{M}_{Edd}$, and $\epsilon$ is the radiative efficiency (cf.
 Equation 13 in \citet{2019MNRAS.486.5377I}).
+The fitted values are $a_0=-0.807$, $a_1=0.27$, $a_n=0$ ($n\geq2$), $b_0=-1.749$, $b_1=-0.267$, $b_2=-0.07492$, and $b_n=0$ ($n\geq3$).
+
 For sources having $\dot{M}_B/\dot{M}_{Edd} > 10^{-3}$, we take $L_x=0.1L_{Bol}$, due to the higher net accretion onto the black hole as a result of cooling of the accretion disc and hence higher gas density.
@@
 
-\begin{comment}
-The resulting net black hole mass accretion rate is approximated by \citet{1944MNRAS.104..273B} and \citet{1952MNRAS.112..195B}:
-\begin{equation}\label{net_accretion}
-    \dot{M}_{acc} = f\frac{4{\pi}G^2M_\mathrm{BH}^2\rho}{(C_s^2+v^2)^{3/2}} \text{  M}_\odot \text{ Myr}^{-1},
-\end{equation}
-where the additional factor $f$ (see \cite{2018MNRAS.476.1412I} and \cite{2019MNRAS.486.5377I}) gives the decline in accretion, interior to the BH radius due to convective (i.e., inefficient) accretion, as calculated in \citet{2019MNRAS.486.5377I}, cf.
-eq 13.
-Additionally, $M_{BH}$ is the black hole mass, $G$ is the gravitational constant, and $v$ is the black hole velocity.
-
-Finally, the black hole X-ray luminosity is estimated from:
-\begin{equation}
-    L_x = \epsilon_{rx}\dot{M}_{acc}c^2 \text{  erg s}^{-1},
-\end{equation}
-where the X-ray radiative efficiency ${\epsilon}_{rx}=0.01$ , and we are assuming for the low-luminosity sources that $L_x{\sim}L_{Bol}$.
-For sources having $\dot{M}_B/\dot{M}_{Edd} > 10^{-3}$, we take $L_x=0.1L_{Bol}$, due to the higher net accretion onto the black hole as a result of cooling of the accretion disc and hence higher gas density.
-The corresponding Eddington limit is defined as:
-\begin{equation}
-    L_{edd} = 1.26 \times 10^{38} (M/M_{\odot}) \text{  erg s}^{-1}.
-\end{equation}
-\end{comment}
-
 \subsubsection{Central Black Hole Influence}
 Within the influence radius of the central black hole, which is defined as the radius at which the total mass of the galaxy within that radius (stars + dark matter) equals the mass of the central black hole, the gas density is much higher than otherwise, and equation \eqref{beta_model} cannot be used in the region where the BH Kepler potential dominates.
-Starting with the equation for hydrostatic equilibrium, assuming isothermality,
-\begin{equation}
-    C_{s}^2\frac{dln\rho}{dr}= -\frac{GM(r)}{r^2},
+We start with the equation for hydrostatic equilibrium, assuming isothermality,
+\begin{equation} \label{sound_speed}
+    C_{s}^2\frac{dln\rho}{dr}= -\frac{GM(r)}{r^2}.
 \end{equation}
-we can integrate with respect to r, leading to 
+Inside the sphere of influence, $M(r)$ is constant, and we can integrate Equation \eqref{sound_speed} with respect to r, leading to 
 \begin{equation}
@@
 
-Figure \ref{fig:ldobhs} represents a histogram of the final X-ray luminosities of the black holes, overlaid by a lognormal distribution.  
+Figure \ref{fig:ldobhs} represents a histogram of the final X-ray luminosities of the black holes, overlaid by a lognormal distribution, obtained with a mean $\mu=1.0\times10^{33}$ and standard deviation $\sigma=4.5\times10^{3}$.
 \begin{figure}
@@
 Green region under curve represents approximate range of detectable orbiting black holes.
-The dashed, red vertical line is the median X-ray luminosity of our sources.}
+The dashed, red vertical line is the median X-ray luminosity of our sources ($1.0\times10^{33}\;\text{erg}\;\text{s}^{-1}$).}
 \label{fig:ldobhs}

### 2020-04-04 paper.tex
FINAL EDITS BETWEEN ME AND JERRY BEFORE SENDING TO ANDREAS FOR HIS FINAL EDITS OR APPROVAL.

@@
 \includegraphics[width=0.5\textwidth]{plots/"Lx of our Galaxies compared to Babyk data".png}
-\caption{X-ray luminosity of hot gas in our galaxies, compared to those from \citet{2018ApJ...857...32B}.}
+\caption{X-ray thermal luminosity of hot gas in our galaxies, compared to those from \citet{2018ApJ...857...32B}.}
 \label{fig:galgas1}
@@
 
-\subsection{Galaxy Gas X-Ray Luminosity}
-First, we construct realistic X-ray luminosities for our host galaxies.
-We compute the X-ray luminosity of the hot gas in these galaxies, adapting Equation 26 from \citet{2012ApJ...754..125C}.
+\subsection{Galaxy Gas X-Ray Thermal Luminosity}
+First, we construct realistic X-ray thermal luminosities for our host galaxies.
+We compute the X-ray thermal luminosity of the hot gas in these galaxies, adapting Equation 26 from \citet{2012ApJ...754..125C}.
 In lieu of summing over discrete particles, we use the beta model of the gas as defined in our equation \ref{beta_model} and integrate:
@@
 
-\subsection{Black Hole X-Ray Luminosity}
+\subsection{Black Hole X-Ray Thermal Luminosity}
 \subsubsection{Assumptions and Method Employed}
@@
     \begin{equation}\label{mdotb}
-        \dot{m}_{B} = \dot{M}_{B}/\dot{M}_{Edd},
+        \dot{m}_{B} \equiv \dot{M}_{B}/\dot{M}_{Edd},
     \end{equation}
     \begin{equation}\label{edd_acc}
-        \dot{M}_{Edd} = \frac{L_{Edd}}{0.1c^2} \text{  g} \text{ s}^{-1},
+        \dot{M}_{Edd} \equiv \frac{L_{Edd}}{0.1c^2} \text{  g} \text{ s}^{-1},
     \end{equation}
     \begin{equation}\label{edd_lum}
-        L_{Edd} = 1.26\times10^{38}\left(\frac{M_{BH}}{M_{\odot}}\right)\;\text{erg}\;\text{s}^{-1}.
+        L_{Edd} \equiv 1.26\times10^{38}\left(\frac{M_{BH}}{M_{\odot}}\right)\;\text{erg}\;\text{s}^{-1}.
     \end{equation}
@@
 \includegraphics[width=0.5\textwidth]{plots/"Comparison of L_x versus radius with and without BH Influence".png}
-\caption{Difference in X-ray luminosity of wandering black holes within the influence radius of the central black hole.
+\caption{Difference in X-ray thermal luminosity of wandering black holes within the influence radius of the central black hole.
 For each vertical line, red (lower) dots are the originally calculated luminosity, not taking the CBH influence into account.
@@
 \includegraphics[width=0.5\textwidth]{plots/"Final Luminosities using Kohei factor".png}
-\caption{X-ray Luminosity Distribution of Orbiting BHs at z=0.
+\caption{X-ray Thermal Luminosity Distribution of Orbiting BHs at z=0.
 Green region under curve represents approximate range of detectable orbiting black holes.
-The dashed, red vertical line is the median X-ray luminosity of our sources ($1.0\times10^{33}\;\text{erg}\;\text{s}^{-1}$).}
+The dashed, red vertical line is the median X-ray thermal luminosity of our sources ($1.0\times10^{33}\;\text{erg}\;\text{s}^{-1}$).}
 \label{fig:ldobhs}
@@
 The median luminosity of $10^{33}\mathrm{erg}~\mathrm{s}^{-1}$ would be undetectable with present instruments, although the top $5\%$ most luminous from this set could be detectable.
+If detected, these orbiting massive black holes would constitute a new category of X-ray source.
 

### 2020-04-04 paper.tex
One last tiny edit before sending to Andreas.

@@
 \subsubsection{Phase-space diffusion} \label{psd}
-Much of this subsection was borrowed from \citet{2017MNRAS.467.4180S}, Section E1, which made use the same modified version of \textsc{AR-Chain}.
+Much of this subsection was borrowed from \citet{2017MNRAS.467.4180S}, Section E1, which made use of the same modified version of \textsc{AR-Chain}.
 

### 2020-04-13 paper.tex
Final edits from Andreas, and last-minute formatting prior to submitting.

@@
 % (version numbers match those of mnras.cls)
-%
 % Copyright (C) Royal Astronomical Society 2015
@@
 
+%
 % Change log
@@
 \section{Methods}\label{sec:methods}
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_1.png}
-%\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_65.png}\\
-%\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_187.png}
-%\includegraphics[width=0.45\textwidth]{plots/Masses_plot_galaxy_217.png}\\
-%\caption{default}
-%\label{default1}
-%\end{center}
-%\end{figure*}
 
@@
 They assume growth of SMBHs to be proportional to that of the bulge stellar mass of the galaxies.
-They further assume a constant relation between bulge and total stellar mass at all redshifts, although some observations suggest that the bulge mass fraction for a fixed stellar mass should increase with decreasing redshift (\citet{2012MNRAS.423.1992S}, \citet{2013MNRAS.428.1351G}, \citet{2014MNRAS.441..417A}), with the result that their SMBHs grow faster at high redshift than would be expected in reality.
+They further assume a constant relation between bulge and total stellar mass at all redshifts, although some observations suggest that the bulge mass fraction for a fixed stellar mass should increase with decreasing redshift (\citealt{2012MNRAS.423.1992S, 2013MNRAS.428.1351G, 2014MNRAS.441..417A}), with the result that their SMBHs grow faster at high redshift than would be expected in reality.
 
@@
 %\begin{center}
-\includegraphics[width=0.5\textwidth]{plots/stellar_to_halo_ratio.png}
+\includegraphics[width=1.0\columnwidth]{plots/stellar_to_halo_ratio.png}
 \caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.
@@
 
-The central density, $\rho_c$, can be found from inverting Equation 5 in Stone and Ostriker 2015 for the galaxy's total mass:
+The central density, $\rho_c$, can be found from inverting Equation 5 in  \citet{2015ApJ...806L..28S} for the galaxy's total mass:
 
@@
 In order to parameterize $r_c$ and $r_h$, we can utilize the relationship between the distribution of light and stellar velocity dispersion at the effective radius, and the shape of the dark matter profile.
-The effective radius $R_{e}$ and velocity dispersion at the effective radius $\sigma(R_e)$, respectively, can be obtained from (\citet{2009ApJ...706L..86N}, \citet{2010ApJ...725.2312O}, \citet{2014ApJ...789..156M}):
+The effective radius $R_{e}$ and velocity dispersion at the effective radius $\sigma(R_e)$, respectively, can be obtained from (\citealt{2009ApJ...706L..86N, 2010ApJ...725.2312O, 2014ApJ...789..156M}):
 
@@
 \begin{equation} \label{sig}
-\sigma(R_{e}) = 190\mathrm{km}\;\mathrm{s}^{-1}\left(\frac{M_{*}}{10^{11}M_{\odot}}\right)^{0.2}(1+z)^{0.47},
+\sigma(R_{e}) = 190\mathrm{km}\;\mathrm{s}^{-1}\left(\frac{M_{*}}{10^{11}M_{\odot}}\right)^{0.2}(1+z)^{0.47}.
 \end{equation}
@@
 We can then equate the value for $\sigma({R_e})$ obtained from Equation \ref{sig} to the analytic expressions for $\sigma$ in the Stone-Ostriker profile (cf.
-Equations 9 and A1-A4 in \cite{2015ApJ...806L..28S}).
+Equations 9 and A1-A4 in \citealt{2015ApJ...806L..28S}).
 The only unknown is $r_h$, which we can solve for using a simple recursive Newton method.
-Whether $\sigma_{near}$ or $\sigma_{far}$ is used from Stone-Ostriker is determined by whether $R_e$ is less than or greater than $\sqrt{r_c r_h}$.
+Whether $\sigma_{near}$ or $\sigma_{far}$ is used from \cite{2015ApJ...806L..28S} is determined by whether $R_e$ is less than or greater than $\sqrt{r_c r_h}$.
 
@@
 The core radius, $r_c$, is recalculated only if an orbiting black hole enters within $r_c$.
-The work done by diffusion, as described in Section \ref{psd} is calculated, the total potential energy and dynamical friction are updated, and $r_c$ is solved for from Equation 8 in Stone-Ostriker based on conservation of energy.
+The work done by diffusion, as described in Section \ref{psd} is calculated, the total potential energy and dynamical friction are updated, and $r_c$ is solved for from Equation 8 in \citet{2015ApJ...806L..28S} based on conservation of energy.
 
@@
 We include gravitational wave recoils following the prescription outlined in \citet{2015ApJ...799..178K}, which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.
-We assume that a merger will be inevitable when the separation between two SMBHs becomes smaller than the Schwarzschild radius.
-At the moment of the merger, we also assume that the spin vectors of the two SBHs are randomly aligned.
+We assume that a merger will be inevitable when the separation between two SMBHs becomes smaller than four times the Schwarzschild radius of the more massive black hole.
+At the moment of the merger, we also assume that the spin vectors of the two SMBHs are randomly aligned.
 
@@
 Black holes can also eject each other via strong three-body interactions.
-We remove SBHs from the simulations once they move beyond $r_h$, assuming that it will take them more than a Hubble time to find their way back into the center of the host galaxy, or that they have achieved escape velocity.
+We remove SMBHs from the simulations once they move beyond $r_h$, assuming that it will take them more than a Hubble time to find their way back into the center of the host galaxy, or that they have achieved escape velocity.
 
@@
 The orbiting black holes were injected into their host galaxy at redshift $z$, at a distance from the galactic center of $R_{e}$ (Equation \ref{re}) following galaxy mergers.
-Their initial velocity was arbitrarily chosen to be circular, $v_c = \sqrt{GM(R_e)/R_e}$, with $v_x$, $v_y$, and $v_z$ randomly chosen.
+Their initial velocity was arbitrarily chosen to be the circular velocity at that radius, $v_c = \sqrt{GM(R_e)/R_e}$, with orientation, $v_x$, $v_y$, and $v_z$, randomly chosen.
 
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{plots/"Summary Results All Galaxies".png}
+\includegraphics[width=1.0\columnwidth]{plots/"Summary Results All Galaxies".png}
 \caption{Histogram of merged, ejected, and orbiting SMBHs at z=0 as a function of BH mass.
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{plots/q_merger_fraction.png}
+\includegraphics[width=1.0\columnwidth]{plots/q_merger_fraction.png}
 \caption{Fraction of BHs that merge with the central BH as a function of the BH mass ratio.
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{plots/time_to_merge.png}
+\includegraphics[width=1.0\columnwidth]{plots/time_to_merge.png}
 \caption{Time required for BHs to merge with host SMBH after galaxy merger.  Form for fitted line is $-0.379M_{BH}+5.766$ in log-log space.}
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{plots/kicked_stats.png}
+\includegraphics[width=1.0\columnwidth]{plots/kicked_stats.png}
 \caption{Histogram of kicked and not-kicked SMBHs at z=0.  Colored arrows along upper x-axis represent median masses of respective sets.  Histograms are stacked.}
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{plots/"Final Radius v Mass of Orbiting BHs".png}
-\caption{Final Radii of remaining orbital black holes at z=0.
+\includegraphics[width=1.0\columnwidth]{plots/"Final Radius v Mass of Orbiting BHs".png}
+\caption{Final radii of remaining orbital black holes at z=0.
 Kicked black holes generally had a low likelihood of finding their way back to the center by z=0.
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{plots/"Lx of our Galaxies compared to Babyk data".png}
+\includegraphics[width=1.0\columnwidth]{plots/"Lx of our Galaxies compared to Babyk data".png}
 \caption{X-ray thermal luminosity of hot gas in our galaxies, compared to those from \citet{2018ApJ...857...32B}.}
@@
 \section{Signatures of Orbiting Black Holes}
-The large fraction of orbiting black holes predicted by our simulations motivates a back-of-the-envelope calculation to see if orbiting black holes produce detectable signatures.
+The large fraction of orbiting black holes found in our simulations motivates a back-of-the-envelope calculation to see if orbiting black holes produce detectable signatures.
 In the following section, we estimate the X-ray thermal luminosities due to gas accreted by these BHs while orbiting through their host galaxies.
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{plots/"rho_0 vs sigma with errors".png}
+\includegraphics[width=1.0\columnwidth]{plots/"rho_0 vs sigma with errors".png}
 \caption{Central gas density versus central velocity dispersion.
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{plots/"Tx vs sigma with errors".png}
+\includegraphics[width=1.0\columnwidth]{plots/"Tx vs sigma with errors".png}
 \caption{X-ray temperature versus central velocity dispersion.
@@
 \subsubsection{Black Hole Mass Accretion and Luminosity}
-At large distances, the black hole mass accretion rate is governed by the Bondi-Hoyle formula (\citet{1944MNRAS.104..273B} and \citet{1952MNRAS.112..195B}):
+At large distances, the black hole mass accretion rate is governed by the Bondi-Hoyle formula (\citealt{1944MNRAS.104..273B} and \citealt{1952MNRAS.112..195B}):
 \begin{equation}\label{net_accretion}
@@
 
-However, due to convective (i.e., inefficient) accretion interior to the Bondi radius (see \cite{2018MNRAS.476.1412I} and \cite{2019MNRAS.486.5377I}), the net accretion to the black hole is often substantially lower than the Bondi-Hoyle accretion.
-It can be inferred from the fitting relation given in Equation 31 of \cite{2019MNRAS.486.5377I}:
+However, due to convective (i.e., inefficient) accretion interior to the Bondi radius (see \citealt{2018MNRAS.476.1412I} and \citealt{2019MNRAS.486.5377I}), the net accretion to the black hole is often substantially lower than the Bondi-Hoyle accretion.
+It can be inferred from the fitting relation given in equation 31 of \cite{2019MNRAS.486.5377I}:
 \begin{subequations}
@@
 \end{subequations}
-$\dot{M}_{\bullet}$ is the net accretion to the black hole, $T_7$ is the temperature of the ambient gas in units of $10^7\;K$, $\alpha$ is the strength of viscosity (generally accepted to be 0.01; see \citet{1973A&A....24..337S}, \citet{1991ApJ...376..214B}, \citet{1995ApJ...445..767M}, \citet{1996ApJ...463..656S}, \citet{1998RvMP...70....1B}, \citet{2004PThPS.155..409S}, \cite{2018MNRAS.476.1412I}), and $f_c$ is the conductivity suppression factor (generally accepted to be 0.1; see \citet{2001ApJ...562L.129N}, \citet{2004PhRvL..92d5001M}, and \cite{2019MNRAS.486.5377I}).
+$\dot{M}_{\bullet}$ is the net accretion to the black hole, $T_7$ is the temperature of the ambient gas in units of $10^7\;K$, $\alpha$ is the strength of viscosity (generally accepted to be 0.01; see \citealt{1973A&A....24..337S, 1991ApJ...376..214B, 1995ApJ...445..767M, 1996ApJ...463..656S, 1998RvMP...70....1B, 2004PThPS.155..409S, 2018MNRAS.476.1412I}), and $f_c$ is the conductivity suppression factor (generally accepted to be 0.1; see \citealt{2001ApJ...562L.129N, 2004PhRvL..92d5001M}, and \citealt{2019MNRAS.486.5377I}).
 The Eddington accretion rate is $\dot{M}_{Edd}$, $c$ is the speed of light, and $L_{Edd}$ is the Eddington luminosity.
@@
 where $\dot{m}=\dot{M_{\bullet}}/\dot{M}_{Edd}$, and $\epsilon$ is the radiative efficiency (cf.
-Equation 13 in \citet{2019MNRAS.486.5377I}).
+Equation 13 in \citealt{2019MNRAS.486.5377I}).
 The fitted values are $a_0=-0.807$, $a_1=0.27$, $a_n=0$ ($n\geq2$), $b_0=-1.749$, $b_1=-0.267$, $b_2=-0.07492$, and $b_n=0$ ($n\geq3$).
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{plots/"Comparison of L_x versus radius with and without BH Influence".png}
+\includegraphics[width=1.0\columnwidth]{plots/"Comparison of L_x versus radius with and without BH Influence".png}
 \caption{Difference in X-ray thermal luminosity of wandering black holes within the influence radius of the central black hole.
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{plots/"luminosities_final_final".png}
+\includegraphics[width=1.0\columnwidth]{plots/"luminosities_final_final".png}
 \caption{Approximation to Figure 12 from \citealt{2019MNRAS.486.5377I}. Black "o"s represent black holes in this study.  We also include observational results for Sgr A*, and BHs in M31 and M87.}
@@
 
-Figure \ref{fig:ldobhs} represents a histogram of the final X-ray luminosities of the black holes, overlaid by a lognormal distribution, obtained with a mean $\mu=1.0\times10^{33}$ and standard deviation $\sigma=4.5\times10^{3}$.
+Figure \ref{fig:ldobhs} represents a histogram of the final X-ray luminosities of the black holes, overlaid by a lognormal distribution, obtained with a mean $\mu=1.0\times10^{33}\,\text{erg s}^{-1}$ and standard deviation $\sigma=4.5\times10^{3}\,\text{erg s}^{-1}$.
 \begin{figure}
 \begin{center}
-\includegraphics[width=0.5\textwidth]{plots/"Final Luminosities using Kohei factor".png}
-\caption{X-ray Thermal Luminosity Distribution of Orbiting BHs at z=0.
+\includegraphics[width=1.0\columnwidth]{plots/"Final Luminosities using Kohei factor".png}
+\caption{X-ray thermal luminosity distribution of orbiting BHs at z=0.
 Green region under curve represents approximate range of detectable orbiting black holes.
@@
 \section{Acknowledgements}
-The authors would like to thank Andrea Kulier and Claire Lackner for providing merger tree data.
+The authors would like to thank Andrea Kulier and Claire Lackner for providing merger tree data, and Seppo Mikkola for making his \textsc{AR-Chain} code available.
 We also thank Renyue Cen, Pieter van Dokkum, Charles Hailey, Zoltan Haiman, Kohei Inayoshi, Sean McWilliams, Taeho Ryu and Nick Stone for useful discussions and insights.

### 2020-07-26 paper.tex
Last commit prior to making changes requested by Referree

@@
 
-The above criteria narrowed the field of eligible galaxies down to 51.
+\textbf{The vast majority of the full set of galaxies (1,537) were eliminated because they did not come into existence until after $z=4$.
+Of the remaining 293 galaxies, 67 of them existed at z=0, and 51 of them also had black holes orbiting at z=0}.
 In considering time and resources, we chose the 11 galaxies that had the largest number black holes to run the simulations.
@@
 \subsection{Simulation setup}\label{subsec:simset}
-For each galaxy in the simulations, we only used black holes that would theoretically have merged with the center of the host galaxy within a dynamical friction time, $t_{fric}$, of less than 100 times a Hubble time, with $t_{fric}$ defined from \citet{2008gady.book.....B} as:
+For each galaxy in the simulations, we only used black holes that would theoretically have merged with the center of the host galaxy within a dynamical friction time, $t_{fric}$, of less than 100 times a Hubble time, with $t_{fric}$ defined by the Chandrasekhar formula from \citet{2008gady.book.....B} as:
 \begin{equation}\label{tfric}
@@
 \end{equation}
+\textbf{The formula above was not a factor during the simulations.
+We used the full dynamical friction model (section \ref{psd}) during the simulations}.
 The orbiting black holes were injected into their host galaxy at redshift $z$, at a distance from the galactic center of $R_{e}$ (Equation \ref{re}) following galaxy mergers.
@@
 The plot monotonically increases with increasing mass ratio, reaching nearly unity for mass ratio of $10^{-1}$, meaning nearly all galaxy mergers with a black hole mass ratio greater than $10^{-1}$ resulted in the orbiting black hole merging with the host.
+\textbf{It is worth noting that all of the mergers were due to N-body effects; without a third interacting black hole, none of the black holes that reached within $r{_c}$ merged with their host.}
 
@@
 It is also evident from the plot that all but two of the black holes that had not been kicked by $z=0$ have mostly approached and entered within the galactic core radius, $r_c$ (which never exceeded 1 kpc in any of the galaxies).
+\textbf{The black holes that were kicked come back to the center, but due to their highly eccentric nature, they spend mos of their time far from the center.
+Additionally, there are only 5 black holes within 10 pc of the center due to N-body effects and the Kozai mechanism}.
 
@@
 \begin{center}
-\includegraphics[width=1.0\columnwidth]{plots/"Summary Results All Galaxies".png}
+\includegraphics[width=1.0\columnwidth]{plots/Summary_Results_All_Galaxies.png}
 \caption{Histogram of merged, ejected, and orbiting SMBHs at z=0 as a function of BH mass.
@@
 \begin{center}
-\includegraphics[width=1.0\columnwidth]{plots/"Final Radius v Mass of Orbiting BHs".png}
+\includegraphics[width=1.0\columnwidth]{plots/Final_Radius_v_Mass_of_Orbiting_BHs.png}
 \caption{Final radii of remaining orbital black holes at z=0.
-Kicked black holes generally had a low likelihood of finding their way back to the center by z=0.
+\textbf{Kicked black holes come back to the center, but due to their highly eccentric nature, they spend most of their time far from the center}.
 There is a slight inverse relationship between BH mass and final distance from center (solid line).}
@@
 \begin{center}
-\includegraphics[width=1.0\columnwidth]{plots/"Lx of our Galaxies compared to Babyk data".png}
+\includegraphics[width=1.0\columnwidth]{plots/Lx_of_our_Galaxies_compared_to_Babyk_data.png}
 \caption{X-ray thermal luminosity of hot gas in our galaxies, compared to those from \citet{2018ApJ...857...32B}.}
@@
 In lieu of summing over discrete particles, we use the beta model of the gas as defined in our equation \ref{beta_model} and integrate:
+
 \begin{equation}
@@
 \begin{center}
-\includegraphics[width=1.0\columnwidth]{plots/"rho_0 vs sigma with errors".png}
+\includegraphics[width=1.0\columnwidth]{plots/rho_0_vs_sigma_with_errors.png}
 \caption{Central gas density versus central velocity dispersion.
@@
 \begin{center}
-\includegraphics[width=1.0\columnwidth]{plots/"Tx vs sigma with errors".png}
+\includegraphics[width=1.0\columnwidth]{plots/Tx_vs_sigma_with_errors.png}
 \caption{X-ray temperature versus central velocity dispersion.
@@
 \begin{center}
-\includegraphics[width=1.0\columnwidth]{plots/"Comparison of L_x versus radius with and without BH Influence".png}
+\includegraphics[width=1.0\columnwidth]{plots/Comparison_of_L_x_versus_radius_with_and_without_BH_Influence.png}
 \caption{Difference in X-ray thermal luminosity of wandering black holes within the influence radius of the central black hole.
@@
 \begin{center}
-\includegraphics[width=1.0\columnwidth]{plots/"Final Luminosities using Kohei factor".png}
+\includegraphics[width=1.0\columnwidth]{plots/Final_Luminosities_using_Kohei_factor.png}
 \caption{X-ray thermal luminosity distribution of orbiting BHs at z=0.

### 2020-08-09 paper.tex
Final edits prior to resubmitting.

@@
 Simulations of structure formation in a $\Lambda$CDM universe show us how the massive galaxies we see today were formed through a myriad of minor and major mergers between (proto) galaxies.
-As most galaxies are believed to contain central massive black holes even at high redshifts, each of these mergers set the stage for a potential encounter between massive black holes.
+As most galaxies are believed to contain central massive black holes even at high redshifts (\citet{1998AJ....115.2285M}, \citet{2003ApJ...589L..21M}, \citet{2004ApJ...604L..89H}, \citet{2013ARA&A..51..511K}), each of these mergers set the stage for a potential encounter between massive black holes.
 Here we investigate what happened to those black holes over a timeframe of billions of years.
@@
 
-%(check if X-1 and X-2 in NGC 1313 are candidates for such objects see https://arxiv.org/pdf/astro-ph/0608066.pdf )
+Orbiting black holes have been studied in the past using both semi-analytical methods and dynamical simulations.
+\citet{2003ApJ...582..559V} followed the merger history of dark matter haloes and associated BH mergers using Monte-Carlo realizations, and found a population of BHs orbiting in galaxy haloes and the intergalactic medium at the present epoch.
+In a follow-up study, \citet{2005MNRAS.358..913V} found that the orbiting black holes should have luminosities in X-ray $\lessapprox10^9 M_{\sun}$.
+\citet{2008MNRAS.390.1311B} looked at the effects of gravitational recoil due to BH mergers on the growth of SMBHs, and found that the recoiled BHs can orbit their host galaxy for $10^6-10^9$ years before returning to the center, while accreting gas equivalent to approximate $10{\%}$ of their initial mass.
+\citet{2017MNRAS.472.1526C} simulated recoiling black hole trajectories, altering various parameters in their simulations and observing the effects on escape velocities.
+They found that the overall mass of the host halo and the accretion rate onto the halo are the largest factors affecting the escape velocity of a recoiled BH.
+In a large-scale cosomological simulation (ROMULUS25) of Milky Way-mass galaxies, \citet{2018ApJ...857L..22T} found that such haloes would have approximately 5 SMBHs within $10kpc$ from the galactic center, and 12 SMBHs within they virial radius.
+\citet{2020MNRAS.495.4681I} used a semi-analytical model to study the mass assembly and spin evolution of SMBHs, as well as the effects of gravitational recoil on central and orbiting black holes.
+One of their findings is that the number and masses of orbiting black holes corresponds with the halo and stellar mass of the host galaxy, with their location within the galaxy being approximately $0.5R_{200}$.
 
@@
 \citet{2015ApJ...799..178K} furthered the merger tree data produced by \citet{2012MNRAS.425..641L} by estimating the evolution of the SMBH population.
+In their simulations, they seed a black hole in any galaxy that reaches their prescribed lower mass limit ($M_* \simeq 10^8 M_{\sun}$).
+The initial mass of the seeded black hole is then taken to be $nM_{*, bulge}$, where $n$ is drawn from a log-normal distribution with median $\simeq10^{-3}$ and intrinsic scatter of 0.35.
+The black holes subsequently grow through BH-BH mergers and gas accretion.
+The accretion component is proportional to the stellar mass formed in the host galaxy in a given redshift slice times the bulge fraction of the host galaxy.
 They assume growth of SMBHs to be proportional to that of the bulge stellar mass of the galaxies.
 They further assume a constant relation between bulge and total stellar mass at all redshifts, although some observations suggest that the bulge mass fraction for a fixed stellar mass should increase with decreasing redshift (\citealt{2012MNRAS.423.1992S, 2013MNRAS.428.1351G, 2014MNRAS.441..417A}), with the result that their SMBHs grow faster at high redshift than would be expected in reality.
+
+\citet{2015ApJ...799..178K} also had a prescription for re-seeding a galaxy with a central black hole in the event the previous one was ejected due to gravitational recoils.
+If the galaxy subsequently produced an additional $10^9M_{\sun}$ in unscaled galactic stellar mass, they re-seed the galaxy using the same method described above.
+In our simulations, the central black holes were never ejected, and we did not need to use the above-described re-seeding.
 
@@
     \item Galactic properties - Each galaxy was distinguished by an id number, with properties such as stellar mass, dark matter (DM) mass, central black hole id number, and orbiting black hole id numbers, recorded at 37 redshift slices between $4\geq z \geq0$.
+The original \citet{2015ApJ...799..178K} simulations had 38 redshift slices.
+However, one was dropped due to an error in the dataset.
     \item Black Hole properties - Each black hole was also distinguished by an id number, with properties such as seed mass, accreted mass, its host galaxy id number, and time after $z=4$ at which the black hole entered its host galaxy, if it was not the central black hole.
@@
 
-\textbf{The vast majority of the full set of galaxies (1,537) were eliminated because they did not come into existence until after $z=4$.
-Of the remaining 293 galaxies, 67 of them existed at z=0, and 51 of them also had black holes orbiting at z=0}.
-In considering time and resources, we chose the 11 galaxies that had the largest number black holes to run the simulations.
+The vast majority of the full set of galaxies (1,537) were eliminated because they did not come into existence until after $z=4$.
+Of the remaining 293 galaxies, 67 of them existed at z=0, and 51 of them also had black holes orbiting at z=0.
+In considering time and resources, we chose the 11 galaxies that had the largest number of black holes to run the simulations.
 The black holes in these galaxies accounted for nearly $84{\%}$ of all orbiting black holes across all the galaxies, so it represented a reasonable balance between completeness and efficiency.
@@
 The standard deviation was assumed arbitrarily to be $0.3\mu$.
+After rescaling the stellar masses at $z=0$, we used that proportionality to rescale the masses through the entire simulation from $4\geq z \geq0$.
 Table \ref{table:gal_char} shows the original and rescaled stellar masses.
@@
 \includegraphics[width=1.0\columnwidth]{plots/stellar_to_halo_ratio.png}
-\caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.
-$f_\mathrm{bary}$ is the universal baryon fraction as a function of total halo mass.
+\caption{Approximation of Figure 11 from \citet{2018AstL...44....8K}.}  $f_\mathrm{bary}$ is the universal baryon fraction as a function of total halo mass.
 Purple dots shown are examples of our rescaled stellar masses.
@@
 For a given galaxy's dark matter mass, the mean of the distribution was taken to be the point on the abundance matching line at that dark matter mass.
-The standard deviation of that mean was taken arbitrarily to be 0.3.}
+The standard deviation of that mean was taken arbitrarily to be 0.3.
 \label{fig:stellar1}
@@
 where $\Delta v_\parallel \equiv \Delta \vec{v}\cdot\vec{v}/v$ is the velocity change in direction of motion, and $\Delta \vec{v}_\bot \equiv \Delta \vec{v} - \Delta v_\parallel \cdot\vec{v}/v$ is the velocity change perpendicular to the direction of motion.
-Here, $M_{BH}$ is the mass of the black hole, and $\chi = \frac{v}{\sqrt{2}\sigma(r)}$.
+Here, $\sigma$ is the local velocity dispersion of the host galaxy, $M_{BH}$ is the mass of the black hole, and $\chi = \frac{v}{\sqrt{2}\sigma(r)}$.
 The function $f(\chi)$ is given by
@@
 \subsubsection{Gravitational wave recoils and escape}
-The code \textsc{AR-Chain} includes post-Newtonian terms up to order 2.5.
+The code \textsc{AR-Chain} (\citet{2006MNRAS.372..219M} and \citet{2008AJ....135.2398M}) includes post-Newtonian terms up to order 2.5.
 The SMBHs can therefore merge via gravitational wave emission.
-We include gravitational wave recoils following the prescription outlined in \citet{2015ApJ...799..178K}, which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.
+We include gravitational wave recoils (\citet{2007ApJ...659L...5C}, \citet{2011PhRvD..83b4003L}, \citet{2013PhRvD..87h4027L}, \citet{2012ApJ...744...45B}) following the prescription outlined in \citet{2015ApJ...799..178K}, which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.
 We assume that a merger will be inevitable when the separation between two SMBHs becomes smaller than four times the Schwarzschild radius of the more massive black hole.
 At the moment of the merger, we also assume that the spin vectors of the two SMBHs are randomly aligned.
+There are reasons to believe that the actual spins of the binary BHs may not be randomly aligned, as described further below.
 
@@
 In our simulations, the binaries never stray more than a few tens of parsecs from the nucleus of the host galaxies.
+As mentioned above, we calculate the spins and kicks (recoil velocities) of the black holes in the same way that \citet{2015ApJ...799..178K} implemented it (their Equations 11), which in turn followed the implementation from \citet{2012PhRvD..85h4015L}.
+We also adopt a value of $\xi$ = 145$^{\circ}$ based on the numerical results for quasi-circular merger configurations from \citet{2008PhRvD..77d4028L}.
+
+The kick distribution is approximated in the way described above, but the actual distribution of kicks may vary since, for example, the alignment of BH spins may not be fully random, as demonstrated in \citet{2012PhRvD..85h4015L} and \citet{2010MNRAS.402..682D}.
+Accretion disks surrounding the merging black holes may help align spins between the merging black holes on a timescale shorter than the time needed to merge.
 
@@
 \end{equation}
-\textbf{The formula above was not a factor during the simulations.
-We used the full dynamical friction model (section \ref{psd}) during the simulations}.
+The formula above was not a factor during the simulations.
+We used the full dynamical friction model (section \ref{psd}) during the simulations.
 The orbiting black holes were injected into their host galaxy at redshift $z$, at a distance from the galactic center of $R_{e}$ (Equation \ref{re}) following galaxy mergers.
@@
 
+In this section, "orbiting" black holes refer to all black holes that are still orbiting within their host galaxy at $z=0$.
+"Kicked" black holes are a subset of orbiting black holes, in that they are still orbiting within their host galaxy, but at some point during the simulation were kicked to a higher orbit due to three-body scattering.
+"Ejected" black holes are those that were given a large enough of a recoil velocity due to three-body scattering that they were ejected from their host galaxy.
+To clarify, any discussion of kicked black holes below only refers to those that are still orbiting their host galaxy.
+Similarly, discussions of ejected black holes only refer to those that were ejected.
+
 Figure \ref{fig:meosmbh} shows the distribution of merged, ejected and orbiting black holes (stacked) across all galaxy simulations as a function of the mass of the infalling black holes.
@@
 
-Given the log distribution of masses, one can see the general trend of larger mass BHs ($\goa\, 10^7\, M_{\odot}$) tending to merge with their respective host BH, while lower mass BHs continue to wander at $z=0$.
+Given the log distribution of masses, one can see the general trend of larger mass BHs ($\goa\, 10^7\, M_{\odot}$) tending to merge with their respective host BH, while lower mass BHs continue to orbit at $z=0$.
 However, there is some overlap with some BHs greater than $10^7\, M_{\odot}$ still orbiting and those less than $10^7\, M_{\odot}$ having merged.
@@
 The plot monotonically increases with increasing mass ratio, reaching nearly unity for mass ratio of $10^{-1}$, meaning nearly all galaxy mergers with a black hole mass ratio greater than $10^{-1}$ resulted in the orbiting black hole merging with the host.
-\textbf{It is worth noting that all of the mergers were due to N-body effects; without a third interacting black hole, none of the black holes that reached within $r{_c}$ merged with their host.}
+It is worth noting that all of the mergers were due to N-body effects; without a third interacting black hole, none of the black holes that reached within $r{_c}$ merged with their host.
+This conclusion is identical to that reached by the careful treatment by \citet{2018MNRAS.473.3410R} (''Interactions between multiple supermassive black holes in galactic nuclei: a solution to the final parsec problem'').
 
@@
 
-Approximately 50\% of the mergers appeared to have been directly assisted by a hard three-body encounter with a third rendezvousing black hole, which as a consequence got kicked to a higher orbit (and in a few instances ejected).
-A large fraction of the remaining BH mergers were accelerated through soft encounters with infalling black holes.
-Our simulations suggest that few-body encounters are in fact a significant driver of BH-BH mergers in galactic centers.
-
-\subsection{Kicked, Ejected and Orbiting Black Holes}\label{sec:kicked_orbiting}
+\subsection{Ejected and Orbiting Black Holes}\label{sec:kicked_orbiting}
 Of the 37 orbiting black holes at $z=0$, 18 of them were kicked to higher orbits during traversal of their host galaxy.
@@
 
-Figure \ref{fig:mvr} is a realization of the final radii of the remaining wandering black holes at $z=0$.
+Figure \ref{fig:mvr} is a realization of the final radii of the remaining orbiting black holes at $z=0$.
 There is a slight inverse relationship between black hole mass and final radius (solid line), but with a wide dispersion.
 It is also evident from the plot that all but two of the black holes that had not been kicked by $z=0$ have mostly approached and entered within the galactic core radius, $r_c$ (which never exceeded 1 kpc in any of the galaxies).
-\textbf{The black holes that were kicked come back to the center, but due to their highly eccentric nature, they spend mos of their time far from the center.
-Additionally, there are only 5 black holes within 10 pc of the center due to N-body effects and the Kozai mechanism}.
+The black holes that were kicked come back to the center, but due to their highly eccentric nature, they spend most of their time far from the center.
+Additionally, there are only 5 black holes within 10 pc of the center due to N-body effects and the Kozai mechanism.
 
@@
 \caption{Final radii of remaining orbital black holes at z=0.
-\textbf{Kicked black holes come back to the center, but due to their highly eccentric nature, they spend most of their time far from the center}.
+Kicked black holes come back to the center, but due to their highly eccentric nature, they spend most of their time far from the center.
 There is a slight inverse relationship between BH mass and final distance from center (solid line).}
@@
 This results in $\mu=0.606$.
-The resulting X-ray thermal luminosities are shown in Figures \ref{fig:galgas1} and compared against a sample from \citet{2018ApJ...857...32B}.
+The resulting X-ray thermal luminosities are shown in Figure \ref{fig:galgas1} and compared against a sample from \citet{2018ApJ...857...32B}.
 
@@
 Since we model the black holes in this work as point particles for purposes of the simulations, we do not assume any particular structure to them.
-Therefore, we adopt the approach and assumptions from \citealt{2018MNRAS.476.1412I} and \citealt{2019MNRAS.486.5377I} in estimating the X-ray luminosities of the remaining black holes left wandering in our subject galaxies.
+Therefore, we adopt the approach and assumptions from \citealt{2018MNRAS.476.1412I} and \citealt{2019MNRAS.486.5377I} in estimating the X-ray luminosities of the remaining black holes left orbiting in our subject galaxies.
 Their approach assumes rotating accretion flows in a very low-density environment.
@@
 \subsubsection{Gas Environment Surrounding Black Holes}
-In order to model the surrounding environment of the wandering black holes, we used the data and scaling relations from \citet{2018ApJ...857...32B}, which are based on Chandra X-ray observations of 94 early-type, gas poor galaxies of several morphological types (elliptical, lenticular, SB, BCGs, and cD galaxies).
+In order to model the surrounding environment of the orbiting black holes, we used the data and scaling relations from \citet{2018ApJ...857...32B}, which are based on Chandra X-ray observations of 94 early-type, gas poor galaxies of several morphological types (elliptical, lenticular, SB, BCGs, and cD galaxies).
 In particular, we used data from Tables 2 and 3 for temperature in X-ray ($T_x$) and central gas density ($\rho_0$) to model the surrounding gas properties.
@@
 \end{equation}
-where $\rho$ is the gas density at the location of the wandering black hole, $\rho_1$ is the density at the radius where the central black hole mass equals the galaxy mass, $r$ is the distance of the wandering black hole from the center, and $r_1$ is the radius where the central black hole mass equals the galaxy mass.
+where $\rho$ is the gas density at the location of the orbiting black hole, $\rho_1$ is the density at the radius where the central black hole mass equals the galaxy mass, $r$ is the distance of the orbiting black hole from the center, and $r_1$ is the radius where the central black hole mass equals the galaxy mass.
 
-Figure \ref{fig:wui} shows the difference in luminosity when taking into account the influence of the central black hole for the 17 wandering black holes that were within the influence radius.
+Figure \ref{fig:wui} shows the difference in luminosity when taking into account the influence of the central black hole for the 17 orbiting black holes that were within the influence radius.
 In all cases, the final luminosity is higher than the original luminosity.
@@
 \includegraphics[width=1.0\columnwidth]{plots/Comparison_of_L_x_versus_radius_with_and_without_BH_Influence.png}
-\caption{Difference in X-ray thermal luminosity of wandering black holes within the influence radius of the central black hole.
+\caption{Difference in X-ray thermal luminosity of orbiting black holes within the influence radius of the central black hole.
 For each vertical line, red (lower) dots are the originally calculated luminosity, not taking the CBH influence into account.
@@
 
-\subsubsection{Final X-ray Luminosities of Wandering Black Holes, and Expected Detection Spectra}
-Figure \ref{fig:loobhs} is an approximation to Figure 12 from \cite{2019MNRAS.486.5377I}, along with the final $L_{Bol}/L_{Edd}$ ratio of the wandering black holes from this study, although extended below $10^{-6}$ $\dot{M}_{B}/\dot{M}_{Edd}$ for the very low accretion-rate sources.
+\subsubsection{Final X-ray Luminosities of orbiting Black Holes, and Expected Detection Spectra}
+Figure \ref{fig:loobhs} is an approximation to Figure 12 from \cite{2019MNRAS.486.5377I}, along with the final $L_{Bol}/L_{Edd}$ ratio of the orbiting black holes from this study, although extended below $10^{-6}$ $\dot{M}_{B}/\dot{M}_{Edd}$ for the very low accretion-rate sources.
 Indeed, such low luminosity sources are common, with some estimates of $L_{Bol}/L_{Edd}$ as low as $10^{-10}$ ( e.g., \citealt{2003ApJ...598..301Y}, \citealt{2004ApJ...613..322Q}, \citealt{2008ARA&A..46..475H}, \citealt{2009ApJ...699..626H}, \citealt{2018MNRAS.476.1412I}).
@@
 \caption{X-ray thermal luminosity distribution of orbiting BHs at z=0.
-Green region under curve represents approximate range of detectable orbiting black holes.
+Green region under curve represents approximate range of detectable orbiting black holes, with the lower limit being approximately $10^{38}\;\text{erg}\;\text{s}^{-1}$ (\citet{2018ApJ...862...73L}).
 The dashed, red vertical line is the median X-ray thermal luminosity of our sources ($1.0\times10^{33}\;\text{erg}\;\text{s}^{-1}$).}
@@
 Conversely low-mass X-ray binaries (LMXRB) have been fit to a power law spectrum with $\Gamma\sim1.5-2.0$ (\citet{2018Natur.556...70H}, and we expect our orbiting sources to be more similar to Sgr A* than to normal LMXRBs.
+
+\citet{guo2020hunting} have shown that there is an additional way of detecting the predicted orbiting massive black holes.
+They compute that the spectra have a peak at the millimeter wave band, and should enable detectors such as the Atacama Large Millimeter/submillimeter Array (ALMA) and upcoming next generation Very Large Array (ngVLA) to find orbiting black holes with masses down to approximately $M_{\bullet}\simeq2\times10^7 M_{\odot}$ in nearby galaxies such as M87, and $M_{\bullet}\simeq10^5 M_{\odot}$ in the Milky Way.
 

### 2020-08-09 paper.tex
Added back bolding to highlight changes from previous version, as per MNRAS instructions

@@
 
-Orbiting black holes have been studied in the past using both semi-analytical methods and dynamical simulations.
+\textbf{Orbiting black holes have been studied in the past using both semi-analytical methods and dynamical simulations.
 \citet{2003ApJ...582..559V} followed the merger history of dark matter haloes and associated BH mergers using Monte-Carlo realizations, and found a population of BHs orbiting in galaxy haloes and the intergalactic medium at the present epoch.
@@
 \citet{2020MNRAS.495.4681I} used a semi-analytical model to study the mass assembly and spin evolution of SMBHs, as well as the effects of gravitational recoil on central and orbiting black holes.
-One of their findings is that the number and masses of orbiting black holes corresponds with the halo and stellar mass of the host galaxy, with their location within the galaxy being approximately $0.5R_{200}$.
+One of their findings is that the number and masses of orbiting black holes corresponds with the halo and stellar mass of the host galaxy, with their location within the galaxy being approximately $0.5R_{200}$.}
 
@@
 \citet{2015ApJ...799..178K} furthered the merger tree data produced by \citet{2012MNRAS.425..641L} by estimating the evolution of the SMBH population.
-In their simulations, they seed a black hole in any galaxy that reaches their prescribed lower mass limit ($M_* \simeq 10^8 M_{\sun}$).
+\textbf{In their simulations, they seed a black hole in any galaxy that reaches their prescribed lower mass limit ($M_* \simeq 10^8 M_{\sun}$).
 The initial mass of the seeded black hole is then taken to be $nM_{*, bulge}$, where $n$ is drawn from a log-normal distribution with median $\simeq10^{-3}$ and intrinsic scatter of 0.35.
 The black holes subsequently grow through BH-BH mergers and gas accretion.
-The accretion component is proportional to the stellar mass formed in the host galaxy in a given redshift slice times the bulge fraction of the host galaxy.
-They assume growth of SMBHs to be proportional to that of the bulge stellar mass of the galaxies.
+The accretion component is proportional to the stellar mass formed in the host galaxy in a given redshift slice times the bulge fraction of the host galaxy.}  They assume growth of SMBHs to be proportional to that of the bulge stellar mass of the galaxies.
 They further assume a constant relation between bulge and total stellar mass at all redshifts, although some observations suggest that the bulge mass fraction for a fixed stellar mass should increase with decreasing redshift (\citealt{2012MNRAS.423.1992S, 2013MNRAS.428.1351G, 2014MNRAS.441..417A}), with the result that their SMBHs grow faster at high redshift than would be expected in reality.
 
-\citet{2015ApJ...799..178K} also had a prescription for re-seeding a galaxy with a central black hole in the event the previous one was ejected due to gravitational recoils.
+\textbf{\citet{2015ApJ...799..178K} also had a prescription for re-seeding a galaxy with a central black hole in the event the previous one was ejected due to gravitational recoils.
 If the galaxy subsequently produced an additional $10^9M_{\sun}$ in unscaled galactic stellar mass, they re-seed the galaxy using the same method described above.
-In our simulations, the central black holes were never ejected, and we did not need to use the above-described re-seeding.
+In our simulations, the central black holes were never ejected, and we did not need to use the above-described re-seeding.}
 
@@
     \item Galactic properties - Each galaxy was distinguished by an id number, with properties such as stellar mass, dark matter (DM) mass, central black hole id number, and orbiting black hole id numbers, recorded at 37 redshift slices between $4\geq z \geq0$.
-The original \citet{2015ApJ...799..178K} simulations had 38 redshift slices.
-However, one was dropped due to an error in the dataset.
+\textbf{The original \citet{2015ApJ...799..178K} simulations had 38 redshift slices.
+However, one was dropped due to an error in the dataset.}
     \item Black Hole properties - Each black hole was also distinguished by an id number, with properties such as seed mass, accreted mass, its host galaxy id number, and time after $z=4$ at which the black hole entered its host galaxy, if it was not the central black hole.
@@
 
-The vast majority of the full set of galaxies (1,537) were eliminated because they did not come into existence until after $z=4$.
-Of the remaining 293 galaxies, 67 of them existed at z=0, and 51 of them also had black holes orbiting at z=0.
+\textbf{The vast majority of the full set of galaxies (1,537) were eliminated because they did not come into existence until after $z=4$.
+Of the remaining 293 galaxies, 67 of them existed at z=0, and 51 of them also had black holes orbiting at z=0}.
 In considering time and resources, we chose the 11 galaxies that had the largest number of black holes to run the simulations.
@@
 The standard deviation was assumed arbitrarily to be $0.3\mu$.
-After rescaling the stellar masses at $z=0$, we used that proportionality to rescale the masses through the entire simulation from $4\geq z \geq0$.
-Table \ref{table:gal_char} shows the original and rescaled stellar masses.
+\textbf{After rescaling the stellar masses at $z=0$, we used that proportionality to rescale the masses through the entire simulation from $4\geq z \geq0$.}  Table \ref{table:gal_char} shows the original and rescaled stellar masses.
 
@@
 where $\Delta v_\parallel \equiv \Delta \vec{v}\cdot\vec{v}/v$ is the velocity change in direction of motion, and $\Delta \vec{v}_\bot \equiv \Delta \vec{v} - \Delta v_\parallel \cdot\vec{v}/v$ is the velocity change perpendicular to the direction of motion.
-Here, $\sigma$ is the local velocity dispersion of the host galaxy, $M_{BH}$ is the mass of the black hole, and $\chi = \frac{v}{\sqrt{2}\sigma(r)}$.
+Here, \textbf{$\sigma$ is the local velocity dispersion of the host galaxy,} $M_{BH}$ is the mass of the black hole, and $\chi = \frac{v}{\sqrt{2}\sigma(r)}$.
 The function $f(\chi)$ is given by
@@
 At the moment of the merger, we also assume that the spin vectors of the two SMBHs are randomly aligned.
-There are reasons to believe that the actual spins of the binary BHs may not be randomly aligned, as described further below.
+\textbf{There are reasons to believe that the actual spins of the binary BHs may not be randomly aligned, as described further below.}
 
@@
 In our simulations, the binaries never stray more than a few tens of parsecs from the nucleus of the host galaxies.
-As mentioned above, we calculate the spins and kicks (recoil velocities) of the black holes in the same way that \citet{2015ApJ...799..178K} implemented it (their Equations 11), which in turn followed the implementation from \citet{2012PhRvD..85h4015L}.
-We also adopt a value of $\xi$ = 145$^{\circ}$ based on the numerical results for quasi-circular merger configurations from \citet{2008PhRvD..77d4028L}.
+\textbf{As mentioned above, we calculate the spins and kicks (recoil velocities) of the black holes in the same way that \citet{2015ApJ...799..178K} implemented it (their Equations 11), which in turn followed the implementation from \citet{2012PhRvD..85h4015L}.
+We also adopt a value of $\xi$ = 145$^{\circ}$ based on the numerical results for quasi-circular merger configurations from \citet{2008PhRvD..77d4028L}.}
 
-The kick distribution is approximated in the way described above, but the actual distribution of kicks may vary since, for example, the alignment of BH spins may not be fully random, as demonstrated in \citet{2012PhRvD..85h4015L} and \citet{2010MNRAS.402..682D}.
-Accretion disks surrounding the merging black holes may help align spins between the merging black holes on a timescale shorter than the time needed to merge.
+\textbf{The kick distribution is approximated in the way described above, but the actual distribution of kicks may vary since, for example, the alignment of BH spins may not be fully random, as demonstrated in \citet{2012PhRvD..85h4015L} and \citet{2010MNRAS.402..682D}.
+Accretion disks surrounding the merging black holes may help align spins between the merging black holes on a timescale shorter than the time needed to merge.}
 
@@
 \end{equation}
-The formula above was not a factor during the simulations.
-We used the full dynamical friction model (section \ref{psd}) during the simulations.
+\textbf{The formula above was not a factor during the simulations.
+We used the full dynamical friction model (section \ref{psd}) during the simulations}.
 The orbiting black holes were injected into their host galaxy at redshift $z$, at a distance from the galactic center of $R_{e}$ (Equation \ref{re}) following galaxy mergers.
@@
 
-In this section, "orbiting" black holes refer to all black holes that are still orbiting within their host galaxy at $z=0$.
+\textbf{In this section, "orbiting" black holes refer to all black holes that are still orbiting within their host galaxy at $z=0$.
 "Kicked" black holes are a subset of orbiting black holes, in that they are still orbiting within their host galaxy, but at some point during the simulation were kicked to a higher orbit due to three-body scattering.
@@
 To clarify, any discussion of kicked black holes below only refers to those that are still orbiting their host galaxy.
-Similarly, discussions of ejected black holes only refer to those that were ejected.
+Similarly, discussions of ejected black holes only refer to those that were ejected.}
 
@@
 The plot monotonically increases with increasing mass ratio, reaching nearly unity for mass ratio of $10^{-1}$, meaning nearly all galaxy mergers with a black hole mass ratio greater than $10^{-1}$ resulted in the orbiting black hole merging with the host.
-It is worth noting that all of the mergers were due to N-body effects; without a third interacting black hole, none of the black holes that reached within $r{_c}$ merged with their host.
-This conclusion is identical to that reached by the careful treatment by \citet{2018MNRAS.473.3410R} (''Interactions between multiple supermassive black holes in galactic nuclei: a solution to the final parsec problem'').
+\textbf{It is worth noting that all of the mergers were due to N-body effects; without a third interacting black hole, none of the black holes that reached within $r{_c}$ merged with their host.
+This conclusion is identical to that reached by the careful treatment by \citet{2018MNRAS.473.3410R} (''Interactions between multiple supermassive black holes in galactic nuclei: a solution to the final parsec problem'').}
 
@@
 It is also evident from the plot that all but two of the black holes that had not been kicked by $z=0$ have mostly approached and entered within the galactic core radius, $r_c$ (which never exceeded 1 kpc in any of the galaxies).
-The black holes that were kicked come back to the center, but due to their highly eccentric nature, they spend most of their time far from the center.
-Additionally, there are only 5 black holes within 10 pc of the center due to N-body effects and the Kozai mechanism.
+\textbf{The black holes that were kicked come back to the center, but due to their highly eccentric nature, they spend most of their time far from the center.
+Additionally, there are only 5 black holes within 10 pc of the center due to N-body effects and the Kozai mechanism}.
 
@@
 \caption{Final radii of remaining orbital black holes at z=0.
-Kicked black holes come back to the center, but due to their highly eccentric nature, they spend most of their time far from the center.
+\textbf{Kicked black holes come back to the center, but due to their highly eccentric nature, they spend most of their time far from the center}.
 There is a slight inverse relationship between BH mass and final distance from center (solid line).}
@@
 \caption{X-ray thermal luminosity distribution of orbiting BHs at z=0.
-Green region under curve represents approximate range of detectable orbiting black holes, with the lower limit being approximately $10^{38}\;\text{erg}\;\text{s}^{-1}$ (\citet{2018ApJ...862...73L}).
+Green region under curve represents approximate range of detectable orbiting black holes, \textbf{with the lower limit being approximately $10^{38}\;\text{erg}\;\text{s}^{-1}$ (\citet{2018ApJ...862...73L})}.
 The dashed, red vertical line is the median X-ray thermal luminosity of our sources ($1.0\times10^{33}\;\text{erg}\;\text{s}^{-1}$).}
@@
 
-\citet{guo2020hunting} have shown that there is an additional way of detecting the predicted orbiting massive black holes.
-They compute that the spectra have a peak at the millimeter wave band, and should enable detectors such as the Atacama Large Millimeter/submillimeter Array (ALMA) and upcoming next generation Very Large Array (ngVLA) to find orbiting black holes with masses down to approximately $M_{\bullet}\simeq2\times10^7 M_{\odot}$ in nearby galaxies such as M87, and $M_{\bullet}\simeq10^5 M_{\odot}$ in the Milky Way.
+\textbf{\citet{guo2020hunting} have shown that there is an additional way of detecting the predicted orbiting massive black holes.
+They compute that the spectra have a peak at the millimeter wave band, and should enable detectors such as the Atacama Large Millimeter/submillimeter Array (ALMA) and upcoming next generation Very Large Array (ngVLA) to find orbiting black holes with masses down to approximately $M_{\bullet}\simeq2\times10^7 M_{\odot}$ in nearby galaxies such as M87, and $M_{\bullet}\simeq10^5 M_{\odot}$ in the Milky Way.}
 

### 2020-08-18 paper.tex
A few minor style revisions.

--- 2020-08-09 paper.tex
@@
 These orbiting BHs should be detectable by their anomalous (not Low Mass X-ray Binary) spectra.
-The X-ray luminosities of the orbiting massive BHs at z=0 are in the range $10^{28}-10^{43}$ $\mathrm{erg}~\mathrm{s}^{-1}$, with a currently undetectable median value of $10^{33}$ $\mathrm{erg}~\mathrm{s}^{-1}$.
+The X-ray luminosities of the orbiting massive BHs at $z=0$ are in the range $10^{28}-10^{43}$ $\mathrm{erg}~\mathrm{s}^{-1}$, with a currently undetectable median value of $10^{33}$ $\mathrm{erg}~\mathrm{s}^{-1}$.
 However, the most luminous $\sim$5\% should be detectable by existing X-ray facilities.
@@
 \citet{2003ApJ...582..559V} followed the merger history of dark matter haloes and associated BH mergers using Monte-Carlo realizations, and found a population of BHs orbiting in galaxy haloes and the intergalactic medium at the present epoch.
-In a follow-up study, \citet{2005MNRAS.358..913V} found that the orbiting black holes should have luminosities in X-ray $\lessapprox10^9 M_{\sun}$.
+In a follow-up study, \citet{2005MNRAS.358..913V} found that the orbiting black holes should have luminosities in X-ray $\lessapprox10^{39} M_{\sun}$.
 \citet{2008MNRAS.390.1311B} looked at the effects of gravitational recoil due to BH mergers on the growth of SMBHs, and found that the recoiled BHs can orbit their host galaxy for $10^6-10^9$ years before returning to the center, while accreting gas equivalent to approximate $10{\%}$ of their initial mass.
@@
 \begin{itemize}
-\item The galaxies had to exist through the entire simulation ($4\geq z \geq 0$).  If they merged with other galaxies, they had to have been the "surviving" galaxy at each merger.
+\item The galaxies had to exist through the entire simulation ($4\geq\;z\;\geq 0$).  If they merged with other galaxies, they had to have been the "surviving" galaxy at each merger.
 \item They had to have accumulated orbiting black holes by $z = 0$.
@@
 The vast majority of the full set of galaxies (1,537) were eliminated because they did not come into existence until after $z=4$.
-Of the remaining 293 galaxies, 67 of them existed at z=0, and 51 of them also had black holes orbiting at z=0.
+Of the remaining 293 galaxies, 67 of them existed at $z=0$, and 51 of them also had black holes orbiting at $z=0$.
 In considering time and resources, we chose the 11 galaxies that had the largest number of black holes to run the simulations.
@@
 \begin{center}
-\caption{Galaxy characteristics at z=0. $M_\mathrm{DM}$ is dark matter mass.  $M_\mathrm{CBH}$ is central black hole mass.  Units are $M_{\odot}$.}
+\caption{Galaxy characteristics at $z=0$. $M_\mathrm{DM}$ is dark matter mass.  $M_\mathrm{CBH}$ is central black hole mass.  Units are $M_{\odot}$.}
 \begin{tabular} {|c | c | c| c|}
@@
 \includegraphics[width=1.0\columnwidth]{plots/Summary_Results_All_Galaxies.png}
-\caption{Histogram of merged, ejected, and orbiting SMBHs at z=0 as a function of BH mass.
+\caption{Histogram of merged, ejected, and orbiting SMBHs at $z=0$ as a function of BH mass.
 Ejected black holes span almost the entire mass range, while lower-mass black holes are orbiting and higher mass black holes tended to merge.
@@
 \includegraphics[width=1.0\columnwidth]{plots/kicked_stats.png}
-\caption{Histogram of kicked and not-kicked SMBHs at z=0.  Colored arrows along upper x-axis represent median masses of respective sets.  Histograms are stacked.}
+\caption{Histogram of kicked and not-kicked SMBHs at $z=0$.  Colored arrows along upper x-axis represent median masses of respective sets.  Histograms are stacked.}
 \label{fig:kicked_stats}
@@
 \includegraphics[width=1.0\columnwidth]{plots/Final_Radius_v_Mass_of_Orbiting_BHs.png}
-\caption{Final radii of remaining orbital black holes at z=0.
+\caption{Final radii of remaining orbital black holes at $z=0$.
 Kicked black holes come back to the center, but due to their highly eccentric nature, they spend most of their time far from the center.
@@
 \includegraphics[width=1.0\columnwidth]{plots/Final_Luminosities_using_Kohei_factor.png}
-\caption{X-ray thermal luminosity distribution of orbiting BHs at z=0.
+\caption{X-ray thermal luminosity distribution of orbiting BHs at $z=0$.
 Green region under curve represents approximate range of detectable orbiting black holes, with the lower limit being approximately $10^{38}\;\text{erg}\;\text{s}^{-1}$ (\citet{2018ApJ...862...73L}).
@@
 \section{Conclusions}\label{sec:conclusions}
-We performed N-body simulations on 11 galaxies ranging in mass between $10^{12}$ M$_{\sun}$ < M < 3$\times$ $10^{13}$ M$_{\sun}$, from 4 $\geq$ z $\geq$ 0.
+We performed N-body simulations on 11 galaxies ranging in mass between $10^{12}$ M$_{\sun}$\;<\;M\;<\;3$\times$ $10^{13}$ M$_{\sun}$, from $4\;\geq\;z\;\geq\;0$.
 A total of 86 orbiting black holes were followed in our simulations, resulting in 42$\%$ mergers with their host galaxy's resident black hole, while another 43$\%$ remained in orbit at $z=0$.
